---
title: "2022 sb 36 tables 1-3"
output: html_document
---

Install
```{r}
#install.packages(c("DBI", "dplyr","dbplyr","odbc"))
install.packages("DBI")
install.packages("xfun")
install.packages("dplyr")
```

Libraries
```{r setup}
library(DBI)
library(dplyr)
library(dbplyr)
library(odbc)
library(tidyverse)
library(openxlsx)
library(lubridate)
```

Connection
```{r eval=FALSE, include=FALSE}
con <- dbConnect(odbc::odbc(), "snowflake_pretrial", uid ="Sal.Lempert@jud.ca.gov", pwd = .rs.askForPassword("Password"))
```

# Aggregate Data

Pull Snowflake data
```{sql connection = con, output.var = full_df}
SELECT *
FROM "DWH_PROD"."DATA_SCIENCE"."CJS_OUTCOME_STD"
;
```

```{r}
names(full_df) <- tolower(names(full_df))  

full_df <- full_df %>%
  mutate(county_orig = county) %>%
   mutate(county = case_when(
    # County %in% c("Sacramento", "Alameda", "Los Angeles") ~ "Large",
    # County %in% c("Sonoma", "San Joaquin", "San Mateo", "Tulare", "Santa Barbara", "Ventura") ~ "Medium",
    county_orig %in% c("Yuba", "Nevada", "Napa", "Kings") ~ "Small/Medium Counties",
    county_orig %in% c("Sierra", "Modoc", "Calaveras", "Tuolumne") ~ "Small Counties",
    T ~ county_orig)) %>% 
  mutate(county = ordered(county),
         county = fct_relevel(county, levels = c("Small Counties", "Small/Medium Counties")))

full_df %>%
  select(contains("sex"))

full_df %>%
  count(sex)

#alternate
full_df <- full_df %>%
   mutate(county_cat = case_when(
    # County %in% c("Sacramento", "Alameda", "Los Angeles") ~ "Large",
    # County %in% c("Sonoma", "San Joaquin", "San Mateo", "Tulare", "Santa Barbara", "Ventura") ~ "Medium",
    county %in% c("Yuba", "Nevada", "Napa", "Kings") ~ "Small/Medium Counties",
    county %in% c("Sierra", "Modoc", "Calaveras", "Tuolumne") ~ "Small Counties",
    T ~ county)) %>% 
  mutate(county_cat = ordered(county_cat),
         county_cat = fct_relevel(county_cat, levels = c("Small Counties", "Small/Medium Counties")))


```


##Rates of Release by Gender - Fresh arrests
```{r}
#look at ppl who do not have completed pretrial periods
#this may falsely represent pretrial releases for counties that have poor court data matching, because they may be released due to a disposition that we do not have a record of

# release_type variable may not be a reliable indicator of pretrial release, but going to try to use it here anyway just to see

gender_df <- full_df %>%
  mutate(release_cat = case_when(release_type %in% c("Cite Release", "CiteR elease", "Bail Bond", "Own Recognizance", "Pretrial Monitor", "PreTrial Monitor", "Unknown_Bail", "Zero Bail") ~ "Pretrial release type",
                                 release_type %in% c("Detain Only", "Detail only", "Dismissed", "Prison", "Time Served") ~ "Post-resolution release type",
                                 release_type %in% c("Hold Release", "Hold Rlease", "Other", "Unknown") ~ "Unclear release type",
                                 T ~ "Unclear release type")) %>%
  filter(release_eligible_count == 1,
         county != "Los Angeles") %>%
  mutate(pre_trial_release_flag = if_else(release_cat == "Pretrial release type", 1, 0)) %>%
  mutate(two_day_release = case_when(
    weekdays(booking_date) == "Thursday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Friday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Saturday" & release_date - booking_date <= 3 ~ 1,
    !weekdays(booking_date) %in% c("Thursday", "Friday", "Saturday") & release_date - booking_date <= 2 ~ 1,
    is.na(release_date) ~ 0,
    T ~ 0)) %>%
  mutate(quick_pretrial_type_flag = if_else(two_day_release == 1 & release_cat == "Pretrial release type", 1, 0),
         #quick_postres_type_flag = if_else(two_day_release == 1 & release_cat == "Post-resolution release type", 1, 0),
         quick_bail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Bail Bond"), 1, 0),
         quick_zerobail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Zero Bail"), 1, 0),
         quick_cite_type_flag = if_else(two_day_release == 1 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         quick_or_type_flag = if_else(two_day_release == 1 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor", "Pretrial Monitor", "PreTrial Monitor"), 1, 0),
         quick_unknown_type_flag = if_else(two_day_release == 1 & release_cat == "Unclear release type", 1, 0),
         convicted_flag = if_else(is.na(convicted_flag), 0, convicted_flag),
         #conviction = if_else(conviction_felony_flag == 1 | conviction_misd_flag == 1 | conviction_flag == 1 | convicted_flag == 1, 1, 0),
         closed_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Prison", "Time Served"), 1, 0),
         closed_not_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Detain Only", "Detain only", "Dismissed"), 1, 0),
         later_pretrial_type_flag = if_else(two_day_release == 0 & release_cat == "Pretrial release type", 1, 0),
         later_bail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Bail Bond"), 1, 0),
         later_zerobail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Zero Bail"), 1, 0),
         later_cite_type_flag = if_else(two_day_release == 0 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         later_or_type_flag = if_else(two_day_release == 0 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0)) %>%
  group_by(county, sex) %>%
  summarise(Total = n(),
            `Charges dropped or case dismissed within 2 court days` = mean(closed_not_convicted_flag),
            `Convicted within 2 court days` = mean(closed_convicted_flag),
            #`Released - (C) Pretrial release (OR or bail) within 2 court days` = mean(pre_arraignment_flag),
            `Bail release type within 2 court days` = mean(quick_bail_type_flag),
            `Zero bail release type within 2 court days` = mean(quick_zerobail_type_flag),
            `Cite & Release release type within 2 court days` = mean(quick_cite_type_flag),
            `OR release type within 2 court days` = mean(quick_or_type_flag),
            #`Released - Post-resolution release type` = mean(quick_postres_type_flag),
            `Unclear release type (post-resolution or pretrial) within 2 court days` = mean(quick_unknown_type_flag),
            `TOTAL: Released within 2 court days` = mean(two_day_release), 
            `Bail release type after 2 days` = mean(later_bail_type_flag),
            `Zero bail release type after 2 days` = mean(later_zerobail_type_flag),
            `Cite & Release release type after 2 days` = mean(later_cite_type_flag),
            `OR release type after 2 days` = mean(later_or_type_flag)) %>%
  filter(sex %in% c("Male", "Female")) %>%
  rename(`Gender` = sex)

write.xlsx(gender_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 tables 2022/2A Gender really.xlsx", asTable = F)

# full_df %>%
#   filter(release_eligible_count == 1) %>%
#   filter(sex %in% c("Male", "Female")) %>%
#   count()

```
\newpage

##Rates of Release by race_standard - Fresh arrests
```{r}
#look at ppl who do not have completed pretrial periods
#this may falsely represent pretrial releases for counties that have poor court data matching, because they may be released due to a disposition that we do not have a record of

# release_type variable may not be a reliable indicator of pretrial release, but going to try to use it here anyway just to see

race_standard_df <- full_df %>%
  mutate(race_standard = if_else(race_standard %in% c("White", "Black", "Hispanic", "Asian"), race_standard, "Other/Unknown")) %>%
  mutate(release_cat = case_when(release_type %in% c("Cite Release", "CiteR elease", "Bail Bond", "Own Recognizance", "Pretrial Monitor", "PreTrial Monitor", "Unknown_Bail", "Zero Bail") ~ "Pretrial release type",
                                 release_type %in% c("Detain Only", "Detain only", "Dismissed", "Prison", "Time Served") ~ "Post-resolution release type",
                                 release_type %in% c("Hold Release", "Other", "Unknown") ~ "Unclear release type",
                                 T ~ "Unclear release type")) %>%
  filter(release_eligible_count == 1,
         county != "Los Angeles") %>%
  mutate(pre_trial_release_flag = if_else(release_cat == "Pretrial release type", 1, 0)) %>%
  mutate(two_day_release = case_when(
    weekdays(booking_date) == "Thursday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Friday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Saturday" & release_date - booking_date <= 3 ~ 1,
    !weekdays(booking_date) %in% c("Thursday", "Friday", "Saturday") & release_date - booking_date <= 2 ~ 1,
    is.na(release_date) ~ 0,
    T ~ 0)) %>%
  mutate(quick_pretrial_type_flag = if_else(two_day_release == 1 & release_cat == "Pretrial release type", 1, 0),
         #quick_postres_type_flag = if_else(two_day_release == 1 & release_cat == "Post-resolution release type", 1, 0),
         quick_bail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         quick_zerobail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Zero Bail"), 1, 0),
         quick_cite_type_flag = if_else(two_day_release == 1 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         quick_or_type_flag = if_else(two_day_release == 1 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0),
         quick_unknown_type_flag = if_else(two_day_release == 1 & release_cat == "Unclear release type", 1, 0),
         convicted_flag = if_else(is.na(convicted_flag), 0, convicted_flag),
         #conviction = if_else(conviction_felony_flag == 1 | conviction_misd_flag == 1 | conviction_flag == 1 | convicted_flag == 1, 1, 0),
         closed_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Prison", "Time Served"), 1, 0),
         closed_not_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Detain Only", "Detain only", "Dismissed"), 1, 0),
         later_pretrial_type_flag = if_else(two_day_release == 0 & release_cat == "Pretrial release type", 1, 0),
         later_bail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         later_zerobail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Zero Bail"), 1, 0),
         later_cite_type_flag = if_else(two_day_release == 0 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         later_or_type_flag = if_else(two_day_release == 0 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0)) %>%
  group_by(county, race_standard) %>%
  summarise(Total = n(),
            `Charges dropped or case dismissed within 2 court days` = mean(closed_not_convicted_flag),
            `Convicted within 2 court days` = mean(closed_convicted_flag),
            #`Released - (C) Pretrial release (OR or bail) within 2 court days` = mean(pre_arraignment_flag),
            `Bail release type within 2 court days` = mean(quick_bail_type_flag),
            `Zero bail release type within 2 court days` = mean(quick_zerobail_type_flag),
            `Cite & Release release type within 2 court days` = mean(quick_cite_type_flag),
            `OR release type within 2 court days` = mean(quick_or_type_flag),
            #`Released - Post-resolution release type` = mean(quick_postres_type_flag),
            `Unclear release type (post-resolution or pretrial) within 2 court days` = mean(quick_unknown_type_flag),
            `TOTAL: Released within 2 court days` = mean(two_day_release), 
            `Bail release type after 2 days` = mean(later_bail_type_flag),
            `Zero bail release type after 2 days` = mean(later_zerobail_type_flag),
            `Cite & Release release type after 2 days` = mean(later_cite_type_flag),
            `OR release type after 2 days` = mean(later_or_type_flag)) %>%
  rename(`Race` = race_standard) 

write.xlsx(race_standard_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 tables 2022/2A race_standard final.xlsx", asTable = F)

# full_df %>%
#   filter(release_eligible_count == 1) %>%
#   filter(race_standard %in% c("White", "Black", "Hispanic")) %>%
#   count()

```
\newpage


\newpage
## Rates of Release by Offense Type - Fresh arrests
```{r}
#look at ppl who do not have completed pretrial periods
#this may falsely represent pretrial releases for counties that have poor court data matching, because they may be released due to a disposition that we do not have a record of

# release_type variable may not be a reliable indicator of pretrial release, but going to try to use it here anyway just to see

charge_level_df <- full_df %>%
  mutate(charge_level = charge_level_standard) %>%
  mutate(release_cat = case_when(release_type %in% c("Cite Release", "CiteR elease", "Bail Bond", "Own Recognizance", "Pretrial Monitor", "PreTrial Monitor", "Unknown_Bail", "Zero Bail") ~ "Pretrial release type",
                                 release_type %in% c("Detain Only", "Detain only", "Dismissed", "Prison", "Time Served") ~ "Post-resolution release type",
                                 release_type %in% c("Hold Release", "Other", "Unknown") ~ "Unclear release type",
                                 T ~ "Unclear release type")) %>%
  filter(release_eligible_count == 1,
         county != "Los Angeles") %>%
  mutate(pre_trial_release_flag = if_else(release_cat == "Pretrial release type", 1, 0)) %>%
  mutate(two_day_release = case_when(
    weekdays(booking_date) == "Thursday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Friday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Saturday" & release_date - booking_date <= 3 ~ 1,
    !weekdays(booking_date) %in% c("Thursday", "Friday", "Saturday") & release_date - booking_date <= 2 ~ 1,
    is.na(release_date) ~ 0,
    T ~ 0)) %>%
  mutate(quick_pretrial_type_flag = if_else(two_day_release == 1 & release_cat == "Pretrial release type", 1, 0),
         #quick_postres_type_flag = if_else(two_day_release == 1 & release_cat == "Post-resolution release type", 1, 0),
         quick_bail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         quick_zerobail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Zero Bail"), 1, 0),
         quick_cite_type_flag = if_else(two_day_release == 1 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         quick_or_type_flag = if_else(two_day_release == 1 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0),
         quick_unknown_type_flag = if_else(two_day_release == 1 & release_cat == "Unclear release type", 1, 0),
         convicted_flag = if_else(is.na(convicted_flag), 0, convicted_flag),
         #conviction = if_else(conviction_felony_flag == 1 | conviction_misd_flag == 1 | conviction_flag == 1 | convicted_flag == 1, 1, 0),
         closed_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Prison", "Time Served"), 1, 0),
         closed_not_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Detain Only", "Detain only", "Dismissed"), 1, 0),
         later_pretrial_type_flag = if_else(two_day_release == 0 & release_cat == "Pretrial release type", 1, 0),
         later_bail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         later_zerobail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Zero Bail"), 1, 0),
         later_cite_type_flag = if_else(two_day_release == 0 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         later_or_type_flag = if_else(two_day_release == 0 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0)) %>%
  group_by(county_cat, charge_level) %>%
  summarise(Total = n(),
            `Charges dropped or case dismissed within 2 court days` = mean(closed_not_convicted_flag),
            `Convicted within 2 court days` = mean(closed_convicted_flag),
            #`Released - (C) Pretrial release (OR or bail) within 2 court days` = mean(pre_arraignment_flag),
            `Bail release type within 2 court days` = mean(quick_bail_type_flag),
            `Zero bail release type within 2 court days` = mean(quick_zerobail_type_flag),
            `Cite & Release release type within 2 court days` = mean(quick_cite_type_flag),
            `OR release type within 2 court days` = mean(quick_or_type_flag),
            #`Released - Post-resolution release type` = mean(quick_postres_type_flag),
            `Unclear release type (post-resolution or pretrial) within 2 court days` = mean(quick_unknown_type_flag),
            `TOTAL: Released within 2 court days` = mean(two_day_release), 
            `Bail release type after 2 days` = mean(later_bail_type_flag),
            `Zero bail release type after 2 days` = mean(later_zerobail_type_flag),
            `Cite & Release release type after 2 days` = mean(later_cite_type_flag),
            `OR release type after 2 days` = mean(later_or_type_flag)) %>%
  mutate(charge_level = case_when(charge_level %in% c("M", "Misdemeanor") ~ "Misdemeanor",
                                  charge_level %in% c("F", "Felony") ~ "Felony",
                                  T ~ "Other")) %>%
  filter(charge_level %in% c("Felony", "Misdemeanor")) %>%
  rename(`Arrest Charge Level` = charge_level) %>%
  arrange(desc(`Arrest Charge Level`))

write.xlsx(charge_level_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 tables 2022/2A Offense Type final.xlsx", asTable = F)

# full_df %>%
#   filter(release_eligible_count == 1) %>%
#   filter(charge_level %in% c("Felony", "Misdemeanor")) %>%
#   count()

# full_df %>%
#   count(county, book_type_original, release_eligible_count)
# 
# full_df %>%
#   count(county, book_type, book_type_original, release_eligible_count)
# 
# full_df %>%
#   filter(county == "Modoc") %>%
#   count(release_eligible_count)
# 
# eval_df %>%
#   count()

# full_df %>%
#   filter(release_type == "Zero Bail") %>%
#   count(county)

# full_df %>%
#   count(county, county)
```


##Rates of Release by Gender -- LA
```{r}
#look at ppl who do not have completed pretrial periods
#this may falsely represent pretrial releases for counties that have poor court data matching, because they may be released due to a disposition that we do not have a record of

# release_type variable may not be a reliable indicator of pretrial release, but going to try to use it here anyway just to see

gender_df <- full_df %>%
  mutate(release_cat = case_when(release_type %in% c("Cite Release", "CiteR elease", "Bail Bond", "Own Recognizance", "Pretrial Monitor", "PreTrial Monitor", "Unknown_Bail", "Zero Bail") ~ "Pretrial release type",
                                 release_type %in% c("Detain Only", "Detain only", "Dismissed", "Prison", "Time Served") ~ "Post-resolution release type",
                                 release_type %in% c("Hold Release", "Other", "Unknown") ~ "Unclear release type",
                                 T ~ "Unclear release type")) %>%
  filter(county == "Los Angeles") %>%
  mutate(pre_trial_release_flag = if_else(release_cat == "Pretrial release type", 1, 0)) %>%
  mutate(two_day_release = case_when(
    weekdays(booking_date) == "Thursday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Friday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Saturday" & release_date - booking_date <= 3 ~ 1,
    !weekdays(booking_date) %in% c("Thursday", "Friday", "Saturday") & release_date - booking_date <= 2 ~ 1,
    is.na(release_date) ~ 0,
    T ~ 0)) %>%
  mutate(quick_pretrial_type_flag = if_else(two_day_release == 1 & release_cat == "Pretrial release type", 1, 0),
         #quick_postres_type_flag = if_else(two_day_release == 1 & release_cat == "Post-resolution release type", 1, 0),
         quick_bail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         quick_zerobail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Zero Bail"), 1, 0),
         quick_cite_type_flag = if_else(two_day_release == 1 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         quick_or_type_flag = if_else(two_day_release == 1 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0),
         quick_unknown_type_flag = if_else(two_day_release == 1 & release_cat == "Unclear release type", 1, 0),
         convicted_flag = if_else(is.na(convicted_flag), 0, convicted_flag),
         #conviction = if_else(conviction_felony_flag == 1 | conviction_misd_flag == 1 | conviction_flag == 1 | convicted_flag == 1, 1, 0),
         closed_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Prison", "Time Served"), 1, 0),
         closed_not_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Detain Only", "Detain only", "Dismissed"), 1, 0),
         later_pretrial_type_flag = if_else(two_day_release == 0 & release_cat == "Pretrial release type", 1, 0),
         later_bail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         later_zerobail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Zero Bail"), 1, 0),
         later_cite_type_flag = if_else(two_day_release == 0 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         later_or_type_flag = if_else(two_day_release == 0 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0)) %>%
  group_by(county, sex) %>%
  summarise(Total = n(),
            `Charges dropped or case dismissed within 2 court days` = mean(closed_not_convicted_flag),
            `Convicted within 2 court days` = mean(closed_convicted_flag),
            #`Released - (C) Pretrial release (OR or bail) within 2 court days` = mean(pre_arraignment_flag),
            `Bail release type within 2 court days` = mean(quick_bail_type_flag),
            `Zero bail release type within 2 court days` = mean(quick_zerobail_type_flag),
            `Cite & Release release type within 2 court days` = mean(quick_cite_type_flag),
            `OR release type within 2 court days` = mean(quick_or_type_flag),
            #`Released - Post-resolution release type` = mean(quick_postres_type_flag),
            `Unclear release type (post-resolution or pretrial) within 2 court days` = mean(quick_unknown_type_flag),
            `TOTAL: Released within 2 court days` = mean(two_day_release), 
            `Bail release type after 2 days` = mean(later_bail_type_flag),
            `Zero bail release type after 2 days` = mean(later_zerobail_type_flag),
            `Cite & Release release type after 2 days` = mean(later_cite_type_flag),
            `OR release type after 2 days` = mean(later_or_type_flag)) %>%
  filter(sex %in% c("Male", "Female")) %>%
  rename(`Gender` = sex)

write.xlsx(gender_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 tables 2022/2A Gender LA.xlsx", asTable = F)

# full_df %>%
#   filter(release_eligible_count == 1) %>%
#   filter(sex %in% c("Male", "Female")) %>%
#   count()

```
\newpage

##Rates of Release by race_standard -- LA
```{r}
#look at ppl who do not have completed pretrial periods
#this may falsely represent pretrial releases for counties that have poor court data matching, because they may be released due to a disposition that we do not have a record of

# release_type variable may not be a reliable indicator of pretrial release, but going to try to use it here anyway just to see

race_standard_df <- full_df %>%
  mutate(race_standard = if_else(race_standard %in% c("White", "Black", "Hispanic", "Asian"), race_standard, "Other/Unknown")) %>%
  mutate(release_cat = case_when(release_type %in% c("Cite Release", "CiteR elease", "Bail Bond", "Own Recognizance", "Pretrial Monitor", "PreTrial Monitor", "Unknown_Bail", "Zero Bail") ~ "Pretrial release type",
                                 release_type %in% c("Detain Only", "Detain only", "Dismissed", "Prison", "Time Served") ~ "Post-resolution release type",
                                 release_type %in% c("Hold Release", "Other", "Unknown") ~ "Unclear release type",
                                 T ~ "Unclear release type")) %>%
  filter(county == "Los Angeles") %>%
  mutate(pre_trial_release_flag = if_else(release_cat == "Pretrial release type", 1, 0)) %>%
  mutate(two_day_release = case_when(
    weekdays(booking_date) == "Thursday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Friday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Saturday" & release_date - booking_date <= 3 ~ 1,
    !weekdays(booking_date) %in% c("Thursday", "Friday", "Saturday") & release_date - booking_date <= 2 ~ 1,
    is.na(release_date) ~ 0,
    T ~ 0)) %>%
  mutate(quick_pretrial_type_flag = if_else(two_day_release == 1 & release_cat == "Pretrial release type", 1, 0),
         #quick_postres_type_flag = if_else(two_day_release == 1 & release_cat == "Post-resolution release type", 1, 0),
         quick_bail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         quick_zerobail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Zero Bail"), 1, 0),
         quick_cite_type_flag = if_else(two_day_release == 1 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         quick_or_type_flag = if_else(two_day_release == 1 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0),
         quick_unknown_type_flag = if_else(two_day_release == 1 & release_cat == "Unclear release type", 1, 0),
         convicted_flag = if_else(is.na(convicted_flag), 0, convicted_flag),
         #conviction = if_else(conviction_felony_flag == 1 | conviction_misd_flag == 1 | conviction_flag == 1 | convicted_flag == 1, 1, 0),
         closed_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Prison", "Time Served"), 1, 0),
         closed_not_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Detain Only", "Detain only", "Dismissed"), 1, 0),
         later_pretrial_type_flag = if_else(two_day_release == 0 & release_cat == "Pretrial release type", 1, 0),
         later_bail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         later_zerobail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Zero Bail"), 1, 0),
         later_cite_type_flag = if_else(two_day_release == 0 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         later_or_type_flag = if_else(two_day_release == 0 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0)) %>%
  group_by(county, race_standard) %>%
  summarise(Total = n(),
            `Charges dropped or case dismissed within 2 court days` = mean(closed_not_convicted_flag),
            `Convicted within 2 court days` = mean(closed_convicted_flag),
            #`Released - (C) Pretrial release (OR or bail) within 2 court days` = mean(pre_arraignment_flag),
            `Bail release type within 2 court days` = mean(quick_bail_type_flag),
            `Zero bail release type within 2 court days` = mean(quick_zerobail_type_flag),
            `Cite & Release release type within 2 court days` = mean(quick_cite_type_flag),
            `OR release type within 2 court days` = mean(quick_or_type_flag),
            #`Released - Post-resolution release type` = mean(quick_postres_type_flag),
            `Unclear release type (post-resolution or pretrial) within 2 court days` = mean(quick_unknown_type_flag),
            `TOTAL: Released within 2 court days` = mean(two_day_release), 
            `Bail release type after 2 days` = mean(later_bail_type_flag),
            `Zero bail release type after 2 days` = mean(later_zerobail_type_flag),
            `Cite & Release release type after 2 days` = mean(later_cite_type_flag),
            `OR release type after 2 days` = mean(later_or_type_flag)) %>%
  rename(`Race` = race_standard) 

write.xlsx(race_standard_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 tables 2022/2A race_standard LA final.xlsx", asTable = F)

# full_df %>%
#   filter(release_eligible_count == 1) %>%
#   filter(race_standard %in% c("White", "Black", "Hispanic")) %>%
#   count()

```
\newpage


\newpage
## Rates of Release by Offense Type -- LA
```{r}
#look at ppl who do not have completed pretrial periods
#this may falsely represent pretrial releases for counties that have poor court data matching, because they may be released due to a disposition that we do not have a record of

# release_type variable may not be a reliable indicator of pretrial release, but going to try to use it here anyway just to see

charge_level_df <- full_df %>%
  mutate(charge_level = charge_level_standard) %>%
  mutate(release_cat = case_when(release_type %in% c("Cite Release", "CiteR elease", "Bail Bond", "Own Recognizance", "Pretrial Monitor", "PreTrial Monitor", "Unknown_Bail", "Zero Bail") ~ "Pretrial release type",
                                 release_type %in% c("Detain Only", "Detain only", "Dismissed", "Prison", "Time Served") ~ "Post-resolution release type",
                                 release_type %in% c("Hold Release", "Other", "Unknown") ~ "Unclear release type",
                                 T ~ "Unclear release type")) %>%
  filter(county == "Los Angeles") %>%
  mutate(pre_trial_release_flag = if_else(release_cat == "Pretrial release type", 1, 0)) %>%
  mutate(two_day_release = case_when(
    weekdays(booking_date) == "Thursday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Friday" & release_date - booking_date <= 4 ~ 1,
    weekdays(booking_date) == "Saturday" & release_date - booking_date <= 3 ~ 1,
    !weekdays(booking_date) %in% c("Thursday", "Friday", "Saturday") & release_date - booking_date <= 2 ~ 1,
    is.na(release_date) ~ 0,
    T ~ 0)) %>%
  mutate(quick_pretrial_type_flag = if_else(two_day_release == 1 & release_cat == "Pretrial release type", 1, 0),
         #quick_postres_type_flag = if_else(two_day_release == 1 & release_cat == "Post-resolution release type", 1, 0),
         quick_bail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         quick_zerobail_type_flag = if_else(two_day_release == 1 & release_type %in% c("Zero Bail"), 1, 0),
         quick_cite_type_flag = if_else(two_day_release == 1 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         quick_or_type_flag = if_else(two_day_release == 1 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0),
         quick_unknown_type_flag = if_else(two_day_release == 1 & release_cat == "Unclear release type", 1, 0),
         convicted_flag = if_else(is.na(convicted_flag), 0, convicted_flag),
         #conviction = if_else(conviction_felony_flag == 1 | conviction_misd_flag == 1 | conviction_flag == 1 | convicted_flag == 1, 1, 0),
         closed_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Prison", "Time Served"), 1, 0),
         closed_not_convicted_flag = if_else(two_day_release == 1 & release_type %in% c("Detain Only", "Detain only", "Dismissed"), 1, 0),
         later_pretrial_type_flag = if_else(two_day_release == 0 & release_cat == "Pretrial release type", 1, 0),
         later_bail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Bail Bond", "Unknown_Bail"), 1, 0),
         later_zerobail_type_flag = if_else(two_day_release == 0 & release_type %in% c("Zero Bail"), 1, 0),
         later_cite_type_flag = if_else(two_day_release == 0 & release_type %in% c("Cite Release", "CiteR elease"), 1, 0),
         later_or_type_flag = if_else(two_day_release == 0 & release_type %in% c("Own Recognizance", "Pretrial Monitor", "PreTrial Monitor"), 1, 0)) %>%
  group_by(county, charge_level) %>%
  summarise(Total = n(),
            `Charges dropped or case dismissed within 2 court days` = mean(closed_not_convicted_flag),
            `Convicted within 2 court days` = mean(closed_convicted_flag),
            #`Released - (C) Pretrial release (OR or bail) within 2 court days` = mean(pre_arraignment_flag),
            `Bail release type within 2 court days` = mean(quick_bail_type_flag),
            `Zero bail release type within 2 court days` = mean(quick_zerobail_type_flag),
            `Cite & Release release type within 2 court days` = mean(quick_cite_type_flag),
            `OR release type within 2 court days` = mean(quick_or_type_flag),
            #`Released - Post-resolution release type` = mean(quick_postres_type_flag),
            `Unclear release type (post-resolution or pretrial) within 2 court days` = mean(quick_unknown_type_flag),
            `TOTAL: Released within 2 court days` = mean(two_day_release), 
            `Bail release type after 2 days` = mean(later_bail_type_flag),
            `Zero bail release type after 2 days` = mean(later_zerobail_type_flag),
            `Cite & Release release type after 2 days` = mean(later_cite_type_flag),
            `OR release type after 2 days` = mean(later_or_type_flag)) %>%
  mutate(charge_level = case_when(charge_level %in% c("M", "Misdemeanor") ~ "Misdemeanor",
                                  charge_level %in% c("F", "Felony") ~ "Felony",
                                  T ~ "Other")) %>%
  filter(charge_level %in% c("Felony", "Misdemeanor")) %>%
  rename(`Arrest Charge Level` = charge_level) %>%
  arrange(desc(`Arrest Charge Level`))

write.xlsx(charge_level_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 tables 2022/2A Offense Type LA final.xlsx", asTable = F)

# full_df %>%
#   filter(release_eligible_count == 1) %>%
#   filter(charge_level %in% c("Felony", "Misdemeanor")) %>%
#   count()

# full_df %>%
#   count(county, book_type_original, release_eligible_count)
# 
# full_df %>%
#   count(county, book_type, book_type_original, release_eligible_count)
# 
# full_df %>%
#   filter(county == "Modoc") %>%
#   count(release_eligible_count)
# 
# eval_df %>%
#   count()

# full_df %>%
#   filter(release_type == "Zero Bail") %>%
#   count(county)

```


## Table 4
```{r}
fta_df <- eval_df %>%
  # filter(tool_name %in% c(""))
  filter(charge_level %in% c("M", "F")) %>%
  mutate(risk_level = case_when(
    vprai_risk_score %in% 5:9|vprair_risk_score %in% 9:14|oras_risk_score %in% 6:9|
      psa_fta_risk_score %in% 5:6 ~ "Higher Scores",
    vprai_risk_score %in% 3:4|vprair_risk_score %in% 5:8|oras_risk_score %in% 3:5|
      psa_fta_risk_score %in% 3:4 ~ "Middle Scores",
    vprai_risk_score %in% 0:2|vprair_risk_score %in% 0:4|oras_risk_score %in% 0:2|
      psa_fta_risk_score %in% 1:2 ~ "Lower Scores",
    T ~ "Other_Unknown")) %>%
  mutate(release_type = if_else(!release_type %in% c("Zero Bail", "Bail Bond") & !is.na(assessment_date), 
                                "Assessed_Release", release_type)) %>%
  filter(release_type %in% c("Zero Bail", "Bail Bond", "Assessed_Release")) %>%
  
  mutate(risk_level = if_else(risk_level %in% c("Other", "Unknown")|is.na(risk_level), "Other_Unknown", risk_level),
         risk_level = if_else(release_type %in% c("Zero Bail", "Bail Bond"), release_type, risk_level)) %>%
  group_by(county, risk_level, charge_level) %>%
  summarise(Total = n(), `Court Appearance Rate` = paste(round(100-mean(fta_flag)*100), "%")) %>%
  mutate(risk_level = factor(risk_level, levels =  c("Lower Scores", "Middle Scores", "Higher Scores", "Other_Unknown", "Zero Bail", "Bail Bond" ))) %>%
  arrange(county, charge_level, risk_level) %>%
  mutate(across(matches("Total|Count$|Rate|Perc"), ~if_else(Total < 30 & Total >= 1, "< 30", as.character(.x))))

names(fta_df) <- c("County", "Release Type/Risk Level", "Offense Type", "Total", "Court Appearance Rate")
  
write.xlsx(fta_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/2022 SB 36 Static Output Tables/2B.xlsx", asTable = T)

# Aggregated
fta_df <- eval_df %>%
  # filter(tool_name %in% c(""))
  filter(charge_level %in% c("M", "F")) %>%
  mutate(risk_level = case_when(
    vprai_risk_score %in% 5:9|vprair_risk_score %in% 9:14|oras_risk_score %in% 6:9|
      psa_fta_risk_score %in% 5:6 ~ "Higher Scores",
    vprai_risk_score %in% 3:4|vprair_risk_score %in% 5:8|oras_risk_score %in% 3:5|
      psa_fta_risk_score %in% 3:4 ~ "Middle Scores",
    vprai_risk_score %in% 0:2|vprair_risk_score %in% 0:4|oras_risk_score %in% 0:2|
      psa_fta_risk_score %in% 1:2 ~ "Lower Scores",
    T ~ "Other_Unknown")) %>%
  mutate(release_type = if_else(!release_type %in% c("Zero Bail", "Bail Bond" ) & !is.na(assessment_date), 
                                "Assessed_Release", release_type)) %>%
  filter(release_type %in% c("Zero Bail", "Bail Bond" , "Assessed_Release")) %>%
  
  mutate(risk_level = if_else(risk_level %in% c("Other", "Unknown")|is.na(risk_level), "Other_Unknown", risk_level),
         risk_level = if_else(release_type %in% c("Zero Bail", "Bail Bond" ), release_type, risk_level)) %>%
  group_by(risk_level, charge_level) %>%
  summarise(Total = n(), `Court Appearance Rate` = paste(round(100-mean(fta_flag)*100), "%")) %>%
  mutate(risk_level = factor(risk_level, levels =  c("Lower Scores", "Middle Scores", "Higher Scores", "Other_Unknown", "Zero Bail", "Bail Bond" ))) %>%
  arrange(charge_level, risk_level)

names(fta_df) <- c("Release Type/Risk Level", "Offense Type", "Total", "Court Appearance Rate")
 
write.xlsx(fta_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/2022 SB 36 Static Output Tables/2B Aggregated.xlsx", asTable = T)


# For PPT
eval_df %>%
  # filter(tool_name %in% c(""))
  mutate(risk_level = case_when(
    vprai_risk_score %in% 5:9|vprair_risk_score %in% 9:14|oras_risk_score %in% 6:9|
      psa_fta_risk_score %in% 5:6 ~ "Higher Scores",
    vprai_risk_score %in% 3:4|vprair_risk_score %in% 5:8|oras_risk_score %in% 3:5|
      psa_fta_risk_score %in% 3:4 ~ "Middle Scores",
    vprai_risk_score %in% 0:2|vprair_risk_score %in% 0:4|oras_risk_score %in% 0:2|
      psa_fta_risk_score %in% 1:2 ~ "Lower Scores",
    T ~ "Other_Unknown")) %>%
  mutate(release_type = if_else(!release_type %in% c("Zero Bail", "Bail Bond" ) & !is.na(assessment_date), 
                                "Assessed_Release", release_type)) %>%
  filter(release_type %in% c("Zero Bail", "Bail Bond" , "Assessed_Release")) %>%
  
  mutate(risk_level = if_else(risk_level %in% c("Other", "Unknown")|is.na(risk_level), "Other_Unknown", risk_level),
         risk_level = if_else(release_type %in% c("Zero Bail", "Bail Bond" ), release_type, risk_level)) %>%
  group_by(county, risk_level) %>%
  summarise(Total = n(), `Court Appearance Rate` = paste(round(100-mean(fta_flag)*100), "%")) %>%
  mutate(risk_level = factor(risk_level, levels =  c("Lower Scores", "Middle Scores", "Higher Scores", "Other_Unknown", "Zero Bail", "Bail Bond" ))) %>%
  arrange(county, risk_level) %>%
  unite(key, c(`Court Appearance Rate`, Total), sep = "--") %>%
  pivot_wider(names_from = "risk_level", values_from = c("key"), values_fill = "-") %>%
  View()

eval_df %>%
  count(tool_name)
  filter(release_type == "Unknown_Bail") %>%
  count(county)
```

## Table 5 
```{r}
new_charge_df <- eval_df %>%
  # filter(tool_name %in% c(""))
  mutate(risk_level = case_when(
    vprai_risk_score %in% 5:9|vprair_risk_score %in% 9:14|oras_risk_score %in% 6:9|
      psa_nca_risk_score %in% 5:6 ~ "Higher Scores",
    vprai_risk_score %in% 3:4|vprair_risk_score %in% 5:8|oras_risk_score %in% 3:5|
      psa_nca_risk_score %in% 3:4 ~ "Middle Scores",
    vprai_risk_score %in% 0:2|vprair_risk_score %in% 0:4|oras_risk_score %in% 0:2|
      psa_nca_risk_score %in% 1:2 ~ "Lower Scores",
    T ~ "Other_Unknown")) %>%
  mutate(release_type = if_else(!release_type %in% c("Zero Bail", "Bail Bond" ) & !is.na(assessment_date), 
                                "Assessed_Release", release_type)) %>%
  filter(release_type %in% c("Zero Bail", "Bail Bond" , "Assessed_Release")) %>%
  # mutate(charge_level = case_when(is.na(charge_level)|charge_level %in% c("Other", "I") ~"Other_Unknown",
  #                                        charge_level == "F" ~ "Felony",
  #                                        charge_level == "M" ~ "Misdemeanor")) %>%
  mutate(risk_level = if_else(risk_level %in% c("Other", "Unknown")|is.na(risk_level), "Other_Unknown", risk_level),
         risk_level = if_else(release_type %in% c("Zero Bail", "Bail Bond" ), release_type, risk_level)) %>%
  group_by(county, risk_level, charge_level) %>%
  summarise(Total = n(), `No New Charge Rate` = paste(round(100-mean(recid_filed_flag)*100), "%")) %>%
  mutate(risk_level = factor(risk_level, levels =  c("Lower Scores", "Middle Scores", "Higher Scores", "Other_Unknown", "Zero Bail", "Bail Bond" ))) %>%
  arrange(county, charge_level, risk_level) %>%
  mutate(across(matches("Total|Count$|Rate|Perc"), ~if_else(Total < 30 & Total >=1, "< 30", as.character(.x))))

names(new_charge_df) <- c("county", "Release Type/Risk Level", "Offense Type", "Total", "No New Charge Rate")
  
write.xlsx(new_charge_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/2022 SB 36 Static Output Tables/2C.xlsx", asTable = T)

# Aggregated
new_charge_df <- eval_df %>%
  # filter(tool_name %in% c(""))
  mutate(risk_level = case_when(
    vprai_risk_score %in% 5:9|vprair_risk_score %in% 9:14|oras_risk_score %in% 6:9|
      psa_nca_risk_score %in% 5:6 ~ "Higher Scores",
    vprai_risk_score %in% 3:4|vprair_risk_score %in% 5:8|oras_risk_score %in% 3:5|
      psa_nca_risk_score %in% 3:4 ~ "Middle Scores",
    vprai_risk_score %in% 0:2|vprair_risk_score %in% 0:4|oras_risk_score %in% 0:2|
      psa_nca_risk_score %in% 1:2 ~ "Lower Scores",
    T ~ "Other_Unknown")) %>%
  mutate(release_type = if_else(!release_type %in% c("Zero Bail", "Bail Bond" ) & !is.na(assessment_date), 
                                "Assessed_Release", release_type)) %>%
  filter(release_type %in% c("Zero Bail", "Bail Bond" , "Assessed_Release")) %>%
  # mutate(charge_level = case_when(is.na(charge_level)|charge_level %in% c("Other", "I") ~"Other_Unknown",
  #                                        charge_level == "F" ~ "Felony",
  #                                        charge_level == "M" ~ "Misdemeanor")) %>%
  mutate(risk_level = if_else(risk_level %in% c("Other", "Unknown")|is.na(risk_level), "Other_Unknown", risk_level),
         risk_level = if_else(release_type %in% c("Zero Bail", "Bail Bond" ), release_type, risk_level)) %>%
  group_by(risk_level, charge_level) %>%
  summarise(Total = n(), `No New Charge Rate` = paste(round(100-mean(recid_filed_flag)*100), "%")) %>%
  mutate(risk_level = factor(risk_level, levels =  c("Lower Scores", "Middle Scores", "Higher Scores", "Other_Unknown", "Zero Bail", "Bail Bond" ))) %>%
  arrange(charge_level, risk_level)

names(new_charge_df) <- c("Release Type/Risk Level", "Offense Type", "Total", "No New Charge Rate")

write.xlsx(new_charge_df, file = "G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/2022 SB 36 Static Output Tables/2C Aggregated.xlsx", asTable = T)

# For PPT
eval_df %>%
  # filter(!is.na(cii),
  #        pretrial_end_date - release_date >= 60) %>%
  mutate(risk_level = case_when(
    vprai_risk_score %in% 5:9|vprair_risk_score %in% 9:14|oras_risk_score %in% 6:9|
      psa_nca_risk_score %in% 5:6 ~ "Higher Scores",
    vprai_risk_score %in% 3:4|vprair_risk_score %in% 5:8|oras_risk_score %in% 3:5|
      psa_nca_risk_score %in% 3:4 ~ "Middle Scores",
    vprai_risk_score %in% 0:2|vprair_risk_score %in% 0:4|oras_risk_score %in% 0:2|
      psa_nca_risk_score %in% 1:2 ~ "Lower Scores",
    T ~ "Other_Unknown")) %>%
  mutate(release_type = if_else(!release_type %in% c("Zero Bail", "Bail Bond" ) & !is.na(assessment_date), 
                                "Assessed_Release", release_type)) %>%
  filter(release_type %in% c("Zero Bail", "Bail Bond" , "Assessed_Release")) %>%
  mutate(charge_level = case_when(is.na(charge_level)|charge_level %in% c("Other", "I") ~"Other_Unknown",
                                         charge_level == "F" ~ "Felony",
                                         charge_level == "M" ~ "Misdemeanor")) %>%
  mutate(risk_level = if_else(risk_level %in% c("Other", "Unknown")|is.na(risk_level), "Other_Unknown", risk_level),
         risk_level = if_else(release_type %in% c("Zero Bail", "Bail Bond" ), release_type, risk_level)) %>%
  group_by(county, risk_level) %>%
  summarise(Total = n(), `No New Charge Rate` = paste(round(100- mean(recid_arrested_flag)*100), "%")) %>%
  mutate(risk_level = factor(risk_level, levels =  c("Lower Scores", "Middle Scores", "Higher Scores", "Other_Unknown", "Zero Bail", "Bail Bond" ))) %>%
  arrange(county, risk_level) %>%
  unite(key, c(`No New Charge Rate`, Total), sep = "--") %>%
  pivot_wider(names_from = "risk_level", values_from = c("key"), values_fill = "-")  %>%
  View()

# eval_df %>%
#   filter(!is.na(cii)) %>%
#   mutate(recid_filed_flag = if_else(!is.na(recid_date), 1, 0)) %>%
#   summarise(recid_filed_flag = mean(recid_filed_flag))
#   select(contains("recid")) %>%
#   View()
#   summarise(across(c(recid_arrested_flag, recid_filed_flag, recid_convicted_flag), mean))
```