---
title: "AB 74 Feb 2021 Output Tables"
author: "Noah Lehman and Sal Lempert"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r include=FALSE}
library(janitor)
library(tidyverse)
library(lubridate)
library(scales)
library(pROC)
library(kableExtra)
library(stargazer)
library(data.table)
library(ggthemes)

```


```{r include=FALSE}
my_kable <- function(x){
  kable(x, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14) %>%
    row_spec(nrow(x), bold = T)
    # column_spec(2, bold = T)
  # footnote(general_title = "", general = "Source: Judicial Council of California, Recidivism Reduction Fund Quarterly Reports (July 1, 2015-March 31, 2018).")  %>%
    
}

# Age Creator
  # mutate(dob = as_date(dob),
  #        assessment_date = as_date(assessment_date)) %>%
  # mutate(age = year(assessment_date) - year(dob),
  #        age = if_else(month(assessment_date) < month(dob), age - 1L, age),
  #        age = if_else(month(assessment_date) == month(dob) & day(assessment_date) < day(dob), age - 1L, age))


```


```{r include=FALSE}
# load("G:/CrimJustice/PretrialAssessmentPilot/Assessment Output Tables" "Assessment Output Data Frame 03-2021.RData")
# 
# 
# # Removing local tools and unrelated tools.
# df <- df %>%
#   mutate(tool_name = if_else(tool_name %in% c("sprat", "tuol_co_pretrial"), "local", tool_name)) %>%
#   filter(!tool_name %in% c("modified wisconsin")) %>%
#   mutate(across(c(psa_nca_risk_score, psa_fta_risk_score), ~if_else(.x > 6 | .x < 1, NA_real_, .x))) %>%
#   mutate(tool_name = if_else(is.na(tool_name), "vprair", tool_name))

# save(df, file = "C:/Work/PretrialAssessmentPilot/Pretrial-Pilot-County-Analysis/Assessment Output Data Frame v2.RData")
# 
# df %>%
#   group_by(county) %>%
#   summarise(min_assessment_date = min(assessment_date),
#             max_assessment_date = max(assessment_date)) %>%
#   View()

# df %>%
#   count(tool_name)

load("G:/CrimJustice/PretrialAssessmentPilot/Final Failure Evaluation2.RData")
# load("Final Failure Evaluation.RData")

eval_df <- eval_df %>%
  filter(!is.na(cii)) %>%
  mutate(monitor_level = case_when(
    monitor_level %in% c("Level I - Pretrial Release Supervision",
                                     "Pretrial Supervision Level I", "1", "Low") ~ "Low",
    monitor_level %in% c("Level II - Pretrial Release Supervision",
                                     "Pretrial Supervision Level II", "2", "Medium") ~ "Medium",
    monitor_level %in% c("Level III - Pretrial Release Supervision",
                                     "Pretrial Supervision Level III", "3:4", "High") ~ "High",
                              T ~ monitor_level)) %>%
  mutate(fta_flag = if_else(fta_flag == 1|arrest_fta_flag == 1|court_fta_flag == 1|court_fta_flag_doj == 1, 1, 0),
         revoked_flag = if_else(pretrial_termination_outcome == "Unsuccessful", 1, 0),
         oras_risk_score = if_else(oras_risk_score == -Inf, NA_real_, oras_risk_score)) %>%
  mutate(monitor_level = factor(monitor_level, levels = c("Low", "Medium", "High", "Other_Unknown")))
```
\newpage

# AB 74: Tables

16. (d) The number and percentage of assessed individuals by supervision level who fail to appear in court as required, are arrested for a new offense during the pretrial period, or have pretrial release revoked.
\newpage



## Pretrial Revocations by Termination Reason and Monitor Level 
```{r message=FALSE, warning=FALSE}
eval_df <- eval_df %>%
  mutate(monitor_level = case_when(monitor_level == "Low" ~ "Basic",
                                   monitor_level == "Medium" ~ "Moderate",
                                   monitor_level == "High" ~ "Enhanced",
                                   monitor_level == "Other_Unknown" ~ "Unspecified",
                                   T ~ as.character(monitor_level))) %>%
  filter(monitor_level %in% c("Basic", "Moderate", "Enhanced")) %>%
  mutate(monitor_level = factor(monitor_level, levels =  c("Basic", "Moderate", "Enhanced"))) %>%
  filter(county != "San Joaquin") %>%
  mutate(revoked_flag = if_else(fta_flag == 1|recid_flag == 1|pretrial_termination_outcome == "Unsuccessful", 1, 0)) %>%
  mutate(revoked_flag = if_else(is.na(revoked_flag), 0, revoked_flag)) 

fta_df <- eval_df %>%
  group_by(monitor_level, fta_flag) %>%
  count() %>%
  group_by(monitor_level) %>%
  mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  spread(fta_flag, n) %>%
  select(-`0`) %>%
  bind_rows(eval_df %>%
              count(fta_flag) %>%
              mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  spread(fta_flag, n) %>%
  select(-`0`) %>%
  mutate(monitor_level = "All_Levels")) %>%
  separate(`1`, sep = " ", into = c("Percent", "Count"))

recid_df <- eval_df %>%
  group_by(monitor_level, recid_flag) %>%
  count() %>%
  group_by(monitor_level) %>%
  mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  spread(recid_flag, n) %>%
  select(-`0`) %>%
  bind_rows(eval_df %>%
              count(recid_flag) %>%
              mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  spread(recid_flag, n) %>%
  select(-`0`) %>%
  mutate(monitor_level = "All_Levels")) %>%
  separate(`1`, sep = " ", into = c("Percent", "Count"))

revoked_df <- eval_df %>%
  group_by(monitor_level, revoked_flag) %>%
  count() %>%
  group_by(monitor_level) %>%
  mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  spread(revoked_flag, n) %>%
  select(-`0`) %>%
  bind_rows(eval_df %>%
              count(revoked_flag) %>%
              mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  spread(revoked_flag, n) %>%
  select(-`0`) %>%
  mutate(monitor_level = "All_Levels")) %>%
  separate(`1`, sep = " ", into = c("Percent", "Count"))

  
outcome_df <- bind_cols(fta_df, recid_df[3:4], revoked_df[3:4]) %>%
  rename("Monitor Level" = "monitor_level")

names(outcome_df) <- gsub("\\..*", "", names(outcome_df))


kable(outcome_df, booktabs = T, format.args = list(big.mark = ","),
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = T,
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray") %>%
  add_header_above(c(" " = 2, "FTA" = 2, "New Crime" = 2,
                     "Total FTA, New Crime,\n or Revocation" = 2)) %>%
  column_spec(2:10, width = ".5in") %>%
  column_spec(1, width = "1in") %>%
  row_spec(5, bold = T)
```
Notes: For counties which use discrete supervision levels, supervision levels were collapsed into 'Basic', 'Moderate', and 'Enhanced' supervision, though what each of these supervision levels mean varies widely across counties.

