---
title: "AB 74 Jan 2021 Output Tables"
author: "Noah Lehman and Sal Lempert"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r include=FALSE}
library(janitor)
library(tidyverse)
library(lubridate)
library(scales)
library(pROC)
library(kableExtra)
library(stargazer)
library(data.table)
library(ggthemes)

```


```{r include=FALSE}
my_kable <- function(x){
  kable(x, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14) %>%
    row_spec(nrow(x), bold = T)
    # column_spec(2, bold = T)
  # footnote(general_title = "", general = "Source: Judicial Council of California, Recidivism Reduction Fund Quarterly Reports (July 1, 2015-March 31, 2018).")  %>%
    
}

# Age Creator
  # mutate(dob = as_date(dob),
  #        assessment_date = as_date(assessment_date)) %>%
  # mutate(age = year(assessment_date) - year(dob),
  #        age = if_else(month(assessment_date) < month(dob), age - 1L, age),
  #        age = if_else(month(assessment_date) == month(dob) & day(assessment_date) < day(dob), age - 1L, age))


```


```{r include=FALSE}
load("C:/Work/PretrialAssessmentPilot/Pretrial-Pilot-County-Analysis/Assessment Output Data Frame v2.RData")

# save(df, file = "C:/Work/PretrialAssessmentPilot/Pretrial-Pilot-County-Analysis/Assessment Output Data Frame v2.RData")
```

\newpage

# Total Assessments by Tool 
```{r echo=FALSE}
suppressMessages(
county_df <- df %>%
  count(county, tool_name) %>%
  group_by(tool_name) %>%
  summarise(county = paste(county, collapse = ", "), Total = sum(n)) %>%
  ungroup() %>%
  mutate(tool_name = toupper(tool_name))
)

names(county_df) <- c("Tool Name", "County", "Assessments")

kable(county_df, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14)
```


```{r include=FALSE}
df <- df %>%
  rename("County" = county) %>%
  mutate_if(is.character, funs(if_else(. == "Other_Unknown", "Other", .))) %>%
  mutate(la_flag = if_else(County == "Los Angeles", 1, 0)) %>%
  mutate(County = case_when(
    County %in% c("Sacramento", "Alameda", "Los Angeles") ~ "Large",
    County %in% c("Sonoma", "San Joaquin", "San Mateo", "Tulare", "Santa Barbara", "Ventura") ~ "Medium",
    County %in% c("Yuba", "Nevada", "Napa", "Kings") ~ "Small/Medium",
    County %in% c("Sierra", "Modoc", "Calaveras", "Tuolumne") ~ "Small",
    T ~ County))%>% 
  mutate(County = ordered(County, levels = c("Small", "Small/Medium", "Medium", "Large"))) %>%
  arrange(County)
```
\newpage


# AB 74: Tables
16.
(a) The number of assessed individuals by age, gender, and race or ethnicity.
(b) The number of assessed individuals by risk level, booking charge levels, and release decision
(c) The number and percentage of assessed individuals who receive pretrial supervision by level of supervision.
(d) The number and percentage of assessed individuals by supervision level who fail to appear in court as required, are arrested for a new offense during the pretrial period, or have pretrial release revoked.

\newpage

# AB 74: Tables
16. (a) The number of assessed individuals by age, gender, and race or ethnicity.
\newpage

## The Number of Assessed Individuals by Age
```{r}
age_df <- df %>%
  count(County, age) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  age, values_from =  n, values_fill = 0) %>%
  select("County Size" = County, `18-25`, `26-35`, `36-45`, `46-55`, `56+`,  "Unknown" = Other, Total) %>%
  bind_rows(df %>%
              count(age) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  age, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select("County Size" = County, `18-25`, `26-35`, `36-45`, `46-55`, `56+`, "Unknown" = Other, Total))

my_kable(age_df)
```
\newpage

## The Number of Assessed Individuals by Gender
```{r}
gender_df <- df %>%
  count(County, sex) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  sex, values_from =  n, values_fill = 0) %>%
  select("County Size" = County, Male, Female, "Other/Unknown" = Other, Total) %>%
  bind_rows(df %>%
              count(sex) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  sex, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select("County Size" = County, Male, Female, "Other/Unknown" = Other, Total))

my_kable(gender_df)
```
\newpage

## The Number of Assessed Individuals by Race
```{r}
race_df <- df %>%
  count(County, race) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  race, values_from =  n, values_fill = 0) %>%
  select("County Size" = County, Black, White, Hispanic, "Other/Unknown" = Other, Total) %>%
  bind_rows(df %>%
              count(race) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  race, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select("County Size" = County, Black, White, Hispanic, "Other/Unknown" = Other, Total))

my_kable(race_df)
```
\newpage



# AB 74: Tables

16. (b) The number of assessed individuals by risk level, booking charge levels, and release decision
\newpage

## The Number of Assessed Individuals by Risk Score (ORAS)
```{r}
risk_df_oras <- df %>%
  filter(tool_name == "oras") %>%
  count(oras_risk_score) %>%
  mutate(oras_risk_score = as.character(oras_risk_score)) %>%
  bind_rows(df %>% filter(tool_name == "oras") %>% count() %>% mutate(oras_risk_score = "Total"))
  
names(risk_df_oras) <- c("ORAS Risk Score", "Count")
  
my_kable(risk_df_oras)
```
Notes: This table includes data from five counties (Modoc, Napa, Nevada, Ventura, Yuba).
\newpage

## The Number of Assessed Individuals by Risk Score (VPRAI)
```{r}
risk_df_vprai <- df %>%
  filter(tool_name == "vprai") %>%
  count(vprai_risk_score) %>%
  mutate(vprai_risk_score = as.character(vprai_risk_score)) %>%
  bind_rows(df %>% filter(tool_name == "vprai") %>% count() %>% mutate(vprai_risk_score = "Total"))
  
names(risk_df_vprai) <- c("VPRAI Risk Score", "Count")
  
my_kable(risk_df_vprai)
```
Notes: This table includes data from two counties (San Joaquin, Santa Barbara).
\newpage

## The Number of Assessed Individuals by Risk Score (VPRAI-R)
```{r}
risk_df_vprair <- df %>%
  filter(tool_name == "vprair") %>%
  count(vprair_risk_score) %>%
  mutate(vprair_risk_score = as.character(vprair_risk_score)) %>%
  bind_rows(df %>% filter(tool_name == "vprair") %>% count() %>% mutate(vprair_risk_score = "Total"))
  
names(risk_df_vprair) <- c("VPRAI-R Risk Score", "Count")
  
my_kable(risk_df_vprair)
```
Notes: This table includes data from two counties (Alameda, San Mateo, Santa Barbara).
\newpage

## The Number of Assessed Individuals by Risk Score (VPRAI-O)
```{r}
risk_df_vpraio <- df %>%
  filter(tool_name == "vpraio") %>%
  count(vpraio_risk_score) %>%
  mutate(vpraio_risk_score = as.character(vpraio_risk_score)) %>%
  bind_rows(df %>% filter(tool_name == "vpraio") %>% count() %>% mutate(vpraio_risk_score = "Total"))
  
names(risk_df_vpraio) <- c("VPRAI-O Risk Score", "Count")
  
my_kable(risk_df_vpraio)
```
Notes: This table includes data from one county (Kings).
\newpage

## The Number of Assessed Individuals by Risk Score (PSA FTA)
```{r}
risk_df_psa_fta <- df %>%
  filter(tool_name == "psa") %>%
  count(psa_fta_risk_score) %>%
  mutate(psa_fta_risk_score = as.character(psa_fta_risk_score)) %>%
  bind_rows(df %>% filter(tool_name == "psa") %>% count() %>% mutate(psa_fta_risk_score = "Total"))
  
names(risk_df_psa_fta) <- c("PSA FTA Risk Score", "Count")
  
my_kable(risk_df_psa_fta)
```
Notes: This table includes data from five counties (Calaveras, Los Angeles, Sacramento, Tulare, Tuolumne).
\newpage

## The Number of Assessed Individuals by Risk Score (PSA New Criminal Activity)
```{r}
risk_df_psa_nca <- df %>%
  filter(tool_name == "psa", psa_nca_risk_score != 9) %>%
  count(psa_nca_risk_score) %>%
  mutate(psa_nca_risk_score = as.character(psa_nca_risk_score)) %>%
  bind_rows(df %>% filter(tool_name == "psa") %>% count() %>% mutate(psa_nca_risk_score = "Total"))
  
names(risk_df_psa_nca) <- c("PSA NCA Risk Score", "Count")
  
my_kable(risk_df_psa_nca)
```
Notes: This table includes data from five counties (Calaveras, Los Angeles, Sacramento, Tulare, Tuolumne).
\newpage

## The Number of Assessed Individuals by Risk Score (PSA New Violent Criminal Activity)
```{r}
risk_df_psa_nvca <- df %>%
  filter(tool_name == "psa", psa_nvca_risk_score != 9) %>%
  count(psa_nvca_risk_score) %>%
  mutate(psa_nvca_risk_score = as.character(psa_nvca_risk_score)) %>%
  bind_rows(df %>% filter(tool_name == "psa") %>% count() %>% mutate(psa_nvca_risk_score = "Total"))
  
names(risk_df_psa_nvca) <- c("PSA NVCA Risk Score", "Count")
  
my_kable(risk_df_psa_nvca)
```
Notes: This table includes data from five counties (Calaveras, Los Angeles, Sacramento, Tulare, Tuolumne).
\newpage

## The Number of Assessed Individuals by Risk Score (SPRAT)
```{r}
risk_df_sprat <- df %>%
  filter(tool_name == "sprat") %>%
  count(sprat_risk_score) %>%
  mutate(sprat_risk_score = as.character(sprat_risk_score)) %>%
  bind_rows(df %>% filter(tool_name == "sprat") %>% count() %>% mutate(sprat_risk_score = "Total"))
  
names(risk_df_sprat) <- c("SPRAT Risk Score", "Count")
  
my_kable(risk_df_sprat)
```
Notes: This table includes data from one county (Sonoma).
\newpage

## The Number of Assessed Individuals by Booking Charge Level
```{r}
# charge_level_df <- df %>%
#   count(County, charge_level) %>%
#   group_by(County) %>%
#   mutate(Total = sum(n)) %>%
#   pivot_wider(names_from =  charge_level, values_from =  n, values_fill = 0) %>%
#   select(County, Felony, Misdemeanor, Other, Total) %>%
#   bind_rows(df %>%
#               count(charge_level) %>%
#               mutate(Total = sum(n)) %>%
#               pivot_wider(names_from =  charge_level, values_from =  n, values_fill = 0) %>%
#               mutate(County = "Total") %>%
#               select(County, Felony, Misdemeanor, Other, Total))
# 
# my_kable(charge_level_df)
```
Notes: Booking charge level is reported in a seperate data source from assessment data. Data on this measure is currently unavailable but will be provided in future reports. 
\newpage

## The Number of Assessed Individuals by Pretrial Program Release Decision
```{r}
release_df <- df %>%
  filter(la_flag == 0) %>%
  mutate(release_decision = if_else(release_decision == "Monitor", "OR", release_decision)) %>%
  count(County, release_decision) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  release_decision, values_from =  n, values_fill = 0) %>%
  select(County, Detain, OR, Other, Total) %>%
  bind_rows(df %>%
              filter(la_flag == 0) %>%
              mutate(release_decision = if_else(release_decision == "Monitor", "OR", release_decision)) %>%
              count(release_decision) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  release_decision, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select(County, Detain, OR, Other, Total))

release_df <- release_df[c(1,3,2)]

names(release_df) <- c("County Size", "Granted Program Release", "Denied Program Release")

my_kable(release_df) %>%
  column_spec(2:3, width = "2in") 
  # column_spec(4, width = "2in")
```
Notes: 'Release Denied' indicates individuals who judicial officers did not choose to release through the pretrial program. These individuals may still have gotten out on bail. 'Release Approved' includes individuals released on OR or monitoring. 'Bail/Zero Bail/Ineligible/Other' includes individuals who bailed out, who were released on zero bail, whose charges were dropped or dismissed, who were held for other reasons, and who are missing release decision data. Total Other = 17,858. Total = 28,516  
\newpage

## The Number of Assessed Individuals by Pre-Arraignment Program Release Decision
```{r}
release_df <- df %>%
  filter(la_flag == 1) %>%
  mutate(release_decision = if_else(release_decision == "Monitor", "OR", release_decision)) %>%
  count(County, release_decision) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  release_decision, values_from =  n, values_fill = 0) %>%
  select(County, Detain, OR, Other, Total) %>%
  bind_rows(df %>%
              filter(la_flag == 1) %>%
              mutate(release_decision = if_else(release_decision == "Monitor", "OR", release_decision)) %>%
              count(release_decision) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  release_decision, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select(County, Detain, OR, Other, Total))

release_df <- release_df[1, c(1,3,2)] %>%
  mutate(County = "Los Angeles")

names(release_df) <- c("County", "Granted Prearraignment Program Release",
                       "Denied Prearraignment Program Release")



 kable(release_df, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14) %>% 
  column_spec(2:3, width = "2.2in") 
```
Notes: 'Release Denied' indicates individuals who judicial officers did not choose to release through the pretrial program. These individuals may still have gotten out on bail. 'Release Approved' includes individuals released on OR or monitoring. 'Bail/Zero Bail/Ineligible/Other' includes individuals who bailed out, who were released on zero bail, whose charges were dropped or dismissed, who were held for other reasons, and who are missing release decision data.
Total Other = 15,158. Total = 24,388
\newpage
# AB 74: Tables

16. (c) The number and percentage of assessed individuals who receive pretrial supervision by level of supervision
\newpage


## The Number and Percentage of Assessed and Supervised Individuals by Supervision Level
```{r warning=FALSE}
monitor_df <- df %>%
  filter(release_decision == "Monitor") %>%
  count(County, monitor_level) %>%
  group_by(County) %>%
  mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  pivot_wider(names_from =  monitor_level, values_from =  n, values_fill = "-") %>%
  select(County, Low, Medium, High, Other, Total) %>%
  bind_rows(df %>%
              filter(release_decision == "Monitor") %>%
              count(monitor_level) %>%
              mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
              pivot_wider(names_from =  monitor_level, values_from =  n, values_fill = "-")) %>%
  ungroup() %>%
  mutate(County = if_else(is.na(County), "Total", as.character(County))) %>%
  # mutate(tool_name=toupper(tool_name),
         # tool_name= gsub("CO_", "", tool_name)) %>%
  select("County" = County, Total, Low, Medium, High, Other) %>%
  separate(Low, c("Percent_low", "Count_low"), sep = " ") %>%
  separate(Medium, c("Percent_med", "Count_med"), sep = " ") %>%
  separate(High, c("Percent_high", "Count_high"), sep = " ") %>%
  separate(Other, c("Percent_other", "Count_other"), sep = " ") %>%
  ungroup() %>%
  mutate_if(is.character, funs(if_else(is.na(.), "-", .))) %>%
  rename("County Size" = County)

names(monitor_df) <- gsub("_.*", "", names(monitor_df))
  

kable(monitor_df, booktabs = T, format.args = list(big.mark = ","),
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = T,
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray") %>%
  add_header_above(c(" " = 2, "Basic" = 2, "Moderate" = 2, "Enhanced" = 2, "Unspecified Supervision" = 2)) %>%
  row_spec(5, bold = T)
```
Notes: 'Unspecified Supervision' includes individuals in counties which do not categorize supervision conditions into discrete levels. For counties which use discrete supervision levels, supervision levels were collapsed into 'Basic', 'Moderate', and 'Enhanced' supervision, though what each of these supervision levels mean varies widely across counties.
\newpage

# AB 74: Tables

16. (d) The number and percentage of assessed individuals by supervision level who fail to appear in court as required, are arrested for a new offense during the pretrial period, or have pretrial release revoked.
\newpage



## Pretrial Revocations by Termination Reason and Monitor Level 
```{r warning=FALSE}
outcome_df <- df %>%
  filter(release_decision == "Monitor") %>%
  # mutate(total_revoked = if_else(pretrial_termination_reason != "Other", "Total Revoked", "Other")) %>%
  mutate(monitor_level = factor(monitor_level, levels = c("Low", "Medium", "High", "Other"))) %>%
  count(pretrial_termination_reason, monitor_level) %>%
  group_by(monitor_level) %>%
  mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  filter(pretrial_termination_reason != "Other") %>%
  # unite(pretrial_termination_reason, c(monitor_level, pretrial_termination_reason)) %>%
  arrange(pretrial_termination_reason) %>%
  pivot_wider(names_from =  pretrial_termination_reason, values_from =  n, values_fill = "-") %>%
  arrange(monitor_level) %>%
  bind_rows(df %>%
              filter(release_decision == "Monitor") %>%
              count(pretrial_termination_reason) %>%
              mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
              filter(pretrial_termination_reason != "Other") %>%
              arrange(pretrial_termination_reason) %>%
              mutate(monitor_level = "All_Levels") %>%
              pivot_wider(names_from =  pretrial_termination_reason, values_from =  n, values_fill = "-")) %>%
  separate(FTA, c("Percent_low", "Count_low"), sep = " ") %>%
  separate(New_Crime, c("Percent_med", "Count_med"), sep = " ") %>%
  separate(Revoked, c("Percent_high", "Count_high"), sep = " ") %>%
  ungroup() %>%
  mutate_if(is.character, funs(if_else(is.na(.), "-", .))) %>%
  mutate(monitor_level = case_when(monitor_level == "Low" ~ "Basic",
                                   monitor_level == "Medium" ~ "Moderate",
                                   monitor_level == "High" ~ "Enhanced",
                                   monitor_level == "Other" ~ "Unspecified",
                                   T ~ as.character(monitor_level))) %>%
  rename("Monitor Level" = monitor_level) 

names(outcome_df) <- gsub("_.*", "", names(outcome_df))

outcome_df2 <- df %>%
  filter(release_decision == "Monitor") %>%
  mutate(pretrial_termination_reason = if_else(pretrial_termination_reason != "Other", "Total Revoked", "Other")) %>%
  mutate(monitor_level = factor(monitor_level, levels = c("Low", "Medium", "High", "Other"))) %>%
  count(pretrial_termination_reason, monitor_level) %>%
  group_by(monitor_level) %>%
  mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  filter(pretrial_termination_reason != "Other") %>%
  # unite(pretrial_termination_reason, c(monitor_level, pretrial_termination_reason)) %>%
  arrange(pretrial_termination_reason) %>%
  pivot_wider(names_from =  pretrial_termination_reason, values_from =  n, values_fill = "-") %>%
  arrange(monitor_level) %>%
  bind_rows(df %>%
              filter(release_decision == "Monitor") %>%
              mutate(pretrial_termination_reason = if_else(pretrial_termination_reason != "Other", 
                                                            "Total Revoked", "Other")) %>%
              count(pretrial_termination_reason) %>%
              mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
              filter(pretrial_termination_reason != "Other") %>%
              arrange(pretrial_termination_reason) %>%
              mutate(monitor_level = "All_Levels") %>%
              pivot_wider(names_from =  pretrial_termination_reason, values_from =  n, values_fill = "-")) %>%
  separate(`Total Revoked`, c("Percent_low", "Count_low"), sep = " ") %>%
  ungroup() %>%
  mutate_if(is.character, funs(if_else(is.na(.), "-", .))) %>%
  mutate(monitor_level = case_when(monitor_level == "Low" ~ "Basic",
                                   monitor_level == "Medium" ~ "Moderate",
                                   monitor_level == "High" ~ "Enhanced",
                                   monitor_level == "Other" ~ "Unspecified",
                                   T ~ as.character(monitor_level))) %>%
  rename("Monitor Level" = monitor_level) 

outcome_df2 <- outcome_df2[3:4]

names(outcome_df2) <- gsub("_.*", "", names(outcome_df2))

outcome_df <- cbind(outcome_df, outcome_df2)

kable(outcome_df, booktabs = T, format.args = list(big.mark = ","),
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = T,
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray") %>%
  add_header_above(c(" " = 2, "FTA" = 2, "New Crime" = 2, "Technical Violation/\n Unknown" = 2,
                     "Total\n Revoked" = 2)) %>%
  column_spec(2:10, width = ".5in") %>%
  column_spec(1, width = "1in") %>%
  row_spec(5, bold = T)
```
Notes: 'Unspecified Supervision' includes individuals in counties which do not categorize supervision conditions into discrete levels. For counties which use discrete supervision levels, supervision levels were collapsed into 'Basic', 'Moderate', and 'Enhanced' supervision, though what each of these supervision levels mean varies widely across counties.
\linebreak

Data quality is low for failures to appear, new offenses during the pretrial period, and revocations of pretrial release. For future reports, FTA and new offense data will come from different data sources which are not currently available; probation departments keep limited records of FTA and new offenses. The data in this table includes individuals whose pretrial period is not yet complete, and may accrue adverse outcomes before completion of the pretrial period. The short time frame for this first reporting period means that that many programs have not been operational long enough to accurately measure outcomes.

