---
title: "AB 74 Jan 2021 Output Tables"
author: "Noah Lehman and Sal Lempert"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r include=FALSE}
library(janitor)
library(tidyverse)
library(lubridate)
library(scales)
library(pROC)
library(kableExtra)
library(stargazer)
library(data.table)
library(ggthemes)

```


```{r include=FALSE}
my_kable <- function(x){
  kable(x, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14) %>%
    row_spec(nrow(x), bold = T)
    # column_spec(2, bold = T)
  # footnote(general_title = "", general = "Source: Judicial Council of California, Recidivism Reduction Fund Quarterly Reports (July 1, 2015-March 31, 2018).")  %>%
    
}

# Age Creator
  # mutate(dob = as_date(dob),
  #        assessment_date = as_date(assessment_date)) %>%
  # mutate(age = year(assessment_date) - year(dob),
  #        age = if_else(month(assessment_date) < month(dob), age - 1L, age),
  #        age = if_else(month(assessment_date) == month(dob) & day(assessment_date) < day(dob), age - 1L, age))


```


```{r}
load("C:/Work/PretrialAssessmentPilot/Pretrial-Pilot-County-Analysis/Assessment Output Data Frame.RData")
```
\newpage


# AB 74: Tables
16.
(a) The number of assessed individuals by age, gender, and race or ethnicity.
(b) The number of assessed individuals by risk level, booking charge levels, and release decision
(c) The number and percentage of assessed individuals who receive pretrial supervision by level of supervision.
(d) The number and percentage of assessed individuals by supervision level who fail to appear in court as required, are arrested for a new offense during the pretrial period, or have pretrial release revoked.

\newpage

# AB 74: Tables
16. (a) The number of assessed individuals by age, gender, and race or ethnicity.

\newpage

## The Number of Assessed Individuals by Gender
```{r}
gender_df <- df %>%
  count(County, sex) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  sex, values_from =  n, values_fill = 0) %>%
  select(County, Male, Female, Other, Total) %>%
  bind_rows(df %>%
              count(sex) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  sex, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select(County, Male, Female, Other, Total))

my_kable(gender_df)
```

## The Number of Assessed Individuals by Race
```{r}
race_df <- df %>%
  count(County, race) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  race, values_from =  n, values_fill = 0) %>%
  select(County, Black, White, Hispanic, Other, Total) %>%
  bind_rows(df %>%
              count(race) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  race, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select(County, Black, White, Hispanic, Other, Total))

my_kable(race_df)
```

## The Number of Assessed Individuals by Age
```{r}
age_df <- df %>%
  count(County, age) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  age, values_from =  n, values_fill = 0) %>%
  select(County, `18-25`, `26-35`, `36-45`, `46-55`, `56+`,  Other, Total) %>%
  bind_rows(df %>%
              count(age) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  age, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select(County, `18-25`, `26-35`, `36-45`, `46-55`, `56+`,  Other, Total))

my_kable(age_df)
```
\newpage

# AB 74: Tables

16. (b) The number of assessed individuals by risk level, booking charge levels, and release decision
\newpage

## The Number of Assessed Individuals by Risk Level (PSA in "Other")
```{r}
risk_df_complete <- df %>%
  count(County, risk_level, tool_name) %>%
  group_by(County, tool_name) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  risk_level, values_from =  n, values_fill = 0) %>%
  select(County, tool_name, Low, Medium, High,  Other, Total) %>%
  bind_rows(df %>%
              count(risk_level) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  risk_level, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total", tool_name = "All") %>%
              select(County, tool_name, Low, Medium, High,  Other, Total))

my_kable(risk_df_complete)
```
\newpage

## The Number of Assessed Individuals by Risk Level (PSA mapped to 3 levels)
```{r}
risk_df_three_levels <- df %>%
  mutate(risk_level = case_when(
    psa_nvca_risk_score == 1 ~"High",
    psa_nca_risk_score %in% 5:6|psa_fta_risk_score %in% 5:6 ~ "High",
    psa_nca_risk_score %in% 3:4|psa_fta_risk_score %in% 3:4 ~ "Medium",
    psa_nca_risk_score %in% 1:2|psa_fta_risk_score %in% 1:2 ~ "Low",
    T ~ risk_level)) %>%
  mutate(risk_level = case_when(
    risk_level == "Medium" & psa_nvca_risk_score == 1 ~ "High",
    risk_level == "Low" & psa_nvca_risk_score == 1 ~ "Medium",
    T ~ risk_level)) %>%
  count(County, risk_level, tool_name) %>%
  group_by(County, tool_name) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  risk_level, values_from =  n, values_fill = 0) %>%
  select(County, tool_name, Low, Medium, High,  Other, Total) %>%
  bind_rows(df %>%
              mutate(risk_level = case_when(
                psa_nca_risk_score %in% 5:6|psa_fta_risk_score %in% 5:6 ~ "High",
                psa_nca_risk_score %in% 3:4|psa_fta_risk_score %in% 3:4 ~ "Medium",
                psa_nca_risk_score %in% 1:2|psa_fta_risk_score %in% 1:2 ~ "Low",
                T ~ risk_level),
                ) %>%
              mutate(risk_level = case_when(
                risk_level == "Medium" & psa_nvca_risk_score == 1 ~ "High",
                risk_level == "Low" & psa_nvca_risk_score == 1 ~ "Medium",
                T ~ risk_level),
                ) %>%
              count(risk_level) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  risk_level, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total", tool_name = "All") %>%
              select(County, tool_name, Low, Medium, High,  Other, Total))


my_kable(risk_df_three_levels)
```
\newpage

## The Number of Assessed Individuals by Risk Level (without PSA)
```{r}
risk_df_no_psa <- df %>%
  filter(tool_name != "psa") %>%
  count(County, risk_level, tool_name) %>%
  group_by(County, tool_name) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  risk_level, values_from =  n, values_fill = 0) %>%
  select(County, tool_name, Low, Medium, High,  Other, Total) %>%
  bind_rows(df %>%
              count(risk_level) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  risk_level, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total", tool_name = "All") %>%
              select(County, tool_name, Low, Medium, High,  Other, Total))


my_kable(risk_df_no_psa)
```
\newpage

## The Number of Assessed Individuals by Risk Level (PSA FTA)
```{r}
risk_df_psa_fta <- df %>%
  filter(tool_name == "psa") %>%
  count(County, psa_fta_risk_score) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  psa_fta_risk_score, values_from =  n, values_fill = 0) %>%
  bind_rows(df %>%
              filter(tool_name == "psa") %>%
              count(psa_fta_risk_score) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  psa_fta_risk_score, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total"))

my_kable(risk_df_psa_fta)
```
\newpage

## The Number of Assessed Individuals by Risk Level (PSA New Criminal Activity)
```{r}
risk_df_psa_nca <- df %>%
  filter(tool_name == "psa",
         psa_nca_risk_score != 9) %>%
  count(County, psa_nca_risk_score) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  psa_nca_risk_score, values_from =  n, values_fill = 0) %>%
  bind_rows(df %>%
              filter(tool_name == "psa",
                     psa_nca_risk_score != 9) %>%
              count(psa_nca_risk_score) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  psa_nca_risk_score, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total"))


my_kable(risk_df_psa_nca)
```
\newpage

## The Number of Assessed Individuals by Risk Level (PSA New Violent Criminal Activity)
```{r}
risk_df_psa_nvca <- df %>%
  filter(tool_name == "psa") %>%
  count(County, psa_nvca_risk_score) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  psa_nvca_risk_score, values_from =  n, values_fill = 0) %>%
  bind_rows(df %>%
              filter(tool_name == "psa") %>%
              count(psa_nvca_risk_score) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  psa_nvca_risk_score, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total"))


my_kable(risk_df_psa_nvca)
```
\newpage

## The Number of Assessed Individuals by Risk Level (PSA FTA X NCA)
```{r}
risk_df_psa_cross <- df %>%
  filter(tool_name == "psa",
         psa_nca_risk_score != 9) %>%
  count(psa_nca_risk_score, psa_fta_risk_score) %>%
  mutate_all(as.character) %>%
  pivot_wider(names_from = psa_fta_risk_score, values_from = n, values_fill = "-") %>%
  rename("PSA NCA Risk Score" = psa_nca_risk_score)


kable(risk_df_psa_cross, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14) %>% 
  add_header_above(c(" ", "PSA FTA Risk Score" = 6))
```
\newpage

## The Number of Assessed Individuals by Booking Charge Level
```{r}
charge_level_df <- df %>%
  count(County, charge_level) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  charge_level, values_from =  n, values_fill = 0) %>%
  select(County, Felony, Misdemeanor, Other, Total) %>%
  bind_rows(df %>%
              count(charge_level) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  charge_level, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select(County, Felony, Misdemeanor, Other, Total))

my_kable(charge_level_df)
```
\newpage

## The Number of Assessed Individuals by Release Decision
```{r}
release_df <- df %>%
  count(County, release_decision) %>%
  group_by(County) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  release_decision, values_from =  n, values_fill = 0) %>%
  select(County, Detain, Monitor, OR, Other, Total) %>%
  bind_rows(df %>%
              count(release_decision) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  release_decision, values_from =  n, values_fill = 0) %>%
              mutate(County = "Total") %>%
              select(County, Detain, Monitor, OR, Other, Total))

my_kable(release_df)
```
\newpage

# AB 74: Tables

16. (c) The number and percentage of assessed individuals who receive pretrial supervision by level of supervision
\newpage


## The Number and Percentage of Assessed and Supervised Individuals by Supervision Level
```{r warning=FALSE}
monitor_df <- df %>%
  filter(release_decision == "Monitor") %>%
  count(County, monitor_level) %>%
  group_by(County) %>%
  mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  pivot_wider(names_from =  monitor_level, values_from =  n, values_fill = "-") %>%
  select(County, Low, Medium, High, Other, Total) %>%
  bind_rows(df %>%
              filter(release_decision == "Monitor") %>%
              count(monitor_level) %>%
              mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
              pivot_wider(names_from =  monitor_level, values_from =  n, values_fill = "-")) %>%
  ungroup() %>%
  mutate(County = if_else(is.na(County), "Total", County)) %>%
  # mutate(tool_name=toupper(tool_name),
         # tool_name= gsub("CO_", "", tool_name)) %>%
  select("County" = County, Total, Low, Medium, High, Other) %>%
  separate(Low, c("Percent_low", "Count_low"), sep = " ") %>%
  separate(Medium, c("Percent_med", "Count_med"), sep = " ") %>%
  separate(High, c("Percent_high", "Count_high"), sep = " ") %>%
  separate(Other, c("Percent_other", "Count_other"), sep = " ") %>%
  ungroup() %>%
  mutate_if(is.character, funs(if_else(is.na(.), "-", .)))

names(monitor_df) <- gsub("_.*", "", names(monitor_df))
  

kable(monitor_df, booktabs = T, format.args = list(big.mark = ","),
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = T,
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray") %>%
  add_header_above(c(" " = 2, "Low" = 2, "Medium" = 2, "High" = 2, "Other" = 2)) %>%
  row_spec(15, bold = T)
  
```
\newpage

# AB 74: Tables

16. (d) The number and percentage of assessed individuals by supervision level who fail to appear in court as required, are arrested for a new offense during the pretrial period, or have pretrial release revoked.
\newpage


## Failures by Monitor Level 
```{r warning=FALSE}
outcome_df <- df %>%
  filter(release_decision == "Monitor") %>%
  mutate(monitor_level = factor(monitor_level, levels = c("Low", "Medium", "High", "Other"))) %>%
  count(County, pretrial_termination_reason, monitor_level) %>%
  group_by(County, monitor_level) %>%
  mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  filter(pretrial_termination_reason != "Other") %>%
  # unite(pretrial_termination_reason, c(monitor_level, pretrial_termination_reason)) %>%
  arrange(pretrial_termination_reason) %>%
  pivot_wider(names_from =  pretrial_termination_reason, values_from =  n, values_fill = "-") %>%
  arrange(County, monitor_level) %>%
  bind_rows(df %>%
              filter(release_decision == "Monitor") %>%
              mutate(monitor_level = factor(monitor_level, levels = c("Low", "Medium", "High", "Other"))) %>%
              count(pretrial_termination_reason, monitor_level) %>%
              group_by(monitor_level) %>%
              mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
              pivot_wider(names_from =  pretrial_termination_reason, values_from =  n, values_fill = "-") %>%
              arrange(monitor_level)) %>%
  ungroup() %>%
  mutate(County = if_else(is.na(County), "Total", County)) %>%
  rename("Monitor Level" = monitor_level) %>%
  separate(FTA, c("Percent_low", "Count_low"), sep = " ") %>%
  separate(New_Crime, c("Percent_med", "Count_med"), sep = " ") %>%
  separate(Revoked, c("Percent_high", "Count_high"), sep = " ") %>%
  ungroup() %>%
  mutate_if(is.character, funs(if_else(is.na(.), "-", .))) %>%
  select(-"Other")

names(outcome_df) <- gsub("_.*", "", names(outcome_df))


outcome2_df <- df %>%
  filter(release_decision == "Monitor") %>%
  mutate(monitor_level = factor(monitor_level, levels = c("Low", "Medium", "High", "Other"))) %>%
  count(pretrial_termination_reason, monitor_level) %>%
  group_by(monitor_level) %>%
  mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
  filter(pretrial_termination_reason != "Other") %>%
  # unite(pretrial_termination_reason, c(monitor_level, pretrial_termination_reason)) %>%
  arrange(pretrial_termination_reason) %>%
  pivot_wider(names_from =  pretrial_termination_reason, values_from =  n, values_fill = "-") %>%
  arrange(monitor_level) %>%
  bind_rows(df %>%
              filter(release_decision == "Monitor") %>%
              count(pretrial_termination_reason) %>%
              mutate(Total = sum(n), n = paste0(round(n = n/Total*100), "%", " ", n)) %>%
              filter(pretrial_termination_reason != "Other") %>%
              arrange(pretrial_termination_reason) %>%
              mutate(monitor_level = "All_Levels") %>%
              pivot_wider(names_from =  pretrial_termination_reason, values_from =  n, values_fill = "-")) %>%
    rename("Monitor Level" = monitor_level) %>%
  separate(FTA, c("Percent_low", "Count_low"), sep = " ") %>%
  separate(New_Crime, c("Percent_med", "Count_med"), sep = " ") %>%
  separate(Revoked, c("Percent_high", "Count_high"), sep = " ") %>%
  ungroup() %>%
  mutate_if(is.character, funs(if_else(is.na(.), "-", .)))

names(outcome2_df) <- gsub("_.*", "", names(outcome2_df))

kable(outcome_df, booktabs = T, format.args = list(big.mark = ","),
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = T,
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray") %>%
  add_header_above(c(" " = 3, "FTA" = 2, "New Crime" = 2, "Revoked" = 2)) %>%
  row_spec(row = 24:27, bold = T)

my_kable(outcome2_df) %>%
  add_header_above(c(" " = 2, "FTA" = 2, "New Crime" = 2, "Revoked" = 2))
```

