---
title: "Alameda FTA test"
output: html_document
date: "2023-12-05"
---

# Settup and Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
knitr::opts_knit$set(root.dir = "C:/PretrialPilot/Pretrial-Pilot-County-Analysis")

# library(rlang)
library(tidyverse)
library(data.table)
library(openxlsx)
#library(readxl)
library(lubridate)
library(gsubfn)
library(fuzzyjoin)
library(dplyr)
# library(multidplyr)
library(pROC)
library(broom)
library(kableExtra)
library(stargazer)
library(DBI)
library(dbplyr)
library(odbc)
library(tinytex)
library(gt)
library(askpass)

# shell.exec(getwd())
```

Connection
```{r include=FALSE}

con <- dbConnect(odbc::odbc(), "snowflake_pretrial", uid ="Sal.Lempert@jud.ca.gov", pwd = rstudioapi::askForPassword("Password"))

```


Pull live snowflake data -- al_agg
```{sql echo=TRUE, connection=con, output.var='al_agg'}
SELECT *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"
;
```

Pull live snowflake data -- al_fcc
```{sql echo=TRUE, connection=con, output.var='al_fcc'}
SELECT *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"
;
```

Pull live snowflake data -- al_fw
```{sql echo=TRUE, connection=con, output.var='al_fw'}
SELECT *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"
;
```

Pull live snowflake data -- al_dw
```{sql echo=TRUE, connection=con, output.var='al_dw'}
SELECT *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"
;
```

Pull live snowflake data -- al_link
```{sql echo=TRUE, connection=con, output.var='al_link'}
SELECT *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"
;

```

Pull live snowflake data -- agg_enh
```{sql echo=TRUE, connection=con, output.var='agg_enh'}
SELECT *
FROM "DWH_PROD"."REPORTING"."AGG_PRETRIAL_KPI_DOJ_ENHANCED"
;

```

# Look at Alameda FTA data
```{r}
afta <- fread("Alameda Raw Failure Rate Data 05082020 to 12042023.csv")

afta <- afta %>%
  mutate(Book_Date = mdy(Book_Date),
         Assessment_Date = mdy(Assessment_Date),
         Release_Date  = mdy(Release_Date))
fta_caseids <- afta %>%
  filter(FTA_Count == 1) %>%
  pull(Case_ID)
```

# Compare datasets
```{r}

afta %>%
  mutate(Case_ID = as.character(Case_ID)) %>%
  count(Case_ID %in% (al_fcc %>% 
                        pull(CASE_ID)))

afta %>%
  mutate(Case_ID = as.character(Case_ID)) %>%
  filter(!Case_ID %in% (al_fcc %>% 
                        pull(CASE_ID)))
 

case_id_key <- al_fcc %>%
  select(CASE_KEY, CASE_ID) %>%
  distinct()


al_agg <- al_agg %>%
  left_join(case_id_key)

match <- afta %>%
  select(CASE_ID = Case_ID, BOOKING_DATE = Book_Date, FTA_Count) %>%
  mutate(CASE_ID = as.character(CASE_ID))

fta_casekeys <- al_agg %>%
  inner_join(match) %>%
  filter(FTA_Count == 1) %>%
  pull(CASE_KEY)

wars <- al_fw %>%
  left_join(al_dw)
  
wars %>%
  filter(CASE_KEY %in% fta_casekeys) %>%
  count(HAS_FTA)

wars %>%
  filter(CASE_KEY %in% fta_casekeys) %>%
  count(HAS_FTA, WARRANT_TYPE, WARRANT_STATUS, WARRANT_REASON)
```
Pull non-matching case ids for Cory
```{r}
missing_case_ids <- afta %>%
  mutate(Case_ID = as.character(Case_ID)) %>%
  filter(!Case_ID %in% (al_fcc %>% 
                        pull(CASE_ID)))

#write.csv(missing_case_ids, "missing cases for Cory.csv")

al_fcc %>%
  filter(CASE_ID %in% (missing_case_ids %>% pull(Case_ID)))
```

# Calculate FTA rate including recalled warrants
```{r}
active_wars <- wars %>%
  filter(WARRANT_STATUS %in% c("Recalled", "Issued"),
         WARRANT_TYPE == "Bench",
         WARRANT_REASON == "FTA") %>%
  select(CASE_KEY, DIM_WARRANT_ISSUANCE_DATE_KEY) %>%
  mutate(fta_test_flag = 1) %>%
  mutate(date_char = as.character(DIM_WARRANT_ISSUANCE_DATE_KEY)) %>%
  mutate(war_issue_date = ymd(date_char)) %>%
  select(CASE_KEY, fta_test_flag, war_issue_date) %>%
  distinct()

links <- al_link %>%
  select(BOOKING_KEY, CASE_KEY)

active_wars <- active_wars %>%
  left_join(links) %>%
  select(-CASE_KEY)


al_agg %>%
  mutate(rownum = row_number()) %>%
  left_join(active_wars) %>% 
  filter(war_issue_date <PRETRIAL_PERIOD_END_DATE & war_issue_date > RELEASE_DATE) %>%
  distinct(rownum)
#5,911 ftas in agg btwn release date and end date, 5,986 btwn book date and end date -- WHY?
#5,635 and 5,706 using booking key to link instead of case key

al_agg %>%
  filter(HAS_FAILURE_TO_APPEAR == 'Yes')
#4,097



test <- al_agg %>%
  mutate(rownum = row_number()) %>%
  left_join(active_wars) %>% 
  mutate(fta_test_flag = case_when(is.na(war_issue_date) ~ 0,
                                   war_issue_date <PRETRIAL_PERIOD_END_DATE & war_issue_date > RELEASE_DATE ~ 1,
                                   T ~ 0)) %>%
  group_by(rownum) %>%
  mutate(fta_test_flag = max(fta_test_flag)) %>%
  ungroup() %>%
  distinct(rownum, .keep_all = T)

test %>%
  count(fta_test_flag)

test %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes") %>%
  filter(!is.na(RISK_SCORE)) %>%
  count(fta_test_flag) %>%
  mutate(tot = sum(n), perc = round(100*n/sum(n),1))

al_agg %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes") %>%
  filter(!is.na(RISK_SCORE)) %>%
  count(HAS_FAILURE_TO_APPEAR) %>%
  mutate(perc = round(100*n/sum(n),1))

al_agg_enh <- agg_enh %>%
  filter(COUNTY == "Alameda")

al_agg_enh <- al_agg_enh %>%
  left_join(test %>% select(BOOKING_KEY, fta_test_flag, RISK_SCORE) %>% distinct())

al_agg_enh %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes") %>%
  filter(!is.na(RISK_SCORE)) %>%
  count(fta_test_flag, RECID_ARREST_FTA_FLAG_DOJ) %>%
  mutate(tot = sum(n), perc = round(100*n/sum(n),1))

al_agg_enh %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes") %>%
  filter(!is.na(RISK_SCORE)) %>%
  mutate(fta_all = case_when(fta_test_flag == 1 ~ 1,
                             RECID_ARREST_FTA_FLAG_DOJ == 1 ~ 1,
                             T ~ 0)) %>%
  count(fta_all) %>%
  mutate(tot = sum(n), perc = round(100*n/sum(n),1))

```
Pull FTAs for Cory
```{r}
ftas_for_cory <- test %>%
  filter(fta_test_flag == 1) %>%
  select(BOOKING_DATE, ASSESSMENT_DATE, RELEASE_DATE, BOOKING_KEY, BOOKING_ID, CASE_KEY, CASE_ID)



#write.csv(ftas_for_cory, "ftas for Cory.csv")

afta %>%
  mutate(CASE_ID = as.character(Case_ID)) %>%
  left_join(case_id_key %>% distinct())

al_fcc %>%
  filter(CASE_KEY %in% c("945772606669", "945772671967", "945772725483"))

al_agg %>%
  filter(BOOKING_KEY %in% c("6066690494986", "6719670494986", "7254830494986"))

```
```{r}
al_link %>%
  select(BOOKING_KEY, CASE_KEY, CASE_ID)

al_fw

al_fta_wars <- wars %>%
  mutate(war_issue_date = ymd(DIM_WARRANT_ISSUANCE_DATE_KEY)) %>%
  select(war_issue_date, CASE_KEY, WARRANT_TYPE, WARRANT_STATUS, WARRANT_REASON) %>%
  filter(!is.na(war_issue_date)) %>%
  filter(WARRANT_TYPE == "Bench",
         WARRANT_REASON == "FTA",
         WARRANT_STATUS %in% c("Issued", "Served", "Ordered", "Recalled")) %>%
  distinct()

al_fta_wars <- al_fta_wars %>%
  left_join(al_link %>%
            select(BOOKING_KEY, CASE_KEY) %>%
              distinct()) %>%
  select(war_issue_date, BOOKING_KEY) %>%
  distinct() %>%
  filter(!is.na(BOOKING_KEY))

test2 <- al_agg %>%
  mutate(row = row_number()) %>%
  left_join(al_fta_wars) %>%
  mutate(fta_test_flag = case_when(is.na(war_issue_date) ~ 0,
                                    war_issue_date >= RELEASE_DATE & war_issue_date <= PRETRIAL_PERIOD_END_DATE ~ 1,
                                   T ~ 0)) %>%
  group_by(BOOKING_KEY) %>%
  arrange(desc(fta_test_flag), war_issue_date) %>%
  mutate(fta_test_flag = max(fta_test_flag)) %>%
  ungroup() %>%
  distinct(row, .keep_all = T) 


test2 %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes") %>%
  filter(!is.na(RISK_SCORE)) %>%
  count(fta_test_flag) %>%
  mutate(tot = sum(n), perc = round(100*n/sum(n),1))

test %>%
  left_join(test2 %>% select(BOOKING_KEY, fta_test_flag) %>% rename(fta_test_flag2 = 'fta_test_flag')) %>%
  count(fta_test_flag, fta_test_flag2)

test %>%
  select(-war_issue_date) %>%
  left_join(test2 %>% select(BOOKING_KEY, fta_test_flag, war_issue_date) %>% rename(fta_test_flag2 = 'fta_test_flag')) %>%
  filter(fta_test_flag != fta_test_flag2) %>%
  select(CASE_KEY, BOOKING_KEY, fta_test_flag, fta_test_flag2, BOOKING_DATE, RELEASE_DATE, war_issue_date, PRETRIAL_PERIOD_END_DATE) %>%
  arrange(desc(fta_test_flag2))
```


```{r}
wars %>%
    filter(CASE_KEY == '975725683666')
  
links %>%
    filter(BOOKING_KEY == '6834351379444')

al_fcc %>%
  filter(CASE_ID == "948442") %>%
  select(CASE_ID, CASE_KEY, BOOKING_KEY)
  
al_fta_wars %>%
  filter(BOOKING_KEY == '6875721381246')

al_fw %>%
  left_join(al_dw) %>%
  filter(CASE_KEY == "943010592976")

```
```{r}
ftas_for_cory <- test2 %>%
  filter(fta_test_flag == 1) %>%
  select(BOOKING_ID, BOOKING_KEY, CASE_KEY, CASE_ID, BOOKING_DATE, RELEASE_DATE, PRETRIAL_PERIOD_END_DATE, war_issue_date, fta_test_flag)

#write.csv(ftas_for_cory, "ftas for cory.csv")

test2 %>%
  filter(fta_test_flag == 1) %>%
  filter(is.na(PRETRIAL_PERIOD_END_DATE))

afta %>%
  mutate(CASE_ID = as.character(Case_ID),
         BOOKING_DATE = Book_Date) %>%
  left_join(ftas_for_cory) %>%
  filter(FTA_Count == 0 & fta_test_flag == 1) %>%
  select(Case_ID, CASE_ID, BOOKING_KEY, CASE_KEY, FTA_Count, BOOKING_DATE, Release_Date, RELEASE_DATE, war_issue_date, PRETRIAL_PERIOD_END_DATE)


afta %>%
  mutate(CASE_ID = as.character(Case_ID),
         BOOKING_DATE = Book_Date) %>%
  left_join(test2 %>% select(BOOKING_ID, BOOKING_KEY, CASE_KEY, CASE_ID, BOOKING_DATE, RELEASE_DATE, PRETRIAL_PERIOD_END_DATE, war_issue_date, fta_test_flag)) %>%
  filter(FTA_Count == 1 & fta_test_flag == 0,
         !is.na(PRETRIAL_PERIOD_END_DATE)) %>%
  select(Case_ID, CASE_ID, BOOKING_KEY, CASE_KEY, FTA_Count, BOOKING_DATE, Release_Date, RELEASE_DATE, war_issue_date, PRETRIAL_PERIOD_END_DATE)
  count(FTA_Count, fta_test_flag)


```

