---
output:
  pdf_document: default
  html_document: default
---
# Settup and Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
knitr::opts_knit$set(root.dir = "G:/CrimJustice/PretrialAssessmentPilot")

# library(rlang)
library(tidyverse)
library(data.table)
library(openxlsx)
library(readxl)
library(lubridate)
library(XML)
library(xml2)
# library(xmltools)o
library(gsubfn)
library(fuzzyjoin)
library(dplyr)
library(openxlsx)
library(fuzzyjoin)
# library(multidplyr)
library(pROC)
library(broom)
library(kableExtra)
library(stargazer)

# shell.exec(getwd())
```

Load data
```{r warning=FALSE, include=FALSE}
load("G:/CrimJustice/PretrialAssessmentPilot/Tool Validation Final Data Frame.RData")

eval_df <- eval_df %>%
  filter(tool_name %in% c("oras", "psa", "vprai", "vprair"))

```

# PSA AUC race comparison

PSA FTA
```{r}
rocW <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

PSA New arrest
```{r}
rocW <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

PSA New filing
```{r}
rocW <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

PSA New conviction
```{r}
rocW <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

PSA New violent arrest
```{r}
rocW <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)

```
\newpage
# PSA AUC gender comparison

PSA FTA
```{r}
rocM <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)
```

PSA New arrest
```{r}
rocM <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)
```

PSA New filing
```{r}
rocM <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)
```

PSA New conviction
```{r}
rocM <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)
```

PSA New violent arrest
```{r}
rocM <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)
```
\newpage

# VPRAI AUC race comparison

VPRAI FTA
```{r}
rocW <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

VPRAI New arrest
```{r}
rocW <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

VPRAI New filing
```{r}
rocW <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

VPRAI New conviction
```{r}
rocW <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

VPRAI New violent arrest
```{r}
rocW <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)

```

VPRAI FTA or new arrest
```{r}
rocW <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "White"), ci = T)
rocB <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Black"), ci = T)
rocH <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)

```
\newpage
# VPRAI AUC gender comparison

VPRAI FTA
```{r}
rocM <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

VPRAI New arrest
```{r}
rocM <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

VPRAI New filing
```{r}
rocM <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

VPRAI New conviction
```{r}
rocM <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

VPRAI New violent arrest
```{r}
rocM <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

VPRAI FTA or new arrest
```{r}
rocM <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Male"), ci = T)
rocF <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```
\newpage

# Los Angeles PSA AUC race comparison
LA FTA
```{r}
rocW <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "White"), ci = T)
rocB <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Black"), ci = T)
rocH <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

LA New arrest
```{r}
rocW <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

LA New filing
```{r}
rocW <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

LA New conviction
```{r}
rocW <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

LA New violent arrest
```{r}
rocW <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)

```

# Los Angeles PSA AUC gender comparison
LA FTA
```{r}
rocM <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Male"), ci = T)
rocF <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

LA New arrest
```{r}
rocM <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

LA New filing
```{r}
rocM <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

LA New conviction
```{r}
rocM <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

LA New violent arrest
```{r}
rocM <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Los Angeles") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)


```
\newpage
# Sacramento PSA AUC race comparison
Sacramento FTA
```{r}
rocW <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "White"), ci = T)
rocB <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Black"), ci = T)
rocH <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

Sacramento New arrest
```{r}
rocW <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

Sacramento New filing
```{r}
rocW <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

Sacramento New conviction
```{r}
rocW <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

Sacramento New violent arrest
```{r}
rocW <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)

```

# Sacramento PSA AUC gender comparison
Sacramento FTA
```{r}
rocM <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Male"), ci = T)
rocF <- roc(fta_flag ~ psa_fta_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

Sacramento New arrest
```{r}
rocM <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrested_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

Sacramento New filing
```{r}
rocM <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_filed_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

Sacramento New conviction
```{r}
rocM <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_convicted_flag ~ psa_nca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

Sacramento New violent arrest
```{r}
rocM <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrest_violent_psa_flag ~ psa_nvca_risk_score, data = eval_df %>% filter(county == "Sacramento") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)


```
\newpage
# San Joaquin AUC race comparison

San Joaquin FTA
```{r}
rocW <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "White"), ci = T)
rocB <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Black"), ci = T)
rocH <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

San Joaquin New arrest
```{r}
rocW <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

San Joaquin New filing
```{r}
rocW <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

San Joaquin New conviction
```{r}
rocW <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)
```

San Joaquin New violent arrest
```{r}
rocW <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "White"), ci = T)
rocB <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Black"), ci = T)
rocH <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)

```

San Joaquin FTA or new arrest
```{r}
rocW <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "White"), ci = T)
rocB <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Black"), ci = T)
rocH <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(race == "Hispanic"), ci = T)
roc.test(rocW, rocB)
roc.test(rocW, rocH)
roc.test(rocB, rocH)

```
\newpage
# San Joaquin AUC gender comparison

San Joaquin FTA
```{r}
rocM <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Male"), ci = T)
rocF <- roc(fta_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

San Joaquin New arrest
```{r}
rocM <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrested_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

San Joaquin New filing
```{r}
rocM <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_filed_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

San Joaquin New conviction
```{r}
rocM <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_convicted_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

San Joaquin New violent arrest
```{r}
rocM <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Male"), ci = T)
rocF <- roc(recid_arrest_violent_psa_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```

San Joaquin FTA or new arrest
```{r}
rocM <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Male"), ci = T)
rocF <- roc(any_pretrial_failure_flag ~ vprai_risk_score, data = eval_df %>% filter(county == "San Joaquin") %>% filter(sex == "Female"), ci = T)
roc.test(rocM, rocF)

```
