---
title: "Charge hierarchy creation"
output: html_notebook
---

# Libraries
```{r}
library(data.table)
library(openxlsx)
library(readxl)
library(lubridate)
library(tidyverse)
library(XML)
library(xml2)
library(xmltools)
library(fuzzyjoin)

```


# Charge Hierarchy Creation

2020 DOJ Hieararchies
```{r, eval=FALSE, include=FALSE}
#DOJ Crime Severity Ratings 2008
doj_hierarchy_2020 <- fread("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Master Charge Code Table 2020.csv")
doj_hierarchy_2020_jbsis <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/2020_March04_DOJ_Offense_Table_JBSIS.xlsx")


names(doj_hierarchy_2020) <- c("summary_code", "cjis_code", "hierarchy", "charge_level", "charge", "charge_code", "master_charge_description", "sentence")
names(doj_hierarchy_2020_jbsis) <- c("summary_code", "cjis_code", "hierarchy", "charge_level", "charge", "charge_code", "master_charge_description", "sentence", "jbsis_code")

doj_hierarchy_2020 <- left_join(doj_hierarchy_2020, doj_hierarchy_2020_jbsis)

doj_hierarchy_2020 <- doj_hierarchy_2020 %>%
  mutate(charge_level = toupper(charge_level),
         charge_level = if_else(!charge_level %in% c("F", "I", "M"), "Other", charge_level),
         charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}|EX|\\+|","", charge)),
         charge_code = if_else(!charge_code %in% c("PC", "VC", "HS", "BP", "WI", "US"), "Other", charge_code)) %>%
  distinct(charge, charge_code, charge_level, .keep_all = T) %>%
  unite(join_var, charge_level, charge_code, charge, remove = F) %>%
  select(join_var, master_charge_description, hierarchy, charge_level, charge_code, charge, jbsis_code, summary_code)
```


2017 DOJ Hieararchies
```{r, eval=FALSE, include=FALSE}
#DOJ Crime Severity Ratings 2008
doj_hierarchy_2017 <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/dojoffenses.xls")

doj_hierarchy_2017 <- doj_hierarchy_2017 %>%
  mutate(STATUTE2 = gsub("\\/|\\(|\\)| |\\.|\\.*","", STATUTE2)) %>%
  unite("charge",STATUTE1,STATUTE2, sep = "") %>%
  mutate(charge = gsub("NA", "", charge)) %>%
  select(charge, master_charge_description = DESCRIPTION, hierarchy = HIERARCHY, charge_code = CODE_TYPE, charge_level = CHARGE_TYPE) %>%
  filter(!is.na(hierarchy)) %>%
  # mutate(charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}","", charge))) %>%
  mutate(charge_level = if_else(!charge_level %in% c("F", "I", "M"), "Other", charge_level),
         charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}|EX|\\+|","", charge)),
         charge_code = if_else(!charge_code %in% c("PC", "VC", "HS", "BP", "WI", "US"), "Other", charge_code)) %>%
  # mutate(charge_level = fct_collapse(charge_level, O = c("S", "X"))) %>% #Incorretly labeled, juvenile, and miscelanious 
  distinct(charge, charge_code, charge_level, .keep_all = T) %>%
  unite(join_var, charge_level, charge_code, charge, remove = F) %>%
  select(join_var, master_charge_description, hierarchy, charge_level, charge_code, charge)

```

 -Visualizes above chunk
```{r, eval=FALSE, include=FALSE} 
#--This visualizes the above chunk
table(doj_hierarchy_2017$charge_code, doj_hierarchy_2017$charge_level)

doj_hierarchy_2017 %>%
  # filter(HIERARCHY < 1.7e5) %>%
  ggplot() +
  aes(x = hierarchy, color = charge_level) +
  geom_density() +
  theme_few()
```


2008 DOJ Hierarchies
```{r}
#DOJ Crime Severity Ratings 2008
doj_hierarchy_2008 <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/DOJ Crime Severity Ratings May 2008.xls", col_names = FALSE, skip = 11)

#Recreating Variables
names(doj_hierarchy_2008) <- c("summary_code", "bcs", "hierarchy", "charge_level", "charge", "charge_code", "master_charge_description", "sentence")

#collapsed codes for merger with Fresno
doj_hierarchy_2008 <- doj_hierarchy_2008 %>% 
  # mutate(charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}","", charge))) %>%
  mutate(charge_level = strapplyc(charge_level, "^(.).*", simplify = T)) %>%
  mutate(charge_level = if_else(!charge_level %in% c("F", "I", "M"), "Other", charge_level),
         charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}|EX|\\+|","", charge)),
         charge_code = if_else(!charge_code %in% c("PC", "VC", "HS", "BP", "WI", "US"), "Other", charge_code)) %>%
  filter(!is.na(hierarchy)) %>%
  # mutate(charge_level = fct_recode(charge_level, "Other" = "S")) %>%
  distinct(charge_level, charge_code, charge, .keep_all = T)  %>%
  select(-c(sum, bcs, sentence)) %>%
  unite(join_var, charge_level, charge_code, charge, remove = F) %>%
  select(join_var, master_charge_description, hierarchy, charge_level, charge_code, charge, summary_code)
 
```

 -Visualizes above chunk
```{r, eval=FALSE, include=FALSE} 
#--This visualizes the above chunk
table(doj_hierarchy_2008$charge_code, doj_hierarchy_2008$charge_level)

doj_hierarchy_2008 %>%
  filter(hierarchy < 1.7e5) %>%
  ggplot() +
  aes(x = hierarchy, color = charge_level) +
  geom_density() +
  theme_few()
```


 Charge Code Table 
```{r}
#--This chunk pulls the master charge code table and standardizes it. 
mcct_2016 <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Master Charge Code Table 2016.xlsx", guess_max = Inf)

mcct_2016 <- mcct_2016 %>%
  filter(!is.na(`CalDOJ HIERARCHY Code Informational only`))

mcct_2016 <- mcct_2016 %>% 
  select(charge_code = CODE, 
         charge = `CODE SECTION (upper/lower case)`, 
         hierarchy = `CalDOJ HIERARCHY Code Informational only`,
         master_charge_description = `Offense Display (For AJIS and ISAB Departments)`,
         charge_level = LEVEL,
         summary_code = `CalDOJ Summary Code`) %>%
  # mutate(charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}","", charge))) %>%
  mutate(charge_level = if_else(!charge_level %in% c("F", "I", "M"), "Other", charge_level),
         charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}|EX|\\+|","", charge)),
         charge_code = if_else(!charge_code %in% c("PC", "VC", "HS", "BP", "WI", "US"), "Other", charge_code)) %>%
  distinct(charge_level, charge_code, charge, .keep_all = T) %>%
  mutate(hierarchy = as.numeric(hierarchy)) %>%
  unite(join_var, charge_level, charge_code, charge, remove = F) %>%
  select(join_var, master_charge_description, hierarchy, charge_level, charge_code, charge, summary_code)
```

 -Visualizes above chunk
```{r, eval=FALSE, include=FALSE} 
#--This visualizes the above chunk
table(mcct_2016$charge_code, mcct_2016$charge_level)

mcct_2016 %>%
  # filter(HIERARCHY < 3e5) %>%
  ggplot() +
  aes(x = hierarchy, color = charge_level) +
  geom_density() +
  theme_few()
```


JBSIS Hierarchies
```{r, eval=FALSE, include=FALSE}
#JBSIS matched Charges
charge_hier_jbsis <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Copy of 2016_Nov21_DOJ_Offense_Table_JBSIS.xlsx") 

names(charge_hier_jbsis) <- toupper(names(charge_hier_jbsis))

charge_hier_jbsis <- charge_hier_jbsis %>% 
  select(charge = `CODE SECTION`,
         charge_code = `CODE TYPE`,
         master_charge_description = `OFFENSE DESCRIPTION`,
         charge_level = `OFF LEVEL`,
         hierarchy = HIERARCHY,
         summary_code = `SUM CODE`) %>%
  # mutate(charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*","", charge))) %>% 
  mutate(charge_level = if_else(!charge_level %in% c("F", "I", "M"), "Other", charge_level),
         charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}|EX|\\+|","", charge)),
         charge_code = if_else(!charge_code %in% c("PC", "VC", "HS", "BP", "WI", "US"), "Other", charge_code)) %>%
  distinct(charge, charge_code, charge_level, .keep_all = T) %>%
  unite(join_var, charge_level, charge_code, charge, remove = F) %>%
  select(join_var, master_charge_description, hierarchy, charge_level, charge_code, charge, summary_code)
```

 -Visualizes above chunk
```{r, eval=FALSE, include=FALSE} 
#--This visualizes the above chunk
table(charge_hier_jbsis$charge_code, charge_hier_jbsis$charge_level)

charge_hier_jbsis %>%
 
   # filter(HIERARCHY < 1.7e5) %>%
  ggplot() +
  aes(x = as.numeric(hierarchy), color = charge_level) +
  geom_density() +
  theme_few()

```

Special Allegations--Hierarchies are Max
```{r}
charge_hier_special <- fread("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/San_Mateo_Qualifier_Flags_Court_charges.csv", header = T)
charge_hier_special2 <- fread("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Yuba_Qualifier_Flags_Court_charges.csv", header = T)
charge_hier_special3 <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/qualifier_codes_for_Noah_Kings_Court.xlsx")
charge_hier_special4 <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/qualifier_codes_for_Noah_Napa_Court.xlsx")
charge_hier_special5 <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/qualifier_codes_for_Noah_Sonoma_Court.xlsx")

charge_hier_special6 <- tibble(join_var = c("M_VC_23578", "M_VC_231035", "F_PC_117012C1", "F_PC_120225A", "F_PC_1170H3", "F_PC_1170H", 
                                               "F_PC_120227A", "F_PC_120221", "F_PC_667A1", "F_PC_12022A1", "F_PC_12022B1", 
                                               "F_VC_23577", "F_PC_1202253C", "F_PC_290018BZ", "F_PC_1202253B", 
                                               "F_PC_6676D", "F_PC_1202253D", "F_PC_1203K", "F_HS_113702A", "F_PC_120307A11", 
                                               "F_HS_11370A", "F_PC_6675C21", "F_PC_667E1", "F_PC_6676C", "F_PC_120306A1", "F_PC_969F", 
                                               "F_PC_120306A1", "F_PC_1170H5B", "F_PC_1170H5A")) %>%
  separate(join_var, c("court_charge_level", "court_charge_code", "court_charge"))


charge_hier_special <- bind_rows(charge_hier_special, charge_hier_special2, charge_hier_special3, charge_hier_special4, charge_hier_special5, charge_hier_special6) 

rm(charge_hier_special2, charge_hier_special3, charge_hier_special4, charge_hier_special5, charge_hier_special6)

charge_hier_special <- charge_hier_special %>%
  select(charge_code = court_charge_code, charge_level = court_charge_level, charge = court_charge, master_charge_description = court_charge_description) %>%
  mutate(charge_level = if_else(!charge_level %in% c("F", "I", "M"), "Other", charge_level),
         charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}|EX|\\+|","", charge)),
         charge_code = if_else(!charge_code %in% c("PC", "VC", "HS", "BP", "WI", "US"), "Other", charge_code)) %>%
  mutate(master_charge_description = gsub("^.*-", "", toupper(master_charge_description))) %>%
  group_by(charge_code, charge) %>% 
  mutate(master_charge_description = if_else(is.na(master_charge_description), max(master_charge_description, na.rm = T), master_charge_description)) %>%
  ungroup() %>%
  distinct(charge, charge_code, charge_level, .keep_all = T) %>%
  unite(join_var, charge_level, charge_code, charge, remove = F) %>%
  mutate(hierarchy = 1e6) %>%
  select(join_var, master_charge_description, hierarchy, charge_level, charge_code, charge) %>%
  mutate(special_flag = 1) 

# charge_hier_special %>%
#   filter(grepl("23578", join_var)) %>%
#   group_by(charge_code, charge) %>%
#   mutate(master_charge_description = if_else(is.na(master_charge_description), max(master_charge_description, na.rm = T), master_charge_description))
```

  -New Special Allegations
```{r}  
  
charge_hier_check <- tibble(join_var = c("M_VC_23578", "M_VC_231035", "F_PC_117012C1", "F_PC_120225A", "F_PC_1170H3", "F_PC_1170H", 
                                               "F_PC_120227A", "F_PC_120221", "F_PC_667A1", "F_PC_667A1", "F_PC_12022A1", "F_PC_12022B1", 
                                               "F_VC_23577", "F_PC_1202253C", "F_PC_290018BZ", "F_PC_290018BZ", "F_PC_1202253B", 
                                               "F_PC_6676D", "F_PC_1202253D", "F_PC_1203K", "F_HS_113702A", "F_PC_120307A11", 
                                               "F_HS_11370A", "F_PC_6675C21"))
anti_join(charge_hier_check, charge_hier_special)
```

Missing Charges
```{r}
charge_hier_missing <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Charges Missing from the Charge Code Tables original.xlsx", sheet = "Combined") 

charge_hier_missing <- charge_hier_missing %>% 
  mutate(charge_level = if_else(!charge_level %in% c("F", "I", "M"), "Other", charge_level),
         charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}|EX|\\+|","", charge)),
         charge_code = if_else(!charge_code %in% c("PC", "VC", "HS", "BP", "WI", "US"), "Other", charge_code)) %>%
  distinct(charge, charge_code, charge_level, .keep_all = T) %>%
  unite(join_var, charge_level, charge_code, charge, remove = F) %>%
  select(join_var, master_charge_description, hierarchy, charge_level, charge_code, charge) 
```

Merging hiearchies 
```{r}
charge_hier <- bind_rows(doj_hierarchy_2020, doj_hierarchy_2017, doj_hierarchy_2008, mcct_2016, charge_hier_jbsis, charge_hier_special, charge_hier_missing) %>%
  mutate(special_flag = if_else(is.na(special_flag), 0, special_flag)) %>%
  group_by(join_var) %>%
  mutate(special_flag = max(special_flag)) %>%
  ungroup() %>%
  distinct(join_var, .keep_all = T) %>%
  mutate(hierarchy = if_else(is.na(hierarchy|hierarchy >= 3e5|hierarchy < 1000), 1e6, hierarchy))

save(charge_hier, file = "Complete Charge Code Hierarchy.RData")
# shell.exec(getwd())
```

 -Visualizes above chunk
```{r, eval=FALSE, include=FALSE} 
#--This visualizes the above chunk
table(charge_hier_jbsis$code_type, charge_hier_jbsis$charge_type)

charge_hier %>%
  filter(hierarchy < 1.7e5) %>%
  ggplot() +
  aes(x = as.numeric(hierarchy), color = charge_level) +
  geom_density() +
  theme_few()

charge_hier %>%
  count(charge_level)

charge_hier %>%
  count(charge_code) %>%
  arrange(desc(n))

charge_hier %>%
  mutate(code_type = gsub(".* ", "", code_type))  %>%
  count(code_type) %>%
  arrange(desc(n))

load("Complete Charge Code Hierarchy.RData")

charge_hier %>%
  count(charge_code)
```


# Charge Hierarchy Flag Adds
```{r}
load("Complete Charge Code Hierarchy.RData")

#Serious and Violent Felonies
serious_violent_charges <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Serious and Violent Charges.xlsx", 
    sheet = "Data") %>%
  # filter(Serious == T | Violent == T)
  select(charge, charge_level, serious_felony_flag = Serious, violent_felony_flag = Violent) %>%
  filter(serious_felony_flag == 1 | violent_felony_flag == 1, charge_level == "F") %>%
  mutate(charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|\\\\.*|\\{o|\\}","", charge))) %>%
  mutate(charge = gsub("HSC", "HS_", charge),
         charge = gsub("PEN", "PC_", charge),
         charge = gsub("VEH", "VC_", charge)) %>%
  unite(join_var, charge_level, charge) %>%
  mutate(serious_violent_flag = if_else(serious_felony_flag == T|violent_felony_flag == T, 1, 0)) %>%
  # mutate(serious_felony_flag = if_else(serious_felony_flag == T, 1, 0),
  #        violent_felony_flag = if_else(violent_felony_flag == T, 1, 0)) %>%
  mutate_all(funs(ifelse(is.na(.), 0, .))) %>%
  distinct(join_var, .keep_all = T) %>%
  ungroup()

charge_hier <- charge_hier %>%
  left_join(serious_violent_charges) %>%
  mutate(serious_violent_flag = if_else(is.na(serious_violent_flag), 0, serious_violent_flag)) 
  # mutate_at(vars(serious_felony_flag, violent_felony_flag), funs(if_else(is.na(.), 0, .)))

rm(serious_violent_charges)

#Pretrial Violent Charges
pretrial_violent <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Pretrial Pilot Consensus on Violent Offense List - FINAL 2-3-20.xlsx")

names(pretrial_violent) <- c("charge", "violent_description", "violent_psa_flag")

pretrial_violent <- pretrial_violent %>%
  mutate(violent_psa_flag = 1,
         charge_code = if_else(grepl("Veh Code", charge), "VC", "PC"),
         charge = gsub("\\/|\\(|\\)| |\\.|\\.*|\\\\.*|\\{|\\}|^[A-Z]* [A-Z]* ","", toupper(charge))) %>%
  select(-violent_description)

charge_hier <- left_join(charge_hier, pretrial_violent) %>%
  mutate(violent_psa_flag = if_else(is.na(violent_psa_flag), 0, violent_psa_flag))


# Charge Flags Added--Needs fixing
charge_hier <- charge_hier %>%
  mutate(capital_flag = if_else(charge_code == "PC" & charge %in% c("37", "128", "206", "2095", "218", "2361C2", "273AB"), 1, 0),
         dv_flag = if_else(grepl("DOMESTIC|SPOUSE|PARTNER|COHABITANT", master_charge_description) &
                             !grepl("MARRY|CRT ORD|COURT ORDER|FOREIGN|LAND|FAIL|SHELTER", master_charge_description), 1, 0),
         #Attach Flags DV and Sup Vio Flags #Sup Vio Based on Charge Descriptions--Including Flash Incarceration
         sup_vio_flag = if_else((grepl("^SUP| SUP |SUPERVISION|PROBATION|PAROLE", master_charge_description) &
                                  !grepl("^AGG ARSON|SUPV/ETC PROSTITUTION|MENTALY DISORDERD|^SEXUAL ACTIVITY|^SUPPLY|^ADL|SEX|TRANSFER|PROSTITUTION",
                                         master_charge_description))| charge %in% c("3454", "3455", "12032", "12032A"), 1, 0),
         fta_flag = if_else(grepl("APPEAR|FTA", master_charge_description) & !grepl("^DEMAND|WITNESS", master_charge_description), 1, 0),
         marijuana_flag = if_else(grepl("MARIJ|CANNA", master_charge_description), 1, 0),
         sex_flag = if_else(grepl("SEX|COPULATION|RAPE|ORAL|PENETRATION|MOLLEST|LASCIVIOUS|INCEST", 
                                  master_charge_description)|(charge_code == "PC" & charge %in% c("2434", "2641", "266H", "266I", "266J", "269", "272", "285", "286", "288",
                                                           "288a", "2882", "2884", "2885", "2887", "289", "3111", "31111", "314",
                                                           "6476", "653FC")), 1, 0),
         sb10_sex_flag = if_else(sex_flag == 1, 1, 0),
         dui_flag = if_else((charge_code == "VC" & charge %in% c("23546", "23153", "23578"))|(charge_code == "PC" & charge == "1915B"), 1, 0),
         sb10_dui_flag = if_else((charge_code == "VC" & charge %in% c("23546", "23153", "23578"))|(charge_code == "PC" & charge == "1915B"), 1, 0),
         restrain_flag = if_else(charge_code == "PC" & charge %in% c("166C4", "166D1", "27365A", "6499B"), 1, 0),
         sb10_witness_intim_flag = if_else(charge_code == "PC" & charge %in% c("1361", "1365"), 1, 0),
         sb10_onduty_inel_flag = if_else(charge_code == "PC" & charge %in% c("166", "18626", "18628", "18633", "240", "241", "2411", "2412", "2413",
                                                                             "2414", "2415", "2416", "2417", "2418", "242", "243", "2431", "2432",
                                                                             "24325", "2433", "24335", "2435", "2436", "24365", "2437", "2438",
                                                                             "24383", "2439", "24310", "24315", "2445", "245", "2456", "2463", "247",
                                                                             "2475","248", "120215", "12022A", "12022B", "12022C", "120222A",
                                                                             "120223B", "120225", "653M"), 1, 0),
         property_flag = if_else(oo_code %in% c("220", "70"), 1, 0),
         drug_flag = if_else(jbsis_code %in% c("230", "80"), 1, 0),
         minor_flag = if_else(charge %in% c("fix this"), 1, 0),
         pre_arr_inel_flag = if_else(charge %in% c("fix this"), 1, 0)) %>%
  mutate_at(vars(contains("flag")), funs(if_else(is.na(.), 0, as.numeric(.))))

save(charge_hier, file = "Complete Charge Code Hierarchy.RData")

# write.xlsx(charge_hier, file = "G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Complete Charge Hieararchy with Flags.xlsx", asTable = T, tableStyle = "TableStyleMedium1")
```

  Flag Excel for Legal
```{r}
load("Complete Charge Code Hierarchy.RData")

flag_list <- lapply(8:28, function(i) {
  df <- charge_hier %>%
    select(1:7, i) %>%
    filter_at(8, all_vars(. == 1)) %>%
    mutate(wrong_offense = 0, missing_offense = 0) %>%
    select(1:2, 4:6, 8:10, 3, 7)
}) 

write.xlsx(
  flag_list,
  "Offense Flags for Kara and Eve Sex Offenses.xlsx",
  asTable = T,
  tableStyle = "TableStyleMedium1",
  sheetName = c(
    "Special Allegations",
    "Serious Felonies",
    "Violent Felonies",
    "Serious and Violent Felonies",
    "PSA Violent",
    "Capital Offenses",
    "Domestic Violence",
    "Supervision Violations",
    "Failures to Appear",
    "Marijuana Offenses",
    "Sex Offenses",
    "SB 10 Sex Offenses",
    "DUIs",
    "SB10 DUIs",
    "Restrain Order Vios",
    "Witness Intimidation",
    "SB 10 Onduty Ineligibile",
    "JBSIS Property Offenses",
    "JBSIS Drug Offenses",
    "Minor Offenses",
    "SB 10 Pre Arraign Ineligible"
  ),
  colWidths = "auto",
  firstRow = T
)

flag_defs <- tibble(
  `Excel Tab Name` = c(
    "Special Allegations",
    "Serious Felonies",
    "Violent Felonies",
    "Serious and Violent Felonies",
    "PSA Violent",
    "Capital Offenses",
    "Domestic Violence",
    "Supervision Violations",
    "Failures to Appear",
    "Marijuana Offenses",
    "Sex Offenses",
    "SB 10 Sex Offenses",
    "DUIs",
    "SB10 DUIs",
    "Restrain Order Vios",
    "Witness Intimidation",
    "SB 10 Onduty Ineligibile",
    "JBSIS Property Offenses",
    "JBSIS Drug Offenses",
    "Minor Offenses",
    "SB 10 Pre Arraign Ineligible"
  ),
  `Flag Names` = names(charge_hier)[8:28],
  Definition = NA
)

write.xlsx(
  flag_defs,
  "Offense Flag Definitions for Kara and Eve.xlsx",
  asTable = T,
  tableStyle = "TableStyleMedium1",
  colWidths = "auto",
  firstRow = T
  )

serious_violent <- fread("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Bail Deviation Exclusion List_for review by Pretrial Pilots - updated for research team 4-24-20.csv", header = T)

names(serious_violent) <- c("charge", "master_charge_description", "serious_flag", "violent_flag", "remove", "remove2", "remove3")

serious_violent <- serious_violent %>%
  filter(charge != "", !grepl("Conspiracy", master_charge_description)) %>%
  select(1:4) %>%
  separate_rows(charge, sep = "/") %>%
  mutate_at(vars(contains("flag")), funs(if_else(. == "", 0, 1))) %>%
  mutate(master_charge_description = gsub("\t", "", master_charge_description),
         charge_level = "F",
         charge_code = case_when(grepl("^Veh", charge) ~ "VC",
                                 grepl("^Health", charge) ~ "HS",
                                 grepl("^Military|^Election", charge) ~ "Other",
                                 grepl("^Welf", charge) ~ "WI",
                                 T ~ "PC"),
         charge = gsub("&| |\\.", "", charge),
         charge = gsub("\\/|\\(|\\)| |\\.|\\.*|\\\\.*|\\{|\\}|\\*|^[A-Z]*","", toupper(charge))) %>%
  unite(join_var, charge_level, charge_code, charge, remove = F) %>%
  mutate(master_charge_description = toupper(master_charge_description)) %>%
  select(join_var, master_charge_description, charge_level, charge_code, charge, serious_flag, violent_flag)

missing_df <- anti_join(serious_violent, charge_hier, by = "join_var") 

write.xlsx(missing_df, file = "G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Missing Serious and Violent Charges.xlsx")
```

  
Flag Add Diagnostics
```{r eval=FALSE, include=FALSE}
charge_hier %>%
  summarise_at(vars(dv_flag:violent), sum)

charge_hier %>%
  filter(violent == 1)

# lapply(names(charge_hier)[grepl("flag", names(charge_hier))], function(i){
#   
#   charge_hier %>%
#     filter(get(i) == 1) %>%
#     select(charge_level, charge_code, charge, master_charge_description, i)
#     
# })

#PC 12032, 
#6675 B

charge_hier %>%
  filter(grepl("300008", join_var))

charge_hier %>%
  filter(dv_flag == 1)

charge_hier %>%
  mutate(dv_fake = if_else(grepl("DOMESTIC|SPOUSE|PARTNER|COHABITANT", master_charge_description), 1, 0)) %>%
  count(dv_flag, dv_fake)

flag_list <- lapply(8:28, function(i) {
  df <- charge_hier %>%
    select(1:7, i) %>%
    filter_at(8, all_vars(. == 1)) %>%
    mutate(wrong_offense = 0, missing_offense = 0) %>%
    select(1:2, 4:6, 8:10, 3, 7)
}) 

charge_hier %>%
  select(1:7)

charge_hier[charge_hier[,8] == 1,]

charge_hier 
```

Lawyer Reviewed Flags
```{r}
file <- "G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/Legal Review of Offense Flags.xlsx"

# getSheetNames(file)


df_list <- lapply(c(2:4, 6:22), function(i){
  df <- read_excel(file, sheet = i) %>%
    mutate_all(as.character)
  
  names(df) <- tolower(names(df))
  
  return(df)
})


charge_df <- bind_rows(df_list)

charge_df <- charge_df %>%
  mutate_all(funs(if_else(is.na(.), "0", .))) %>%
  mutate(wrong_offense = if_else(wrong_offense == "1" & grepl("Already captured|repealed|extra numbers", notes), 
                                 "0", 
                                 wrong_offense),
         dv_possible_flag = if_else(grepl("DV depending", notes), "1", "0"),
         charge_level = if_else(charge_level == "0", "Other", charge_level),
         join_var = if_else(!grepl("_.*_", join_var), paste(charge_level, charge_code, charge, sep = "_"), join_var)) %>% 
  select(-c(charge_level, charge_code, charge)) %>%
  separate(join_var, c("charge_level", "charge_code", "charge"), sep = "_", remove = F) %>% 
  filter(wrong_offense != "1") %>%
  select(-contains("notes"), -`sarah review`, -not_charge, -wrong_offense, -missing_offense) %>%
  group_by(join_var) %>%
  mutate_at(vars(hierarchy, jbsis_code, contains("flag")), parse_number) %>%
  summarise_all(max) 
  
  
load("G:/CrimJustice/PretrialAssessmentPilot/Complete Charge Code Hierarchy Base.RData")

#Putting on lawyer reviewed flags
match_df <- charge_hier %>%
  select(join_var) %>%
  inner_join(charge_df, by = "join_var")

match_df2 <- charge_hier %>%
  select(join_var:jbsis_code) %>%
  anti_join(charge_df, by = "join_var") 
  
match_df3 <- charge_df %>%
  anti_join(charge_hier, by = "join_var") 

charge_hier <- bind_rows(match_df, match_df3, match_df2) %>%
  distinct(join_var, .keep_all = T) %>%
  mutate_at(vars(contains("flag")), funs(if_else(is.na(.), 0, .))) %>%
  select(-contains("sb10")) 


#Fixing missing JBSIS Codes
doj_hierarchy_2020_jbsis <- read_excel("G:/CrimJustice/PretrialAssessmentPilot/Charge Definitions and Hierarchy/2020_March04_DOJ_Offense_Table_JBSIS.xlsx")

names(doj_hierarchy_2020_jbsis) <- c("offense_id", "cjis_code", "hierarchy", "charge_level", "charge", "charge_code", "master_charge_description", "sentence", "jbsis_code")

doj_hierarchy_2020_jbsis <- doj_hierarchy_2020_jbsis %>%
  mutate(charge_level = toupper(charge_level),
         charge_level = if_else(!charge_level %in% c("F", "I", "M"), "Other", charge_level),
         charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}|EX|\\+|","", charge)),
         charge_code = if_else(!charge_code %in% c("PC", "VC", "HS", "BP", "WI", "US"), "Other", charge_code)) %>%
  distinct(charge, charge_code, charge_level, .keep_all = T) %>%
  unite(join_var, charge_level, charge_code, charge, remove = F) %>%
  select(join_var, jbsis_code)


charge_hier <- charge_hier %>%
  select(-jbsis_code) %>%
  #Fixing a few codes manually that didn't match on to the DOJ data. We selected the top 7 codes which were not matched.
  left_join(doj_hierarchy_2020_jbsis, by = "join_var") %>%
  mutate(jbsis_code = if_else(join_var == "M_HS_113641A", 230, jbsis_code),
         jbsis_code = if_else(join_var == "M_PC_484488", 220, jbsis_code),
         jbsis_code = if_else(join_var == "M_BP_4140", 230, jbsis_code),
         jbsis_code = if_else(join_var == "F_PC_12020A", 90, jbsis_code),
         jbsis_code = if_else(join_var == "F_PC_45736", 90, jbsis_code))


# Updated 1/7/2021 to match jbsis codes to charges with missing jbsis codes determined by the base charge, when there is no conflict of jbsis codes.
# SB 10 flags are also removed due to its failure. 
charge_hier <- charge_hier %>%
  mutate(charge_start = as.integer(parse_number(charge)),
         jbsis_code = if_else(is.na(jbsis_code)|jbsis_code == 0, 1000, jbsis_code)) %>%
  group_by(charge_level, charge_code, charge_start) %>%
  mutate(n = sum(!(unique(jbsis_code) %in% c(1000, 90, 250, 270)))) %>%
  mutate(jbsis_code = if_else(jbsis_code == 1000 & n %in% 0:1, min(jbsis_code), jbsis_code)) %>%
  ungroup() %>%
  mutate(#Fixing property and drug jbsis flagsdd
         property_flag = if_else(jbsis_code %in% c("220", "70"), 1, 0),
         drug_flag = if_else(jbsis_code %in% c("230", "80"), 1, 0))

save(charge_hier, file = "Complete Charge Code Hierarchy.RData")

# load("Complete Charge Code Hierarchy.RData")
# 
# charge_hier %>%
#   filter(property_flag == 1)
# 
# charge_hier %>%
#   filter(property_flag == 1, grepl("GRAND THEFT", master_charge_description))
# 
# 
# charge_hier %>%
#   filter(property_flag == 1, grepl("487", charge))
# 
# charge_hier %>%
#   filter(property_flag == 0, grepl("GRAND THEFT", master_charge_description))
# 
# charge_hier %>%
#   mutate(property_flag = if_else())


  
# 
# charge_hier %>%
#   ungroup() %>%
#   filter(charge_start == 487) %>%
#   count(jbsis_code, charge_level)
#   filter(jbsis_code == 270)
#   count(jbsis_code)
#   filter(charge_level == "M", jbsis_code < 100)
# 
#   group_by(charge_level, charge_code, charge_start) %>%
#   add_count() %>%
#   arrange(desc(nn))
#   filter(n > 1)
# 
# charge_hier %>%
#   filter(as.integer(parse_number(charge)) == 4324)
# 
# charge_hier %>%
#   filter(grepl("^647[A-Z]", charge))
# 
# sum(unique(c("A", "B", "0")) != 0)
# 
# charge_hier %>%
#   filter(jbsis_code == 1000, special_flag == 0)
# 
# charge_hier <- charge_hier %>%
#   mutate(charge_start = as.integer(parse_number(charge)),
#          jbsis_code = if_else(is.na(jbsis_code)|jbsis_code == 0, 1000, jbsis_code)) %>%
#   group_by(charge_level, charge_code, charge_start) %>%
#   # mutate(n = sum(!(unique(jbsis_code) %in% c(1000, 90, 250, 270)))) %>%
#   mutate(jbsis_code = if_else(jbsis_code == 1000, min(jbsis_code), jbsis_code)) %>%
#   ungroup()

# charge_hier_jbsis %>%
#   filter(charge == "11377A")
# 
# shell.exec(getwd())

# charge_hier %>%
#   filter(grepl("45736", charge))
# 
# doj_hierarchy_2020_jbsis %>%
#   filter(grepl("12020", join_var))

```

