---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}

library(data.table)
library(openxlsx)
library(readxl)
library(lubridate)
library(tidyverse)
library(gdata)
```


# XXXXXXX OLD MODOC SPECIFIC STUFF, no longer relevant as of 10.12.22 extraction
```{r}
# this file should have 386 observations. It had a wierd last line that said "386 Records"
modocCII <- read_csv("G:/CrimJustice/PretrialAssessmentPilot/CII.csv")

modocCII <- modocCII %>%
  rename(oldCII=CII);
#this snippet removed the weird last row

modocCII <- modocCII[-c(387), ]modocCII <- modocCII %>%
  mutate(county="Modoc") %>%
  mutate(cii = gsub("[^0-9]", "", oldCII)) %>%
  mutate(cii = case_when(nchar(cii) == 6 ~ paste0("0000", cii),
              nchar(cii) == 7 ~ paste0("000", cii),
              nchar(cii) == 8 ~ paste0("00", cii),
              nchar(cii) == 9 ~ paste0("0", cii),
              T ~ as.character(cii)),
         cii = if_else(nchar(cii) != 10, NA_character_, (cii)));

modocCII <- modocCII %>%
  select(cii, DOB) %>%
  mutate(DOB=mdy(DOB))
#View(modocCII)
```

```{r}
#write.xlsx(modocCII, "C:/R Work/Append Modoc CIIs/modocCIIplus.xlsx")
modocCII <- read.xlsx("G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/CIIs for DOJ 3 21 2022/modocCIIplus.xlsx")

modocCII <- modocCII %>%
  mutate(DOB = mdy(DOB))
```

# Read in data downloaded from Snowflake
```{r}
#sf <- fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/CIIs for DOJ 3 21 2022/SnowflakeCIIDOB 3 21 2022.csv', header = TRUE)

# sf <- fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/Oct 12 2022/CII for DOJ 10 12 2022.csv', header = TRUE)

sf <- fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/temp files 2.28.23/ciidobs2.28.2023.csv', header = TRUE) 

sf <- sf %>%
  select(-COUNTY)


```
Process Snowflake extract as of 3.22.22 extract requires CII and DOB
```{r}
names(sf) <- c("cii", "DOB")


#this snippet finds any observations that have a digit or any missing values 
# 3.21.22 it finds ("A10707613" and "Unknown" and "")
sf %>%
  mutate(bad = if_else(grepl("\\D", cii) | cii=="", 1, 0)) %>%
  filter(bad == 1)
# 10.12.22 found bad record "A10707613"


sf <- sf %>%
  mutate(bad = if_else(grepl("\\D", cii) | cii=="", 1, 0)) %>%
  filter(bad == "0") %>%
  select(-bad)


#bind Modoc and Snowflake CIIs
#10.12.22 no longer have separate modoc extract
# doj_cii_3_21_2022 <- bind_rows(modocCII, sf) %>% 
#   distinct()
```

Import data from counties not processed into Snowflake yet (2.28.23 extract)
Kings
```{r}
k1 <- fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/temp files 2.28.23/Kings/1st Quarter 2022-23.csv', header = F, colClasses=c("character")) 

k2 <- fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/temp files 2.28.23/Kings/2nd Quarter 2022-23.csv', header = F, colClasses=c("character"))

k3 <- fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/temp files 2.28.23/Kings/3rd Quarter 2021-22.csv', header = F, colClasses=c("character"))

k4 <- fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/temp files 2.28.23/Kings/4th Quarter 2021-22.csv', header = F, colClasses=c("character"))

k <- k1 %>%
  bind_rows(k2) %>%
  bind_rows(k3) %>%
  bind_rows(k4)

k <- k %>%
  select(V2, V10)

names(k) <- c("cii", "DOB")

k <- k %>%
  distinct()

k <- k %>%
   mutate(
         cii = parse_number(cii),
         cii = case_when(nchar(cii) == 6 ~ paste0("0000", cii),
                         nchar(cii) == 7 ~ paste0("000", cii),
                         nchar(cii) == 8 ~ paste0("00", cii),
                         nchar(cii) == 9 ~ paste0("0", cii),
                         T ~ as.character(cii)),
         cii = if_else(nchar(cii) != 10, NA_character_, cii)) %>%
  mutate(DOB = mdy(DOB))
```
San Joaquin
```{r}
sj <- fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/temp files 2.28.23/San Joaquin/Jail_Individual.csv', header = T, colClasses=c("character")) 

sj<- sj %>%
  select(CII, DOB)

names(sj) <- c("cii", "DOB")

sj <- sj %>%
   mutate(
         cii = parse_number(cii),
         cii = case_when(nchar(cii) == 6 ~ paste0("0000", cii),
                         nchar(cii) == 7 ~ paste0("000", cii),
                         nchar(cii) == 8 ~ paste0("00", cii),
                         nchar(cii) == 9 ~ paste0("0", cii),
                         T ~ as.character(cii)),
         cii = if_else(nchar(cii) != 10, NA_character_, cii)) %>%
  mutate(DOB = mdy(DOB))

sj <- sj %>%
  distinct()
```
Yuba
```{r}
yu <- fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/temp files 2.28.23/Yuba/2023-01-05-Jail.csv', header = T, colClasses=c("character")) %>%
  bind_rows(fread(file = 'G:/CrimJustice/PretrialAssessmentPilot/temp files 2.28.23/Yuba/2023-02-10-Jail.csv', header = T, colClasses=c("character")))

yu <- yu %>%
  select(STATIP, BIRTHDATE)

names(yu) <- c("cii", "DOB")

yu <- yu %>%
   mutate(
         cii = parse_number(cii),
         cii = case_when(nchar(cii) == 6 ~ paste0("0000", cii),
                         nchar(cii) == 7 ~ paste0("000", cii),
                         nchar(cii) == 8 ~ paste0("00", cii),
                         nchar(cii) == 9 ~ paste0("0", cii),
                         T ~ as.character(cii)),
         cii = if_else(nchar(cii) != 10, NA_character_, cii)) %>%
  mutate(DOB = mdy(DOB))

yu <- yu %>%
  distinct()
```
counts
```{r}
k %>%
  count() # 3,482 as of 2/28/23

sj %>%
  count() #50,752 as of 2/28/23

yu %>%
  count() # 1,820 as of 2/28/23
```
Combine non-snowflake counties with Snowflake counties
```{r}
sf <- sf %>%
  mutate(DOB = as.Date(DOB))

sf <- sf %>%
  bind_rows(k) %>%
  bind_rows(sj) %>%
  bind_rows(yu)

sf <- sf %>%
  distinct()
```


Format data 10/12/22
```{r}
#Format DOB and add spacer variables for required formatting specifications
doj_cii_10_12_2022 <- sf %>%
  mutate(DOBstring=format(DOB,"%Y%m%d")) %>%
  mutate(spacer1=str_pad("",30), spacer2=str_pad("",30)) %>%
  select(cii, spacer1,DOBstring, spacer2)

#from email from DataRequests 3.22.22 "Per the CSD the CII number must begin with ‘10’, ‘30’, ‘32’, ‘40’, or ‘00’. Otherwise, use two spaces to fill."
#mark rows for removal if CII does not begin with the specified numbers
doj_invalid_removed <- doj_cii_10_12_2022 %>%
  mutate(remove = if_else(grepl("^00|^10|^30|^40|^32", cii), 0, 1))

doj_invalid_removed %>%
  filter(remove == 1)
#10.12.22 519 records tagged for removal based on starting two digits

# email from DataRequests 3.22.22 "Per the CSD the file cannot contain more than one record for each CII number submitted."
# remove records flagged as starting with the wrong digits and distinct on CIIs because DOJ will not accept multiple rows per CII even if associated with a different DOB. 
doj_invalid_removed <- doj_invalid_removed %>%
  filter(remove ==0) %>%
  select(-remove) %>%
  distinct(cii, .keep_all = T)



#diagnostic, CIIs with multiple rows
doj_invalid_removed %>%
  add_count(cii) %>%
  filter(n>1) %>%
  arrange(cii)
# no duplicates in de-duped df
doj_cii_10_12_2022 %>%
    add_count(cii) %>%
  filter(n>1) %>%
  arrange(cii)
#duplicates in pre-de-duped df


#combine columns into one column as required by DOJ formatting guidelines
doj_single <- doj_invalid_removed %>%
  unite("all", cii:spacer2, sep= "", remove = T)

#check that all rows have the correct number of characters
doj_single %>%
  mutate(n = nchar(all)) %>%
  count(n)


#one more distinct, just in case
doj_single <- doj_single %>%
  distinct()




# no longer paert of DOJ process, we need
#doj_cii_3_18_2022$recordid=seq(from=100000000001, by=1, length = nrow(doj_cii_3_18_2022))
#doj_cii_3_18_2022 <- doj_cii_3_18_2022 %>%
# mutate(recordid=as.character(recordid)) %>%
# select(recordid, cii)#doj_cii_3_18_2022 <- doj_cii_3_18_2022 %>%
#unite(idcii, c("recordid","cii"), sep="|", remove=T)


```

Format data 2/28/23
```{r}
#Format DOB and add spacer variables for required formatting specifications
doj_cii_2_28_23 <- sf %>%
  mutate(DOBstring=format(DOB,"%Y%m%d")) %>%
  mutate(spacer1=str_pad("",30), spacer2=str_pad("",30)) %>%
  select(cii, spacer1,DOBstring, spacer2)

#from email from DataRequests 3.22.22 "Per the CSD the CII number must begin with ‘10’, ‘30’, ‘32’, ‘40’, or ‘00’. Otherwise, use two spaces to fill."
#mark rows for removal if CII does not begin with the specified numbers
doj_invalid_removed <- doj_cii_2_28_23 %>%
  mutate(remove = if_else(grepl("^00|^10|^30|^40|^32", cii), 0, 1))

doj_invalid_removed %>%
  filter(remove == 1)
#10.12.22 519 records tagged for removal based on starting two digits

# email from DataRequests 3.22.22 "Per the CSD the file cannot contain more than one record for each CII number submitted."
# remove records flagged as starting with the wrong digits and distinct on CIIs because DOJ will not accept multiple rows per CII even if associated with a different DOB. 
doj_invalid_removed <- doj_invalid_removed %>%
  filter(remove ==0) %>%
  select(-remove) %>%
  distinct(cii, .keep_all = T)

# remove missing DOBs introduced by non-snowflake counties
doj_invalid_removed <- doj_invalid_removed %>%
  filter(!is.na(DOBstring))

#diagnostic, CIIs with multiple rows
doj_invalid_removed %>%
  add_count(cii) %>%
  filter(n>1) %>%
  arrange(cii)
# no duplicates in de-duped df
doj_cii_2_28_23 %>%
    add_count(cii) %>%
  filter(n>1) %>%
  arrange(cii)
#duplicates in pre-de-duped df


#combine columns into one column as required by DOJ formatting guidelines
doj_single <- doj_invalid_removed %>%
  unite("all", cii:spacer2, sep= "", remove = T)

#check that all rows have the correct number of characters
doj_single %>%
  mutate(n = nchar(all)) %>%
  count(n)

doj_single %>%
  mutate(n = nchar(all)) %>%
  filter(n == 72)

#one more distinct, just in case
doj_single <- doj_single %>%
  distinct()




# no longer paert of DOJ process, we need
#doj_cii_3_18_2022$recordid=seq(from=100000000001, by=1, length = nrow(doj_cii_3_18_2022))
#doj_cii_3_18_2022 <- doj_cii_3_18_2022 %>%
# mutate(recordid=as.character(recordid)) %>%
# select(recordid, cii)#doj_cii_3_18_2022 <- doj_cii_3_18_2022 %>%
#unite(idcii, c("recordid","cii"), sep="|", remove=T)


```

Write to file for upload to DOJ
```{r}
# write.fwf(doj_single, file="senddoj_cii_3_22_2022.txt", sep="", na="NULL",
# rownames=FALSE, colnames=FALSE, justify="left",
# formatInfo=FALSE, quoteInfo=TRUE, width=78, eol="\r",
# scientific=FALSE)
# 
# 
# 
# write.fwf(doj_single, file="G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/CIIs for DOJ 3 21 2022/senddoj_cii_3_22_2022.txt", sep="", na="NULL",
# rownames=FALSE, colnames=FALSE, justify="left",
# formatInfo=FALSE, quoteInfo=TRUE, width=78, eol="\r",
# scientific=FALSE)

# write to a fixed width txt file with carriage returns at the end of each line, each line width 78 characters, as required by DOJ
write.fwf(doj_single, file="G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/Oct 12 2022/senddoj_cii_10_12_2022.txt", sep="", na="NULL",
rownames=FALSE, colnames=FALSE, justify="left",
formatInfo=FALSE, quoteInfo=TRUE, width=78, eol="\r",
scientific=FALSE)

# 2.28.23
write.fwf(doj_single, file="G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/February 2023/senddoj_cii_2_28_2023.txt", sep="", na="NULL",
rownames=FALSE, colnames=FALSE, justify="left",
formatInfo=FALSE, quoteInfo=TRUE, width=78, eol="\r",
scientific=FALSE)
```

```{r}
#write.csv(doj_cii_3_18_2022, "C:/R Work/Append Modoc CIIs/doj_cii_3_18_2022.csv", row.names=F, quote=F)
```

Pull in cii files to re-process for new DOJ format requirements 3.7.23
```{r}
c1 <- fread("G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/Oct 12 2022/senddoj_cii_10_12_2022.txt", colClasses = c("character"))

c2 <- fread("G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/February 2023/senddoj_cii_2_28_2023.txt", colClasses = c("character"))

c <- c1 %>%
  bind_rows(c2)

names(c) <- c("cii", "dob")

c <- c %>%
  select(cii)

c <- c %>%
  distinct()

c <- c %>%
  mutate(id = as.character(row_number() + 100000000000)) %>%
  select(id, cii)

c <- c %>%
  unite("id|cii", id:cii, sep= "|", remove = T)

write.fwf(c, file="G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/February 2023/senddoj_cii_3_7_2023.txt", sep="", na="NULL",
rownames=FALSE, colnames=FALSE, justify="left",
formatInfo=FALSE, quoteInfo=TRUE, width=23, eol="\r",
scientific=FALSE)
```

?fread
