---
title: "R Notebook"
output: html_notebook
---
Libraries
```{r setup}
library(gsubfn)
library(lubridate)
library(openxlsx)
library(readxl)
library(fuzzyjoin)
# library(pROC)
library(tidyverse)
#library(tools)
library(data.table)
```

Loading in Full DOJ RRF Data
```{r eval=FALSE, include=FALSE}
#files <- list.files("D:/DOJ Pretrial Pilot Data/19-148/Output", full.names = T)
files <- list.files("C:/temp files for transfer 3.30.22/Run 05/unzipped", full.names = T)

#1st Partition
doj_df <- lapply(files[2:38], function(x){
  
  df <- read.csv(x, colClasses = "character", header = F) %>%
    select_if(function(x) !(all(is.na(x)) | all(x=="") | all(x=="#")))
  
  return(df)
})

doj_df <- doj_df %>% bind_rows()

fwrite(doj_df, file = "1 of 2 CORI CII Pretrial Dataset.csv")
rm(doj_df)

#2nd Partition
doj_df2 <- lapply(files[39:77], function(x){
  
  df <- read.csv(x, colClasses = "character", header = F) %>%
    select_if(function(x) !(all(is.na(x)) | all(x=="") | all(x=="#")))
  
  return(df)
})

doj_df2 <- doj_df2 %>% bind_rows()

fwrite(doj_df2, file = "2 of 2 CORI CII Pretrial Dataset.csv")
rm(doj_df2)

# Combinging First Partition with Headers
doj_df <- fread("1 of 2 CORI CII Pretrial Dataset.csv", colClasses = "character")

#Top with Headers, except this time they did not  give us headers
top_doj <- read.csv(files[1], colClasses = "character", header = F)
top_doj <- read_fwf(files[1])

top_doj <- top_doj %>%
  select_if(function(x) !(all(is.na(x)) | all(x=="") | all(x=="#")))

names(doj_df) <- names(top_doj)

doj_df <- bind_rows(top_doj, doj_df)

doj_df <- doj_df %>%
  filter(as_date(CYC_DATE) >= "2012-01-01")

#Combining Second Partition
doj_df2 <- fread("2 of 2 CORI CII Pretrial Dataset.csv", colClasses = "character")

names(doj_df2) <- names(top_doj)

doj_df2 <- doj_df2 %>%
  filter(as_date(CYC_DATE) >= "2012-01-01")

doj_df <- bind_rows(doj_df, doj_df2)

fwrite(doj_df, file = "CORI CII Pretrial Dataset Post 2012.csv")

rm(top_doj, doj_df2)

# fread(files[1])

# c(12, 2, 12, 1, 10, 30, 1, 8, 8, 9, 1, 10, 30, 1, 8, 9, 8, 8, 8, 9, 1, 1, 15, 3, 30, 3, 30, 3, 3, 1, 1, 2, 30, 8, 30, 1, 12, 8, 1, 12, 8, 2, 30, 1, 25, 9, 25, 2, 30, 1, 12, 8, 20, 5, 50, 1, 30, 5, 50, 1, 30, 12, 5, 50, 1, 30, 12, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 12, 4, 40, 1, 20, 1, 12, 2, 15, 3, 1, 15, 3, 1, 1, 150, 1)

read_fwf(files[1], col_positions = fwf_widths(c(12, 2, 12, 1, 10, 30, 1, 8, 8, 9, 1, 10, 30, 1, 8, 9, 8, 8, 8, 9, 1, 1, 15, 3, 30, 3, 30, 3, 3, 1, 1, 2, 30, 8, 30, 1, 12, 8, 1, 12, 8, 2, 30, 1, 25, 9, 25, 2, 30, 1, 12, 8, 20, 5, 50, 1, 30, 5, 50, 1, 30, 12, 5, 50, 1, 30, 12, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 12, 4, 40, 1, 20, 1, 12, 2, 15, 3, 1, 15, 3, 1, 1, 150, 1), col_names = c("RECORD_ID", "SUBJECT_STATUS", "SUBJECT_ID",
"REQ_SEG_SEP", "REQ_CII_NUMBER", "REQ_NAME", "REQ_GENDER", "REQ_DOB", "REQ_CDL", "REQ_SSN", "PII_SEG_SEP",
"CII_NUMBER", "PRI_NAME", "GENDER", "PRI_DOB", "PRI_SSN", "PRI_CDL", "PRI_IDN", "PRI_INN", "FBI_NUMBER", "PDR_SEG_SEP",
"RACE_CODE", "RACE_DESCR", "EYE_COLOR_CODE", "EYE_COLOR_DESCR", "HAIR_COLOR_CODE", "HAIR_COLOR_DESCR",
"HEIGHT", "WEIGHT", "SINGLE_SOURCE", "MULTI_SOURCE", "POB_CODE", "POB_NAME", "POB_TYPE", "CITIZENSHIP_LIST",
"CYC_SEG_SEP","CYC_ORDER", "CYC_DATE", "STP_SEG_SEP", "STP_ORDER", "STP_EVENT_DATE", "STP_TYPE_CODE", "STP_TYPE_DESCR",
"STP_ORI_TYPE", "STP_ORI_TYPE_DESCR", "STP_ORI_CODE", "STP_ORI_DESCR", "STP_ORI_CNTY_CODE", "STP_ORI_CNTY_NAME",
"CNT_SEG_SEP", "CNT_ORDER", "DISP_DATE", "OFN", "OFFENSE_CODE", "OFFENSE_DESCR", "OFFENSE_TOC", "OFFENSE_QUAL_LST",
"DISP_OFFENSE_CODE", "DISP_OFFENSE_DESCR", "DISP_OFFENSE_TOC", "DISP_OFFENSE_QUAL_LST", "CONV_OFFENSE_ORDER", "CONV_OFFENSE_CODE", "CONV_OFFENSE_DESCR",
"CONV_OFFENSE_TOC", "CONV_OFFENSE_QUAL_LST", "FE_NUM_ORDER", "FE_NUM_ARR_AGY", "FE_NUM_BNCH_WARR", "FE_NUM_CITE", "FE_NUM_DOCKET",
"FE_NUM_INCIDENT", "FE_NUM_BOOKING", "FE_NUM_NUMBER", "FE_NUM_REMAND", "FE_NUM_OOS_INN", "FE_NUM_CRT_CASE", "FE_NUM_WARRANT",
"DISP_ORDER", "DISP_CODE", "DISP_DESCR", "CONV_STAT_CODE", "CONV_STAT_DESCR", "SENT_SEG_SEP",
"SENT_ORDER", "SENT_LOC_CODE", "SENT_LOC_DESCR", "SENT_LENGTH", "SENT_TIME_CODE", "SENT_TIME_DESCR", "CYC_AGE", "CII_TYPE", "CII_TYPE_ALPHA", "COMMENT_TEXT", "END_OF_REC")))

# c("RECORD_ID", "SUBJECT_STATUS", "SUBJECT_ID",
# "REQ_SEG_SEP",
# "REQ_CII_NUMBER", "REQ_NAME", "REQ_GENDER", "REQ_DOB", "REQ_CDL", "REQ_SSN",
# "PII_SEG_SEP",
# "CII_NUMBER", "PRI_NAME", "GENDER", "PRI_DOB", "PRI_SSN", "PRI_CDL", "PRI_IDN", "PRI_INN", "FBI_NUMBER",
# "PDR_SEG_SEP",
# "RACE_CODE", "RACE_DESCR", "EYE_COLOR_CODE", "EYE_COLOR_DESCR", "HAIR_COLOR_CODE", "HAIR_COLOR_DESCR",
# "HEIGHT", "WEIGHT", "SINGLE_SOURCE", "MULTI_SOURCE", "POB_CODE", "POB_NAME", "POB_TYPE", "CITIZENSHIP_LIST",
# "CYC_SEG_SEP","CYC_ORDER", "CYC_DATE",
# "STP_SEG_SEP",
# "STP_ORDER", "STP_EVENT_DATE", "STP_TYPE_CODE", "STP_TYPE_DESCR",
# "STP_ORI_TYPE", "STP_ORI_TYPE_DESCR", "STP_ORI_CODE", "STP_ORI_DESCR",
# "STP_ORI_CNTY_CODE", "STP_ORI_CNTY_NAME",
# "CNT_SEG_SEP",
# "CNT_ORDER", "DISP_DATE", "OFN", "OFFENSE_CODE", "OFFENSE_DESCR", "OFFENSE_TOC", "OFFENSE_QUAL_LST",
# "DISP_OFFENSE_CODE", "DISP_OFFENSE_DESCR", "DISP_OFFENSE_TOC", "DISP_OFFENSE_QUAL_LST",
# "CONV_OFFENSE_ORDER", "CONV_OFFENSE_CODE", "CONV_OFFENSE_DESCR",
# "CONV_OFFENSE_TOC", "CONV_OFFENSE_QUAL_LST",
# "FE_NUM_ORDER", "FE_NUM_ARR_AGY", "FE_NUM_BNCH_WARR", "FE_NUM_CITE", "FE_NUM_DOCKET",
# "FE_NUM_INCIDENT", "FE_NUM_BOOKING", "FE_NUM_NUMBER", "FE_NUM_REMAND", "FE_NUM_OOS_INN",
# "FE_NUM_CRT_CASE", "FE_NUM_WARRANT",
# "DISP_ORDER", "DISP_CODE", "DISP_DESCR", "CONV_STAT_CODE", "CONV_STAT_DESCR",
# "SENT_SEG_SEP",
# "SENT_ORDER", "SENT_LOC_CODE", "SENT_LOC_DESCR", "SENT_LENGTH", "SENT_TIME_CODE", "SENT_TIME_DESCR",
# "CYC_AGE", "CII_TYPE", "CII_TYPE_ALPHA", "COMMENT_TEXT",
# "END_OF_REC")
```

```{r}
ct <- "ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc"

doj_df <- lapply(files, function(x){
  
  df <- read_fwf(x, 
                 col_positions = fwf_widths(c(12, 2, 12, 1, 10, 30, 1, 8, 8, 9, 1, 10, 30, 1, 8, 9, 8, 8, 8, 9, 1, 1, 15, 3, 30, 3, 30, 3, 3, 1, 1, 2, 30, 8, 30, 1, 12, 8, 1, 12, 8, 2, 30, 1, 25, 9, 25, 2, 30, 1, 12, 8, 20, 5, 50, 1, 30, 5, 50, 1, 30, 12, 5, 50, 1, 30, 12, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 12, 4, 40, 1, 20, 1, 12, 2, 15, 3, 1, 15, 3, 1, 1, 150, 1), 
                 col_names = c("RECORD_ID", "SUBJECT_STATUS", "SUBJECT_ID",
"REQ_SEG_SEP", "REQ_CII_NUMBER", "REQ_NAME", "REQ_GENDER", "REQ_DOB", "REQ_CDL", "REQ_SSN", "PII_SEG_SEP",
"CII_NUMBER", "PRI_NAME", "GENDER", "PRI_DOB", "PRI_SSN", "PRI_CDL", "PRI_IDN", "PRI_INN", "FBI_NUMBER", "PDR_SEG_SEP",
"RACE_CODE", "RACE_DESCR", "EYE_COLOR_CODE", "EYE_COLOR_DESCR", "HAIR_COLOR_CODE", "HAIR_COLOR_DESCR",
"HEIGHT", "WEIGHT", "SINGLE_SOURCE", "MULTI_SOURCE", "POB_CODE", "POB_NAME", "POB_TYPE", "CITIZENSHIP_LIST",
"CYC_SEG_SEP","CYC_ORDER", "CYC_DATE", "STP_SEG_SEP", "STP_ORDER", "STP_EVENT_DATE", "STP_TYPE_CODE", "STP_TYPE_DESCR",
"STP_ORI_TYPE", "STP_ORI_TYPE_DESCR", "STP_ORI_CODE", "STP_ORI_DESCR", "STP_ORI_CNTY_CODE", "STP_ORI_CNTY_NAME",
"CNT_SEG_SEP", "CNT_ORDER", "DISP_DATE", "OFN", "OFFENSE_CODE", "OFFENSE_DESCR", "OFFENSE_TOC", "OFFENSE_QUAL_LST",
"DISP_OFFENSE_CODE", "DISP_OFFENSE_DESCR", "DISP_OFFENSE_TOC", "DISP_OFFENSE_QUAL_LST", "CONV_OFFENSE_ORDER", "CONV_OFFENSE_CODE", "CONV_OFFENSE_DESCR",
"CONV_OFFENSE_TOC", "CONV_OFFENSE_QUAL_LST", "FE_NUM_ORDER", "FE_NUM_ARR_AGY", "FE_NUM_BNCH_WARR", "FE_NUM_CITE", "FE_NUM_DOCKET",
"FE_NUM_INCIDENT", "FE_NUM_BOOKING", "FE_NUM_NUMBER", "FE_NUM_REMAND", "FE_NUM_OOS_INN", "FE_NUM_CRT_CASE", "FE_NUM_WARRANT",
"DISP_ORDER", "DISP_CODE", "DISP_DESCR", "CONV_STAT_CODE", "CONV_STAT_DESCR", "SENT_SEG_SEP",
"SENT_ORDER", "SENT_LOC_CODE", "SENT_LOC_DESCR", "SENT_LENGTH", "SENT_TIME_CODE", "SENT_TIME_DESCR", "CYC_AGE", "CII_TYPE", "CII_TYPE_ALPHA", "COMMENT_TEXT", "END_OF_REC")),
                col_types = ct) 
  
  return(df)
})

doj_d <- doj_df %>% bind_rows() %>%
    select_if(function(x) !(all(is.na(x)) | all(x=="") | all(x=="#"))) %>%
    filter(as_date(CYC_DATE) >= "2012-01-01") #fix this with more appropriate date cutoff

fwrite(doj_d, file = "CORI CII Pretrial Dataset Post 2012 4.5.22.csv")

```


Cleaning--Only looking at 2016-11-08+ for now.
```{r}
doj_d <- fread("CORI CII Pretrial Dataset Post 2012.csv", colClasses = "character")

doj_df <- doj_d %>%
  #Earliest assessment
  filter(as_date(CYC_DATE) >= "2016-11-08")

doj_df <- doj_df %>%
  ungroup() %>%
  select(4,6:7, 21:24,26,28,32,34:38,48,50,52:59, DISP_CODE, DISP_DESCR) %>%
  mutate(DISP_CODE = as.numeric(DISP_CODE)) %>%
  mutate(arrested_flag = if_else(grepl("ARREST", STP_TYPE_DESCR), 1, 0),
       filed_flag = if_else(grepl("COURT", STP_TYPE_DESCR), 1, 0),
       convicted_flag = if_else(DISP_CODE %in% c(2500:2799), 1, 0),
       dismissed_flag = if_else(DISP_CODE %in% c(50:299, 450:549, 550:599, 1000:1299, 1900:2199, 2800:3099), 1, 0),
       acquitted_flag = if_else(DISP_CODE %in% c(3100:3399), 1, 0),
       non_final_disp_flag = if_else(DISP_CODE %in% c(0:50, 300:449, 600:999, 1300:1899, 2200:2499, 3400:5000), 1, 0),
       arrest_disp_flag = if_else(DISP_CODE %in% c(50:299, 1000:1299), 1, 0),
       pros_disp_flag = if_else(DISP_CODE %in% c(450:549, 1900:2199), 1, 0),
       court_disp_flag = if_else(DISP_CODE %in% c(550:599, 2500:3399), 1, 0)) %>% # disposition code list provided by DOJ
  mutate(SENTENCE_DATE = if_else(SENT_ORDER != "", STP_EVENT_DATE, ""),
         DISP_DATE = if_else(!is.na(DISP_CODE) & DISP_DATE == "", STP_EVENT_DATE , DISP_DATE),
         DISP_DATE = if_else(non_final_disp_flag == 1, "" , DISP_DATE)) %>%
  filter(!grepl("ADDITIONAL ACTION", STP_TYPE_DESCR)) %>%
  separate(OFFENSE_DESCR, c("charge","doj_charge_description"), sep = "-") %>%
  separate(charge, c("charge", "charge_code"), sep = " " ) %>%
  mutate(charge_original = charge) %>%
  mutate(charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}","", charge))) %>%
  rename(charge_level = OFFENSE_TOC) %>%
  unite(join_var, charge_level, charge_code, charge, remove = T)


  
save(doj_df, file = "CORI CII Pretrial Dataset Post 2018 4.6.22.RData")

```

Hierarchy
```{r}
# doj_df <- doj_df %>%
#   select(-c(OFFENSE_TOC, charge, code_type)) %>%
#   rename(doj_charge_description = desc)

load("Complete Charge Code Hierarchy.RData")

doj_df <- left_join(doj_df, charge_hier) 

doj_df <- doj_df %>%
  ungroup() %>%
  mutate(felony_flag = if_else(charge_level == "F", 1, 0),
         misd_flag = if_else(charge_level == "M", 1, 0)) %>%
  mutate_if(is.numeric, funs(if_else(is.na(.), 0, .))) %>%
  mutate(hierarchy = if_else(hierarchy == 0, 1e6, hierarchy)) 
 
# ?mutate_if
# charge_list <- doj_df %>%
#   count(charge, desc) %>%
#   arrange(desc(n))
# 
# write.xlsx(charge_list, file = "All DOJ Charges.csv")
# 
# charge_hier
```

XXXXXXXX Flag Adds--Old Not Used (flags now already in hierarchy)
```{r eval=FALSE, include=FALSE}
#Adding dv and sup_vio flags to data.
doj_df <- doj_df %>%
  select(-charge_level) %>%
  rename(charge_level = OFFENSE_TOC) %>%
  mutate(dv_flag = if_else(grepl("DOMESTIC|SPOUSE|PARTNER|COHABITANT", desc), 1, 0),
         sup_vio_flag = if_else(grepl("^SUP| SUP |SUPERVISION|PROBATION|PAROLE|SUPV ", desc), 1, 0),
         fta_flag = if_else(grepl("APPEAR|FTA", desc), 1, 0),
         enhancement_flag = if_else(grepl("ENHANCE", desc), 1, 0),
         marijuana_flag = if_else(grepl("MARIJUANA|HASH|CANNAB", desc), 1, 0),
         #Disorderly Conduct, Driving without a Licencse, Contempt, Posession of Controlled Substance, Paraphenlia, Under Influence, False ID, 
         #Possess Burg Tools, Fail to prove financial responsibility, LIc Suspended, Pos Marijuna for Sale, Vandalism less than $400
         #Under Influence, Possession w/out prescriptioin, Reg of cntrl sub, App lost property, Poss canabis, Poss hyp needle, Furnish MJ, No REJ Vehicle
         #Flash Incarceration, Noise, Plan Marijuana
         minor_flag = if_else(charge %in% c("647F", "12500A", "146011A", "146012A", "166A4", "11377A", 
                                            "11354A", "11364A", "11550A", "1489A", "466", "16028A", 
                                            "146015A", "11359", "594B2A", "11550", "4060", "11590", "11375B2",
                                            "485", "11357A", "4140", "11360A", "4000A", "3454", "4152", "11358"), 1, 0),
         misd_flag = if_else(charge_level == "M" & sup_vio_flag == 0 & fta_flag == 0 & minor_flag == 0, 1, 0),
         felony_flag = if_else(charge_level == "F" & sup_vio_flag == 0 & fta_flag == 0 & minor_flag == 0, 1, 0)) 

#Serious and Violent
serious_violent_charges <- read_excel("Serious and Violent Charges.xlsx", sheet = "Data") %>%
  select(charge, charge_level, serious = Serious, violent = Violent) %>%
  filter(serious == 1 | violent == 1) %>%
  mutate(charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|\\\\.*|\\{|\\}","", charge))) %>%
  mutate(charge = gsub("HSC", "HS_", charge),
         charge = gsub("PEN", "PC_", charge),
         charge = gsub("VEH", "VC_", charge)) %>%
  unite(join_var, charge_level, charge) %>%
  mutate(serious = if_else(serious == T, 1, 0),
         violent = if_else(violent == T, 1, 0)) %>%
  mutate_all(funs(ifelse(is.na(.), 0, .))) %>%
  distinct(join_var, .keep_all = T)

doj_df <- doj_df %>%
  left_join(serious_violent_charges, by = "join_var") %>%
  mutate_at(vars(serious, violent), funs(if_else(is.na(.), 0, .))) %>%
  ungroup() %>%
  mutate(hierarchy = if_else(is.na(hierarchy), 1e6, as.numeric(hierarchy))) %>%
  select(-c(OFFENSE_QUAL_LST, DISP_ORDER, CONV_STAT_DESCR, SENT_LOC_CODE, SENT_TIME_CODE, CYC_AGE))

sf_violent_df <- read_csv("Final cleaned SF Violent Charges.csv") %>%
  select(-X1)

attributes(sf_violent_df)$spec <- NULL
sf_violent_df <- tibble(join_var = as.character(sf_violent_df$join_var), sf_violent = as.numeric(sf_violent_df$sf_violent))

doj_df <- doj_df %>%
  left_join(sf_violent_df, by = "join_var") %>%
  mutate(sf_violent = if_else(is.na(sf_violent), 0, sf_violent))

# SF Violent
# sf_violent_df <- read_csv("Cleaned SF Violent Charges.csv")
# 
# sf_violent_df <- sf_violent_df %>%
#   mutate(sf_violent = 1) %>%
#   unite(join_var, charge_level, code_type, charge, remove = F) %>%
#   distinct(join_var, sf_violent)
# 
# sf_violent_df <- as.tibble(sf_violent_df)

# write.csv(sf_violent_df, file = "Final cleaned SF Violent Charges.csv")

save(doj_df, file = "Cleaned Full Matched DOJ Data.RData")
```

Collapse to Booking and Court
```{r}
# doj_df <- fread("CORI CII Pretrial Dataset Post 2012.csv", colClasses = "character")

# court_dispo is an intermediate flag to make sure dispostion is only related to court actions 
doj_df <- doj_df %>%
  rename(CII_NUMBER = REQ_CII_NUMBER) %>%
  # mutate(court_dispo_flag = if_else(STP_ORI_TYPE_DESCR == "Court", 1, 0),
  #        dispo_flag = if_else(court_dispo_flag == 1 | DISP_DESCR != "", 1, 0)) %>%
  # mutate(SENTENCE_DATE = if_else(SENT_ORDER != "", STP_EVENT_DATE, ""),
  #        DISP_DATE = if_else(DISP_DESCR != "" & DISP_DATE == "", STP_EVENT_DATE, DISP_DATE),
  #        DISP_DATE = if_else(STP_ORI_TYPE_DESCR == "Court" & DISP_DATE == "", STP_EVENT_DATE, DISP_DATE)) %>%
  group_by(CII_NUMBER, CYC_DATE) %>%
  mutate(arrest_date = min(STP_EVENT_DATE),
         SENTENCE_DATE = max(SENTENCE_DATE), # LOOK AT THIS -- should this be min instead of max????? ******************** (currently formatted as character, so if you take min it will mess it up, change format or otherwise deal with this)
         DISP_DATE = max(DISP_DATE)) %>%
  ungroup() %>%
  select(-c(SENT_ORDER:SENT_TIME_DESCR))

#save(doj_df, file = "Cleaned uncollapsed DOJ Data 4.6.22.RData")

# load("Cleaned uncollapsed DOJ Data 4.6.22.RData")


coll_df <- doj_df %>%
  mutate(CYC_DATE = ymd(CYC_DATE),
         STP_EVENT_DATE = ymd(STP_EVENT_DATE),
         DISP_DATE = ymd(DISP_DATE),
         SENTENCE_DATE = ymd(SENTENCE_DATE),
         arrest_date = ymd(arrest_date)) %>% 
  mutate_at(vars(special_flag:dv_possible_flag, -hierarchy), funs("arrest" = if_else(. == 1 & STP_ORI_TYPE_DESCR == "Arrest", 1, 0))) %>%
  mutate_at(vars(special_flag:dv_possible_flag, -hierarchy), funs("court" = if_else(. == 1 & STP_ORI_TYPE_DESCR == "Court", 1, 0))) %>%
  mutate_at(vars(special_flag:dv_possible_flag, -hierarchy), funs("conviction" = if_else(. == 1 & convicted_flag == 1, 1, 0))) %>%
  rename_at(vars(ends_with("arrest")), funs(paste0("arrest_", gsub("_arrest", "", .)))) %>%
  rename_at(vars(ends_with("court")), funs(paste0("court_", gsub("_court", "", .)))) %>%
  rename_at(vars(ends_with("conviction")), funs(paste0("conviction_", gsub("_conviction", "", .)))) %>%
  mutate(pretrial_end_date = if_else(DISP_DATE <= SENTENCE_DATE | is.na(SENTENCE_DATE), DISP_DATE, SENTENCE_DATE)) %>%
  group_by(CII_NUMBER, CYC_DATE) %>%
  mutate_at(vars(contains("flag")), max) %>%
  # mutate(pretrial_dispo_date = if_else(convicted == 1|dismissed == 1, max(STP_EVENT_DATE[convicted == 1|dismissed == 1]), as_date(NA))) %>%
  # mutate(max_hier = min(hierarchy),
  #        max_charge = charge[hierarchy == max_hier][1],
  #        max_descrip = off_descrip[hierarchy == max_hier][1]) %>%
  # mutate(max_conv_charge = charge[grepl("^CONVICTED", DISP_DESCR)][1],
  #        max_conv_descrip = off_descrip[grepl("^CONVICTED", DISP_DESCR)][1],
  #        max_conv_hier = hierarchy[max_conv_charge == charge][1]) %>%
  # mutate_at(vars(dv_flag:violent), funs(max(.))) %>%
  mutate(join_var = paste(join_var, collapse = " ")) %>%  
  filter(hierarchy == min(hierarchy)) %>%
         # SENT_LOC_DESCR = paste(unique(SENT_LOC_DESCR), collapse = ", "),
         # SENT_LENGTH = paste(unique(SENT_LENGTH), collapse = ", "),
         # SENT_TIME_DESCR = paste(unique(SENT_TIME_DESCR), collapse = ", ")) %>%
  # filter(hierarchy == min(hierarchy)) %>%
  ungroup() %>%
  distinct(CII_NUMBER, CYC_DATE, .keep_all = T) 
  # mutate(pretrial_end_date = if_else(is.na(DISP_DATE), SENTENCE_DATE, pretrial_end_date))

# coll_df <- coll_df %>%
#   mutate(max_conv_hier = if_else(max_conv_charge == "", 1e6, max_conv_hier)) %>%
#   mutate_at(vars(DISP_DESCR, desc), funs(gsub("^,", "", .)))

#save(coll_df, file = "Collapsed Pretrial DOJ Data 4.6.22.RData")

```

Checks
```{r eval=FALSE, include=FALSE}
sort(table(doj_df$DISP_DESCR), decreasing = T)

#42.3% Have a court action old
#~38.7% court action 4.6.22
doj_df %>%
  mutate(dispo = if_else(grepl("Court", STP_ORI_TYPE_DESCR), 1, 0)) %>%
  group_by(CII_NUMBER, CYC_DATE) %>%
  summarise(dispo = max(dispo)) %>%
  ungroup() %>%
  count(dispo)
    
grepl("DISCH|ACQUIT|DISMISSED", dispdescr)  

doj_df %>%
  filter(DISP_DESCR == "")

coll_df %>%
  group_by(dispoed) %>%
  count()

coll_df %>%
  filter(CYC_DATE <= as_date("2017-06-30")) %>%
         # charge_level %in% c("F", "M")) %>%
         
  count(filed, STP_ORI_CNTY_NAME) %>%
  spread(STP_ORI_CNTY_NAME)
  # group_by(charge_level) %>%
  mutate(n/sum(n))

  group_by(DISP_DESCR) %>%
  count() %>%
  arrange(desc(n)) %>%
  View()
  
df <- tibble(group = rep(c("A", "B"), each = 4), x = c(1,0,0,0,0,0,0,0))

df %>%
  group_by(group) %>%
  mutate(tot = if_else(sum(x) >= 1, 1, 0))

doj_df %>%
  filter(DISP_DESCR == "DISPO SEE MATCH ARR/DET/CITE NUMB(FDSMN)")
  count(DISP_DESCR) %>%
  arrange(desc(n))
  
coll_df %>%
  filter(!is.na(charge_level)) %>%
  count(charge_level)
  
coll_df %>%
  count(filed) %>%
  mutate(n/sum(n))

coll_df %>%
  count(filed_flag) %>%
  mutate(n/sum(n))

doj_df %>%
  distinct(STP_ORI_TYPE_DESCR) 

sort(table(doj_df$DISP_DESCR[doj_df$STP_ORI_TYPE_DESCR == "Arrest"]), decreasing = T)

doj_df[doj_df$STP_ORI_TYPE_DESCR == "Arrest",]

doj_df %>%
  group_by(CII_NUMBER, CYC_ORDER)


coll_df %>%
  count(RACE_CODE) %>%
  mutate(perc = n/sum(n)*100)

names(coll_df)
```
 

XXXXXXXX Priors--Fix Later, NOT USED CURRENTLY
```{r eval=FALSE, include=FALSE}
load("D:/DOJ Pretrial Pilot Data/Collapsed Pretrial DOJ Data.RData")

coll_df <- coll_df %>%
  group_by(CII_NUMBER) %>%
  mutate_at(vars(contains("conviction")), funs(prior = lag(cumsum(.), default = 0))) %>%
  ungroup() 
  # filter(STP_TYPE_DESCR == "ARREST/DETAINED/CITED",
  #        CYC_DATE >= as_date("2015-07-01")) 

# save(coll_df, file = "Collapsed 2015 DOJ Data.RData")

# load("Collapsed 2011 DOJ Data.RData")
# 
# rm(col_df)
save(coll_df, file = "Collapsed Pretrial DOJ Data.RData")
load("Collapsed Pretrial DOJ Data 4.6.22.RData")
```

Checks
```{r eval=FALSE, include=FALSE}
n_distinct(coll_df$CII_NUMBER, coll_df$CYC_ORDER)

summary(coll_df)

table(coll_df$STP_TYPE_DESCR)

coll_df

load("Court and County Joined Stats.RData")

mis_all_dispo <- coll_df %>%
  filter(felony_flag == 0) %>%
  filter(cyc_date <= as_date("2018-03-31")) %>%
  filter(stp_ori_cnty_name %in% c("FRESNO", "IMPERIAL", "ORANGE", "SOLANO")) %>%
  count(stp_ori_cnty_name, dispo, year = year(cyc_date)) %>%
  mutate(stp_ori_cnty_name = toTitleCase(tolower(stp_ori_cnty_name))) %>%
  group_by(stp_ori_cnty_name, year) %>%
  mutate(total = sum(n), n = round(n/total*100)) %>%
  filter(dispo == 1) %>%
  select(-dispo)

fel_all_dispo <-coll_df %>%
  filter(felony_flag == 1) %>%
  filter(cyc_date <= as_date("2018-03-31")) %>%
  filter(stp_ori_cnty_name %in% c("FRESNO", "IMPERIAL", "ORANGE", "SOLANO")) %>%
  count(stp_ori_cnty_name, dispo, year = year(cyc_date)) %>%
  mutate(stp_ori_cnty_name = toTitleCase(tolower(stp_ori_cnty_name))) %>%
  group_by(stp_ori_cnty_name, year) %>%
  mutate(total = sum(n), n = round(n/total*100)) %>%
  filter(dispo == 1) %>%
  select(-dispo)

mis_court_dispo <- coll_df %>%
  filter(felony_flag == 0) %>%
  filter(cyc_date <= as_date("2018-03-31")) %>%
  filter(stp_ori_cnty_name %in% c("FRESNO", "IMPERIAL", "ORANGE", "SOLANO")) %>%
  count(stp_ori_cnty_name, court_dispo, year = year(cyc_date)) %>%
  mutate(stp_ori_cnty_name = toTitleCase(tolower(stp_ori_cnty_name))) %>%
  group_by(stp_ori_cnty_name, year) %>%
  mutate(total = sum(n), n = round(n/total*100)) %>%
  filter(court_dispo == 1) %>%
  select(-court_dispo)

fel_court_dispo <-coll_df %>%
  filter(felony_flag == 1) %>%
  filter(cyc_date <= as_date("2018-03-31")) %>%
  filter(stp_ori_cnty_name %in% c("FRESNO", "IMPERIAL", "ORANGE", "SOLANO")) %>%
  count(stp_ori_cnty_name, court_dispo, year = year(cyc_date)) %>%
  mutate(stp_ori_cnty_name = toTitleCase(tolower(stp_ori_cnty_name))) %>%
  group_by(stp_ori_cnty_name, year) %>%
  mutate(total = sum(n), n = round(n/total*100)) %>%
  filter(court_dispo == 1) %>%
  select(-court_dispo)

dispo_list <- list(mis_all_dispo, fel_all_dispo, mis_court_dispo, fel_court_dispo)

save(dispo_list, file = "Percent of DOJ Data with Dispositions.RData")
```

Load and format Snowflake extract
```{r}
load("D:/DOJ Pretrial Pilot Data/Collapsed Pretrial DOJ Data 4.6.22.RData")
#load("Pre-DOJ Combined County Pretrial Data.RData")
# load("Unmatched Court Data.RData")
# G:\CrimJustice\PretrialAssessmentPilot\CIIs for DOJ\CIIs for DOJ 3 21 2022
files <- list.files("G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/CIIs for DOJ 3 21 2022/snowflake extract with joining fields", full.names = T)

#1st Partition
sf_df <- lapply(files[2:16], function(x){
  
  df <- fread(x, colClasses = "character")
  
  return(df)
})

#2nd partition
sf_dfhead <- fread(files[1], colClasses = "character")

sf_df <- sf_df %>% bind_rows()
names(sf_df) <- names(sf_dfhead)

sf_df <- sf_dfhead %>%
  bind_rows(sf_df)


sf_df <- sf_df %>%
  mutate(across(contains("DATE"), ~ymd(.x)))

#save(sf_df, file = "Snowflake extract for joining 4.6.22.RData")
```

Standardizing names in doj data
```{r}
names(coll_df) <- tolower(names(coll_df))

coll_df <- coll_df %>%
  rename(cii = cii_number)

#standardizing cii and then race variable names.
#names(coll_df)[1:3] <- c("cii", "sex", "race")

names(sf_df) <- tolower(names(sf_df))

names(sf_df)
```

Primary Joining
```{r}
# coll_df <- coll_df %>%
  # Flags are currently off
  # filter(filed_flag == 1)
  # select(-c(race, cyc_order, stp_order, stp_type_descr, stp_ori_type_descr, offense_code, charge_original), -(dv_flag:sf_violent), everything(),
  #        sentence_date) %>%
  # mutate(pretrial_dispo_date = if_else(is.na(disp_date), sentence_date, pretrial_dispo_date)) %>%
  # mutate(start = as.numeric(cyc_date),
  #        end = start) %>%
  # ungroup() %>%
  # filter(charge_level %in% c("F", "M")) %>%
  # mutate(row_doj = row_number())


dispo_df <- coll_df %>%
  mutate(start = as.numeric(cyc_date),
         end = start) %>%
  select(cii, arrest_date, start, end, sentence_date, disp_date, pretrial_end_date, disp_descr, filed_flag, convicted_flag, court_disp_flag, matches("court_.*_flag"), matches("conviction_.*_flag"))

 
# full_df <- df %>%
#   mutate(start = as.numeric(if_else(is.na(arrest_date), book_date - 2, arrest_date)),
#          end = as.numeric(if_else(is.na(arrest_date), book_date, arrest_date)),
#          row_m = row_number()) 


full_df <- sf_df %>%
  filter(!is.na(booking_date)) %>%
  mutate(start = as.numeric(booking_date -2),
         end = as.numeric(booking_date),
         row_m = row_number())

full_df %>%
  filter(is.na(start))

sf_df %>%
  #filter(is.na(booking_date)) %>%
  count(county)
```

Diagnostic
```{r}
dispo_df <- coll_df %>%
  mutate(start = as.numeric(CYC_DATE),
         end = start)

dispo_df %>%
  summarise(min_start = min(start), min_end = min(end), max_start = max(start), max_end = max(end))

dispo_df %>%
  summarise(min_cyc = min(CYC_DATE), max_cyc = max(CYC_DATE))
  

load("G:/CrimJustice/PretrialAssessmentPilot/temp files for transfer 3.30.22/processed/Snowflake extract for joining 4.6.22.RData")

sf_df %>%
  summarise(min(BOOKING_DATE, na.rm = T), max(BOOKING_DATE, na.rm = T), sum(is.na(BOOKING_DATE)))

sf_df %>%
  count(is.na(CII))

sf_cii <- sf_df %>%
  select(CII) %>%
  distinct()

coll_cii <- coll_df %>%
  select(CII_NUMBER) %>%
  distinct() %>%
  rename(CII = CII_NUMBER)

coll_cii %>%
  semi_join(sf_cii)
#584,959 matching CIIs

sf_df %>%
  filter(!is.na(BOOKING_DATE)) %>%
  filter(BOOKING_DATE >= "2016-11-30") %>%
  distinct(BOOKING_DATE) %>%
  mutate(bdateminus = BOOKING_DATE -2) %>%
  mutate(bdatenum = as.numeric(BOOKING_DATE)) %>%
  mutate(bdatenumminus = as.numeric(bdateminus)) %>%
  select(BOOKING_DATE, bdateminus, bdatenum, bdatenumminus) %>%
  arrange(BOOKING_DATE)

sf_df %>%
  filter(!is.na(BOOKING_DATE)) %>%
  mutate(start = as.numeric(BOOKING_DATE -2),
         end = as.numeric(BOOKING_DATE),
         row_m = row_number())

coll_df %>%
  filter(!is.na(CYC_DATE)) %>%
  filter(CYC_DATE >= "2016-11-30") %>%
  distinct(CYC_DATE) %>%
  mutate(bdateminus = CYC_DATE -2) %>%
  mutate(bdatenum = as.numeric(CYC_DATE)) %>%
  mutate(bdatenumminus = as.numeric(bdateminus)) %>%
  select(CYC_DATE, bdateminus, bdatenum, bdatenumminus) %>%
  arrange(CYC_DATE)

as.numeric(as.Date("2018-01-01"))
as.numeric(as.Date("2018-01-03"))


gen_anti <- genome_anti_join(full_df, dispo_df, by = c("cii", "start", "end"))

#save(gen_anti, file = "anti genome join 4.7.22.RData")

full_df
```


```{r}
full_df <- genome_left_join(full_df, dispo_df, by = c("cii", "start", "end"))

full_df <- full_df %>%
  rename_all(funs(gsub("\\.y$", "_doj", .))) %>%
  rename_all(funs(gsub("\\.x$", "", .))) %>%
  mutate(match_dif = abs(as.numeric(booking_date) - start_doj)) %>%
  group_by(county, row_m) %>%
  filter(match_dif == min(match_dif)|is.na(match_dif)) %>%
  ungroup() %>%
  distinct(row_m, .keep_all = T)
 

full_df <- full_df %>%
  rename(pretrial_period_end_date_doj = pretrial_end_date) 

#save(full_df, file = "SF DOJ Joined 4.6.22.RData")



load("G:/CrimJustice/PretrialAssessmentPilot/temp files for transfer 3.30.22/processed/SF DOJ Joined 4.6.22.RData")

full_df %>%
  count(match_dif)

full_df %>%
  mutate(pretrial_end_date_doj = if_else(is.na(pretrial_period_end_date), pretrial_period_end_date_doj, pretrial_period_end_date)) %>%
  mutate(start = as.numeric(as_date(release_date)) + 1,
         end = as.numeric(pretrial_period_end_date_doj)) %>%
  count(!is.na(pretrial_end_date_doj), !is.na(release_date), end > start)
```


```{r}
# load("Jail, RRF, Court, DOJ Joined.RData")

match_df_2022 <- full_df %>%
  mutate(pretrial_period_end_date_doj = if_else(is.na(pretrial_period_end_date), pretrial_period_end_date_doj, pretrial_period_end_date)) %>% #changed this, used to be assigned to pretrial_end_date, need to fix variable names going forward ****************************************************
  filter(!is.na(pretrial_period_end_date_doj)) %>%
  arrange(booking_date) %>%
  # group_by(row_j, county) %>%
  # mutate(pretrial_dispo_date = max(pretrial_dispo_date)) %>%
  ungroup() 
  # distinct(local_id, pretrial_dispo_date, .keep_all = T)
#

#save(match_df_2022, file = "Match df 4.12.22.RData")

# load("Court Collapsed Full Data.RData")
#load("Match df 4.12.22.RData")


# With county data unmatched with DOJ data for now.
match_df_2022 <- match_df_2022 %>%
  filter(!is.na(release_date),
         !is.na(pretrial_period_end_date_doj)) %>%
  filter(pretrial_period_end_date_doj - as_date(release_date) > 0) %>%
  mutate(start = as.numeric(as_date(release_date)) + 1,
         end = as.numeric(pretrial_period_end_date_doj)) %>%
  ungroup() %>%
  mutate(match_id = paste0(cii, county)) %>%
  filter(end > start) %>%
  mutate(row_m = row_number()) 





#With DOJ Data
recid_df <- coll_df %>%
  # filter(convicted_flag == 1) %>%
  mutate(row_doj = row_number()) %>%
  mutate(start = as.numeric(cyc_date),
         end = start) %>%
  # mutate(small_vio = if_else(max_charge %in% c("647F", "12500A", "146011A", "ARRM", "3056", "146012A", "166A4", "8537") |
  #        grepl("PROBATION VIOL|^POST RELEASE|^VIO CRT ORD|CONTEMPT|FTA|FAILURE TO APPEAR|PRCS|BENCH WARRANT|FAIL APPEAR", "PAROLE",
  #               "PROBATION|FAIL TO APPEA|DRIVE:SUSPENDED", desc), 1, 0),
  #        recid = if_else(small_vio == 0, 1, 0),
  #        violent_recid = if_else(grepl("INJ |BAT |BAT:|GBT|BATTERY|INJURY|ASSAULT|MURDER|ROBBERY|KIDNAPPING|BODILY INJURY|RAPE|SEX BATT|L&L W/CHILD|
  #                                      SEX WITH MINOR:3|SEXUAL ABUSE", desc), 1, 0)) %>%
  select(recid_date = cyc_date, cii, recid_join_var = join_var, recid_charge_description = doj_charge_description, arrested_flag, 
         recid_filed_flag = filed_flag, recid_convicted_flag = convicted_flag, matches("convict|^arrest.*flag|^court.*flag"), start, end, row_doj) 

names(recid_df) <- gsub("conviction", "recid_conviction", names(recid_df))
names(recid_df) <- gsub("arrest", "recid_arrest", names(recid_df))
names(recid_df) <- gsub("court", "recid_filed", names(recid_df))

#With In-county data
# recid_df <- full_df %>%
#   filter(book_date >= as_date("2015-07-01"),
#          book_type %in% c("Street", "Wart", "Owart")) %>%
#   mutate(match_id = paste0(local_id, county)) %>%
#   mutate(small_vio = if_else(max_charge %in% c("647F", "12500A", "146011A", "ARRM", "3056", "146012A", "166A4", "8537") |
#          grepl("PROBATION VIOL|^POST RELEASE|^VIO CRT ORD|CONTEMPT|FTA|FAILURE TO APPEAR|PRCS|BENCH WARRANT|FAIL APPEAR", "PAROLE",
#                 "PROBATION|FAIL TO APPEA|DRIVE:SUSPENDED", max_descrip), 1, 0),
#          recid = if_else(small_vio == 0, 1, 0),
#          violent_recid = if_else(grepl("INJ |BAT |BAT:|GBT|BATTERY|INJURY|ASSAULT|MURDER|ROBBERY|KIDNAPPING|BODILY INJURY|RAPE|SEX BATT|L&L W/CHILD|
#                                        SEX WITH MINOR:3|SEXUAL ABUSE", max_descrip), 1, 0)) %>%
#   select(match_id, book_type, book_date, max_descrip, hierarchy:tot_misd, small_vio:violent_recid) %>%
#   mutate(start = as.numeric(book_date),
#          end = start)


eval_df <- genome_left_join(match_df_2022, recid_df, by = c("cii", "start", "end"))

 
eval_df <- eval_df %>%
  mutate(recid_date = if_else(is.na(recid_date), as_date("2030-01-01"), recid_date)) %>%
  mutate_at(vars(contains("flag")), funs(if_else(is.na(.), 0, .))) %>%
  group_by(row_m) %>%
  mutate_at(vars(filed_flag:recid_conviction_dv_possible_flag, -row_m), max) %>%
  mutate(recid_date = min(recid_date)) %>%
  ungroup() %>%
  distinct(row_m, .keep_all = T) %>%
  mutate(recid_date = if_else(recid_date == as_date("2030-01-01"), as_date(NA), recid_date)) %>%
  select(-matches("^start"), -matches("^end")) %>%
  rename(cii = cii.x) %>%
  select(-cii.y)

#save(eval_df, file = "Eval df2 4.6.22.RData")
#save(eval_df, file = "Eval df 4.12.22.RData")

shell.exec(getwd())

eval_df %>%
  count(county)
```

Diagnostic
```{r}
full_df %>%
  count(!is.na(release_date), !is.na(pretrial_period_end_date), !is.na(pretrial_period_end_date_doj), release_date < pretrial_period_end_date, release_date < pretrial_period_end_date_doj)

load("G:/CrimJustice/PretrialAssessmentPilot/temp files for transfer 3.30.22/processed/Eval df 4.12.22.RData")

eval_df %>%
  summarise(min(booking_date), max(booking_date))

summary(eval_df$booking_date)
summary(eval_2021$book_date)

eval_df %>%
  filter(booking_date >= "2019-07-01") %>%
  #filter(county == "Sacramento") %>%
  group_by(year(booking_date), month(booking_date), county) %>%
  count()

eval_2021 %>%
  filter(book_date >= "2019-07-01") %>%
    filter(county == "Sacramento") %>%
  group_by(year(book_date), month(book_date), county) %>%
  count()

eval_df %>%
  filter(county == "Los Angeles") %>%
  count()

eval_2021 %>%
  filter(county == "Los Angeles") %>%
  count()

eval_df %>%
  filter(booking_date >= "2018-07-01") %>%
  filter(county == "Los Angeles") %>%
  mutate(book_my = floor_date(booking_date, unit = "month")) %>%
  group_by(book_my, county) %>%
  count() %>%
  ggplot() +
  aes(x = book_my, y = n, color = county) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


eval_2021 %>%
  filter(book_date >= "2018-07-01") %>%
  filter(county == "Los Angeles") %>%
  mutate(book_my = floor_date(book_date, unit = "month")) %>%
  group_by(book_my, county) %>%
  count() %>%
  ggplot() +
  aes(x = book_my, y = n, color = county) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


summary_2022 <- eval_df %>%
  filter(booking_date >= "2017-01-01") %>%
  filter(booking_date < "2021-01-01") %>%
  group_by(year = year(booking_date), county) %>%
  count() %>%
  rename(count_2022 = n)

summary_2021 <- eval_2021 %>%
  filter(book_date >= "2017-01-01") %>%
  filter(book_date < "2021-01-01") %>%
  group_by(year = year(book_date), county) %>%
  count()  %>%
  rename(count_2021 = n)

summary_both <- summary_2022 %>%
  full_join(summary_2021, by = c("year","county")) %>%
  mutate(dif_2022minus2021 = count_2022 - count_2021) %>%
  arrange(year)
```


```{r}
summary_both %>%
  #filter(year == 2019) %>%
  ungroup() %>%
  select(-month, -dif_2022minus2021) %>%
  group_by(year, county) %>%
  mutate(sum2022 = sum(count_2022), sum2021 = sum(count_2021)) %>%
  select(-count_2022, -count_2021) %>%
  distinct() 

annual_2022 <- eval_df %>%
  group_by(year = year(booking_date)) %>%
  count() %>%
  rename(count_2022 = n)

annual_2021 <- eval_2021 %>%
  group_by(year = year(book_date)) %>%
  count() %>%
  rename(count_2021 = n)

annual_2022 %>%
  full_join(annual_2021) %>%
  mutate(count_2021 = if_else(is.na(count_2021), 0, as.numeric(count_2021))) %>%
  mutate(dif = count_2022 - count_2021) %>%
  select(-count_2022, -count_2021) 


eval_df %>%
  filter(booking_date <= "2017-01-01")
  
```


Anonymized Data Set
```{r}

# names(eval_df)

anon_df <- eval_df %>%
  select(-c(book_num, court_case_id, court_docket_id, cdl_id, fbi, cii, contains("name"), dob, matches("id$"), zip_code))

write.csv(anon_df, file = "Anonymized Fabricated Data for Practice.csv")

# load("Final Failure Evaluation.RData")

#not sure what this piece of code is for, seems unnecessary and weird
eval_df_2022 <- eval_df %>%
  rename_all(funs(gsub("\\.y$", "_r", .))) %>%
  rename_all(funs(gsub("\\.x$", "", .))) %>%
  # select(-charge_level_r) %>%
  #Change Back tot_misd_r to actual match
  #mutate_at(vars(court_dispo:sf_violent_filing, -sentence_date), funs(if_else(is.na(.), 0, as.numeric(.)))) %>%
  mutate_at(vars(contains("_flag")), funs(if_else(is.na(.), 0, as.numeric(.)))) %>%
  # mutate_at(vars(dv_flag_r:tot_misd_r, small_vio:violent_recid), funs(if_else(is.na(.), 0, as.numeric(.)))) %>%
  group_by(row_m) %>%
  mutate_at(vars(court_dispo:sf_violent_filing, -sentence_date, -row_m), sum) %>%
  # mutate_at(vars(dv_flag_r:tot_misd_r, small_vio:violent_recid), sum) %>%
  # mutate_at(vars(contains("prior")), max) %>%
  filter(max_hier == min(max_hier)|is.na(max_hier)) %>%
  ungroup() %>%
  distinct(row_m, .keep_all = T) 

#save(eval_df, file = "Final Failure Evaluation 4.RData")
# 
# eval_df %>%
#   # filter(as_date(pretrial_dispo_date) - cyc_date == 0)
#   # mutate(dif = cyc_date - as_date(release_date)) %>%
#   mutate(dif = pretrial_dispo_date - cyc_date) %>%
#   ggplot() +
#   aes(x = dif) +
#   geom_density()
# 
# eval_df %>%
#   filter(!is.na(match_id.y))
# 
# match_df %>%
#   filter(match_id %in% unique(recid_df$match_id))
# 
# match_df %>%
#   add_count()

names(eval_df)
```

```{r}
eval_df <- eval_df %>%
  mutate(fta_warrant = if_else(fta_warrant == 0 & !is.na(fta_flag_r), fta_flag_r, as.numeric(fta_warrant))) %>%
  mutate(recid_combined = if_else(fta_warrant == 1, 1, recid)) 
# 
# eval_df <- eval_df %>%
#   filter(book_date >= as_date("2015-07-01"),
#          # book_type == "Street",
#          pretrial_dispo_date - as_date(release_date) > 0)

eval_df %>%
  count(county, recid, assessed_risk_level) %>%
  group_by(county, assessed_risk_level) %>%
  mutate(total = sum(n), n = n/total) %>%
  filter(recid == 1) %>%
  select(-total, -recid) %>%
  spread(assessed_risk_level, n) %>%
  select(county, low, med, high, unk, `<NA>`)

eval_df %>%
  count(county, fta_warrant, assessed_risk_level) %>%
  group_by(county, assessed_risk_level) %>%
  mutate(total = sum(n), n = n/total) %>%
  filter(fta_warrant == 1) %>%
  select(-total, -fta_warrant) %>%
  spread(assessed_risk_level, n) %>%
  select(county, low, med, high, unk, `<NA>`)

eval_df %>%
  count(county, recid_combined, assessed_risk_level) %>%
  group_by(county, assessed_risk_level) %>%
  mutate(total = sum(n), n = n/total) %>%
  filter(recid_combined == 1) %>%
  select(-total, -recid_combined) %>%
  spread(assessed_risk_level, n) %>%
  select(county, low, med, high, unk, `<NA>`)

roc_df <- eval_df %>%
  mutate(ra = case_when(assessed_risk_level == "low" ~ 0,
            assessed_risk_level == "med" ~ 1,
            assessed_risk_level == "high" ~ 2,
            T ~ NA_real_)) %>%
  filter(!is.na(ra))

summary(glm(fta_warrant ~ as.factor(ra) + county, data = roc_df))

sapply(unique(roc_df$county), function(i){
  roc_df <- roc_df %>%
    filter(county == i)
  roc(roc_df$recid_combined ~ roc_df$ra)
  })

  
eval_df %>%
  select(start, end, start_r, end_r)

check_df <- match_df %>%
  # mutate(dif = as.numeric(book_date) - start_doj) %>%
  mutate(dif = end - start) 
  count(dif)
  
summary(check_df$dif)

table(imp_df$book_type_original)
```

#Checks
```{r}
full_df %>%
  filter(as_date(book_date) >= as_date("2015-07-01")) %>%
  filter(is.na(pretrial_dispo_date), !is.na(pretrial_dispo_date_doj)) %>%
  count(county)
```

```{r}
load("All Data Combined.RData")

join %>%
  filter(!is.na(cii)) %>%
  distinct(cii, court_id, court_id_j, court_id_c)

table(join$book_type)

coll_df %>%
  group_by(cii, cyc_date) %>%
  add_count() %>%
  filter(n > 1)

cycle <- full_join %>%
  filter(as_date(book_date) + 60 >= stp_event_date) %>%
  group_by(cii.x, court_id) %>%
  mutate(recid_total = n() - 1) %>%
  ungroup() %>%
  mutate(recid = if_else(recid_total > 0, 1, 0)) %>%
  distinct(cii.x, court_id, .keep_all = T)

recid <- cycle %>%
  filter(!county_j %in% c("Shasta", "Yuba"),
         release_type %in% c("Bail", "OR")) %>%
  mutate(release_type = if_else(is.na(assessed_risk_level), "Not Assesed", "Assessed")) %>%
  group_by(county_j, recid, release_type) %>%
  count()

recid %>%
  rename(n = nnn) %>%
  ungroup() %>%
  group_by(county_j, release_type) %>%
  mutate(total = sum(n)) %>%
  ungroup() %>%
  dplyr::filter(recid == 1) %>%
  mutate(n = round(n/total*100)) %>%
  select(-recid, - total) %>%
  spread(release_type, n)

recid <- cycle %>%
  filter(!county_j %in% c("Shasta", "Yuba")) %>%
  # mutate(release_type = if_else(is.na(assessed_risk_level), release_type, "Assessed")) %>%
  group_by(county_j, recid, assessed_risk_level) %>%
  count()

recid %>%
  rename(n = nnn) %>%
  ungroup() %>%
  group_by(county_j, assessed_risk_level) %>%
  mutate(total = sum(n)) %>%
  ungroup() %>%
  dplyr::filter(recid == 1) %>%
  mutate(n = round(n/total*100)) %>%
  select(-recid, - total) %>%
  spread(assessed_risk_level, n)

table(cycle$assessed_risk_level, useNA = "ifany")

full_join %>%
  group_by(county_j, cii.x) %>%
  add_count() %>%
  filter(nnn > 5) %>%
  arrange(desc(n))

cycle %>%
  filter(is.na(court_id))

sample(full_join$court_id, 100)

cycle %>%
  filter(court_id == "11NF0034")

cycle <- cycle %>%
  mutate(dif = pretrial_dispo_date - as_date(book_date))

quantile(cycle$dif, c(.25, .75))

join %>%
  filter(book_type == "Street") 
  
cycle %>%
  group_by(county_j) %>%
  summarise(mean = mean(dif), med = median(dif))

table(coll_df$stp_ori_type_descr)

coll_df %>%
  filter(tot_felony == 0 & tot_misd == 0)

coll_df %>%
  filter(charge_level %in% c("F", "M"))

coll_df %>%
  filter(cyc_date >= as_date("2015-07-01")) %>%
  filter(!charge %in% c("647F", "12500A", "146011A", "ARRM", "3056", "146012A", "166A4", "8537"),
         !grepl("PROBATION VIOL|^POST RELEASE|^VIO CRT ORD|CONTEMPT|FTA|FAILURE TO APPEAR|PRCS|BENCH WARRANT|FAIL APPEAR", "PAROLE", "PROBATION|FAIL TO APPEA|DRIVE:SUSPENDED", desc))
  group_by(desc) %>%
  count() %>%
  arrange(desc(n))

coll_df <- coll_df %>%
  mutate(cii = parse_number(CII_NUMBER))
  
join %>%
  semi_join(coll_df, by = "cii")

coll_df$cii[1:100]
```

```{r}
cumsum(c(1,1,1))-1

names(coll_df) <- tolower(names(coll_df))

sample(coll_df$cii, 100)

coll_df %>%
  count(nchar(cii))

coll_df %>%
  filter(grepl("^10", cii))

sort(names(coll_df))
sort(names(join))

table(names(join))

full_join %>%
  mutate(arrest = 1,
         cii = if_else(is.na(cii.x), cii.y, cii.x)) %>%
  filter(!is.na(cii)) %>%
  group_by(cii) %>%
  arrange(stp_event_date) %>%
  mutate(prev_arrest = cumsum(arrest) -1,
         prev_violent = cumsum(violent_j) -1,
         pretrial_recid = if_else())
  distinct(cii.x, book_date)
  group_by()
  distinct(stp_event_date, cii.x)
  
df <- tibble(x = rep(c("group1", "group2"), each = 3), book_date = as_date(c("2015-01-01", "2015-01-15", "2015-03-01", "2015-04-01", "2015-05-01", "2015-06-01")), dispo_date = as_date(c("2015-02-01", "2015-03-01", "2015-04-01", "2015-05-01", "2015-06-01", "2015-07-01")))

df %>%
  group_by(x, dispo_date) %>%
  mutate(recide = sum(book_date < dispo_date))
```

#Post 2011
```{r}
load("Post 2011 CORI CII Matched Dataset.RData")

doj_df11 <- doj_df11 %>%
  mutate(unique_id = paste0(REQ_CII_NUMBER, CYC_DATE))

samp <- sample(doj_df11$unique_id, 1e5, replace = F)

sample_df <- doj_df11 %>%
  filter(unique_id %in% samp)

load("Sample Post 2011 100K CORI CII Matched Dataset.RData")

sample_df2 <- sample_df %>%
  group_by(REQ_CII_NUMBER, CYC_DATE) %>%
  mutate(DISP_DATE = max(DISP_DATE)) %>%
  distinct(REQ_CII_NUMBER, CYC_DATE, .keep_all = T)

sample_df2 %>%
  filter(DISP_DATE == "")


max("", "20071022")

sample_df$DISP_OFFENSE_CODE[1]

# sample_df <- sample_df %>%
#   ungroup() %>%
#   select(5:7, 21:24,26,28,32,34:38,48,50,52:59) %>%
sample_df %>%
  mutate(STP_EVENT_DATE = if_else(STP_EVENT_DATE == "" & grepl("COURT", STP_TYPE_DESCR), DISP_DATE, STP_EVENT_DATE)) %>%
  separate(OFFENSE_DESCR, c("charge","desc"), sep = "-") %>%
  separate(charge, c("charge", "code_type"), sep = " " )
  


sample_df %>%
  filter(CII_NUMBER %in% CII_NUMBER[STP_EVENT_DATE != "" & DISP_DATE != "" & STP_EVENT_DATE != DISP_DATE]) %>%
  View()

table(sample_df$STP_TYPE_DESCR)

?separate

join %>%
  ungroup() %>%
  filter(book_type == "Street") %>%
  group_by(cii, court_id, county_j) %>%
  mutate(recid = n_distinct(book_num) - 1,
         recid = if_else(recid > 0,1,0)) %>%
  group_by(county_j, recid) %>%
  count()

join$county  
```

Group for Matching with Jail Data
```{r}
load("Post 2011 CORI CII Matched Dataset.RData")

doj_sum <- doj_df11 %>%
  # select(REQ_CII_NUMBER, CYC_DATE, DISP_DATE) %>%
  group_by(REQ_CII_NUMBER, CYC_DATE) %>%
  mutate(DISP_DATE = max(DISP_DATE)) %>%
  distinct(REQ_CII_NUMBER, CYC_DATE, .keep_all = T)

# save(doj_sum, file = "Three Variable DOJ Summary.RData")

# rm(doj_df11)

load("E:/Confidential Data/Jail Data/Unfinished Booking Level Collapse of Jail Data.RData")

book_df <- full_df2 %>%
  ungroup() %>%
  select(cii, book_date, court_id)

book_df %>%
  group_by(cii) %>%
  mutate(start = book_date,
         end = lead(book_date))

lead(c(0,1), default = 2)

n_distinct(doj_sum$REQ_CII_NUMBER)


#98% of CIIs matched 
sum(unique(full_df2$cii) %in% unique(doj_sum$REQ_CII_NUMBER))/n_distinct(full_df2$cii)

c(1,2) %in% 1

doj_df11
```

```{r}
doj_sum %>%
  mutate(DISP_DATE_y = if_else(DISP_DATE == "", "No", "Yes")) %>%
  group_by(DISP_DATE_y, STP_ORI_CNTY_NAME, OFFENSE_TOC) %>%
  count()
```


#Sample examination
```{r}
sample_df %>%
  group
```

#Tests
```{r eval=FALSE, include=FALSE}
read.csv(files, colClasses = "character", header = F)

example <- read_lines("RR_19-004_JCC_Tafoya/20190314_RRC100_OUTPUT_RR_19-004_JCC_TAFOYA_01_00001.dat.gz")
example2 <- read_lines("RR_19-004_JCC_Tafoya/20190314_RRC100_OUTPUT_RR_19-004_JCC_TAFOYA_01_00002.dat.gz")

length(example[2] )

str_count(example2[6], pattern = ",")

example2[1]

gzfile("RR_19-004_JCC_Tafoya/20190314_RRC100_OUTPUT_RR_19-004_JCC_TAFOYA_01_00001.dat.gz")

read.table("RR_19-004_JCC_Tafoya/20190314_RRC100_OUTPUT_RR_19-004_JCC_TAFOYA_01_00002.dat.gz", sep = ",", header = F) %>%
  View()

read.pattern("RR_19-004_JCC_Tafoya/20190314_RRC100_OUTPUT_RR_19-004_JCC_TAFOYA_01_00002.dat.gz", pattern = ",", header = F)

read.csv("RR_19-004_JCC_Tafoya/20190314_RRC100_OUTPUT_RR_19-004_JCC_TAFOYA_01_00001.dat.gz", colClasses = "character")

files[-1]
```


#Post 2012 Included Variables Output for Joining
```{r eval=FALSE, include=FALSE}
doj_df <- fread("CORI CII Pretrial Dataset Post 2012.csv", colClasses = "character")

doj_dates <- doj_df %>%
  select(STP_ORI_CNTY_NAME, REQ_CII_NUMBER, CYC_ORDER, STP_EVENT_DATE, STP_TYPE_DESCR, DISP_DATE) %>%
  group_by(REQ_CII_NUMBER, CYC_ORDER) %>%
  mutate(DISP_DATE = max(DISP_DATE)) %>%
  filter(STP_TYPE_DESCR %in% c("ARREST/DETAINED/CITED", "COURT ACTION")) %>%
  distinct()
  
doj_dates <- doj_dates %>%
  group_by(REQ_CII_NUMBER, CYC_ORDER, STP_TYPE_DESCR) %>%
  filter(STP_EVENT_DATE == min(STP_EVENT_DATE)) %>%
  ungroup()

doj_dates <- doj_dates %>%
  spread(STP_TYPE_DESCR, STP_EVENT_DATE) 

names(doj_dates2) <- c("county", "cii", "cycle", "disposition_date", "arrest_date", "filing_date")

doj_dates2 <- doj_dates2 %>%
  mutate_at(vars(contains("date")), ymd)

samp <- doj_dates2 %>%
  sample_n(1000) 
  
doj_dates_list <- split.data.frame(doj_dates2, doj_dates2$county)

lapply(doj_dates_list, function(i){
  fwrite(i, file = paste("D:/DOJ Pretrial Pilot Data/County Join Dates/",i$county[1],"Join Dates.csv"))
})

names(doj_df)[order(names(doj_df))]

doj_df[1:1000,] %>%
  View()
  count(STP_ORI_TYPE_DESCR, STP_TYPE_DESCR) %>%
  arrange(desc(n)) %>%
  View()
  
doj_df %>%
  sample_n(1e6) %>%
  count(SENT_LOC_DESCR)
```
