---
title: "FTA with recalled combined counties"
output: html_document
date: "2023-12-19"
---


# Settup and Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
knitr::opts_knit$set(root.dir = "C:/PretrialPilot/Pretrial-Pilot-County-Analysis")

# library(rlang)
library(tidyverse)
library(data.table)
library(openxlsx)
#library(readxl)
library(lubridate)
library(gsubfn)
library(fuzzyjoin)
library(dplyr)
# library(multidplyr)
library(pROC)
library(broom)
library(kableExtra)
library(stargazer)
library(DBI)
library(dbplyr)
library(odbc)
library(tinytex)
library(gt)
library(askpass)

# shell.exec(getwd())
```

Connection
```{r include=FALSE}
con <- dbConnect(odbc::odbc(), "snowflake_pretrial", uid ="Sal.Lempert@jud.ca.gov", pwd = rstudioapi::askForPassword("Password"))
```
# Pull agg_enh
Pull live snowflake data -- agg_enh
```{sql echo=TRUE, connection=con, output.var='agg_enh'}
SELECT *
FROM "DWH_PROD"."REPORTING"."AGG_PRETRIAL_KPI_DOJ_ENHANCED";
```

# Pull data for counties combined
Pull live snowflake data -- agg
```{sql echo=TRUE, connection=con, output.var='agg'}
SELECT *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "05_CALAVERAS-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "016_KINGS-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "19_LOSANGELES-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "25_MODOC-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "28_NAPA-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "29_NEVADA-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "34_SACRAMENTO-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "39_SANJOAQUIN-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "41_SANMATEO-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "42_SANTABARBARA-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "46_SIERRA-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "49_SONOMA-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "54_TULARE-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "55_TUOLUMNE-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "56_VENTURA-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"

UNION ALL

SELECT  *
from "58_YUBA-DWH_PROD"."SECURE_SHARE"."AGG_PRETRIAL_KPI"
;
```



Pull live snowflake data -- fcc
```{sql echo=TRUE, connection=con, output.var='fcc'}
SELECT 'Alameda' as county, *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Calaveras' as county, *
from "05_CALAVERAS-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Kings' as county, *
from "16_KINGS-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Los Angeles' as county, *
from "19_LOSANGELES-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Modoc' as county, *
from "25_MODOC-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Napa' as county, *
from "28_NAPA-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Nevada' as county, *
from "29_NEVADA-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Sacramento' as county, *
from "34_SACRAMENTO-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'San Joaquin' as county, *
from "39_SANJOAQUIN-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'San Mateo' as county, *
from "41_SANMATEO-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Santa Barbara' as county, *
from "42_SANTABARBARA-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Sierra' as county, *
from "46_SIERRA-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Sonoma' as county, *
from "49_SONOMA-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Tulare' as county, *
from "54_TULARE-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Tuolumne' as county, *
from "55_TUOLUMNE-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Ventura' as county, *
from "56_VENTURA-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"

UNION ALL

SELECT  'Yuba' as county, *
from "58_YUBA-DWH_PROD"."SECURE_SHARE"."FACT_COURT_CASE"
;
```

Pull live snowflake data -- fw
```{sql echo=TRUE, connection=con, output.var='fw'}
SELECT 'Alameda' as county, *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Calaveras' as county, *
from "05_CALAVERAS-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Kings' as county, *
from "16_KINGS-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Los Angeles' as county, *
from "19_LOSANGELES-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Modoc' as county, *
from "25_MODOC-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Napa' as county, *
from "28_NAPA-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Nevada' as county, *
from "29_NEVADA-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Sacramento' as county, *
from "34_SACRAMENTO-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'San Joaquin' as county, *
from "39_SANJOAQUIN-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'San Mateo' as county, *
from "41_SANMATEO-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Santa Barbara' as county, *
from "42_SANTABARBARA-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Sierra' as county, *
from "46_SIERRA-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Sonoma' as county, *
from "49_SONOMA-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Tulare' as county, *
from "54_TULARE-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Tuolumne' as county, *
from "55_TUOLUMNE-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Ventura' as county, *
from "56_VENTURA-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"

UNION ALL

SELECT  'Yuba' as county, *
from "58_YUBA-DWH_PROD"."SECURE_SHARE"."FACT_WARRANT"
;
```

Pull live snowflake data -- dw
```{sql echo=TRUE, connection=con, output.var='dw'}
SELECT 'Alameda' as county, *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Calaveras' as county, *
from "05_CALAVERAS-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Kings' as county, *
from "16_KINGS-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Los Angeles' as county, *
from "19_LOSANGELES-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Modoc' as county, *
from "25_MODOC-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Napa' as county, *
from "28_NAPA-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Nevada' as county, *
from "29_NEVADA-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Sacramento' as county, *
from "34_SACRAMENTO-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'San Joaquin' as county, *
from "39_SANJOAQUIN-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'San Mateo' as county, *
from "41_SANMATEO-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Santa Barbara' as county, *
from "42_SANTABARBARA-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Sierra' as county, *
from "46_SIERRA-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Sonoma' as county, *
from "49_SONOMA-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Tulare' as county, *
from "54_TULARE-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Tuolumne' as county, *
from "55_TUOLUMNE-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Ventura' as county, *
from "56_VENTURA-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"

UNION ALL

SELECT  'Yuba' as county, *
from "58_YUBA-DWH_PROD"."SECURE_SHARE"."DIM_WARRANT"
;
```

Pull live snowflake data -- link
```{sql echo=TRUE, connection=con, output.var='link'}
SELECT 'Alameda' as county, *
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Calaveras' as county, *
from "05_CALAVERAS-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Kings' as county, *
from "16_KINGS-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Los Angeles' as county, *
from "19_LOSANGELES-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Modoc' as county, *
from "25_MODOC-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Napa' as county, *
from "28_NAPA-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Nevada' as county, *
from "29_NEVADA-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Sacramento' as county, *
from "34_SACRAMENTO-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'San Joaquin' as county, *
from "39_SANJOAQUIN-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'San Mateo' as county, *
from "41_SANMATEO-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Santa Barbara' as county, *
from "42_SANTABARBARA-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Sierra' as county, *
from "46_SIERRA-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Sonoma' as county, *
from "49_SONOMA-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Tulare' as county, *
from "54_TULARE-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Tuolumne' as county, *
from "55_TUOLUMNE-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Ventura' as county, *
from "56_VENTURA-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"

UNION ALL

SELECT  'Yuba' as county, *
from "58_YUBA-DWH_PROD"."SECURE_SHARE"."DS_PRETRIAL_BOOKING_CASE_LINK"
;
```

```{r}
dw
```

# Calculate FTA rate including recalled warrants 
```{r}
wars <- fw %>%
  left_join(dw)

fta_wars <- wars %>%
  mutate(war_issue_date = ymd(DIM_WARRANT_ISSUANCE_DATE_KEY)) %>%
  select(war_issue_date, CASE_KEY, WARRANT_TYPE, WARRANT_STATUS, WARRANT_REASON) %>%
  filter(!is.na(war_issue_date)) %>%
  filter(WARRANT_TYPE == "Bench",
         WARRANT_REASON == "FTA",
         WARRANT_STATUS %in% c("Issued", "Served", "Ordered", "Recalled")) %>%
  distinct()

fta_wars <- fta_wars %>%
  left_join(link %>%
            select(COUNTY, BOOKING_KEY, CASE_KEY) %>%
              distinct()) %>%
  select(COUNTY, war_issue_date, BOOKING_KEY) %>%
  distinct() %>%
  filter(!is.na(BOOKING_KEY))

agg_rec<- agg_enh %>%
  mutate(row = row_number()) %>%
  left_join(fta_wars) %>%
  mutate(fta_test_flag = case_when(is.na(war_issue_date) ~ 0,
                                    war_issue_date >= RELEASE_DATE & war_issue_date <= PRETRIAL_PERIOD_END_DATE ~ 1,
                                   T ~ 0)) %>%
  group_by(COUNTY, BOOKING_KEY) %>%
  arrange(desc(fta_test_flag), war_issue_date) %>%
  mutate(fta_test_flag = max(fta_test_flag)) %>%
  ungroup() %>%
  distinct(row, .keep_all = T) 


```

Join to FTAs from DOJ flag
```{r}
# test <- agg_enh %>%
#   left_join(agg_rec %>% select(COUNTY, BOOKING_KEY, fta_test_flag, RISK_SCORE) %>% distinct())

```

# Look at new FTA rate

Count of new flag, old flag, doj flag
```{r}
agg_rec %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes") %>%
  #filter(!is.na(RISK_SCORE)) %>%
  count(COUNTY, fta_test_flag, FAILURE_TO_APPEAR_COUNT, RECID_ARREST_FTA_FLAG_DOJ) %>%
  group_by(COUNTY) %>%
  mutate(tot = sum(n), perc = round(100*n/sum(n),1))

```

Overall new fta rate
```{r}
fta_rec <- agg_rec %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes" | !is.na(PRETRIAL_PERIOD_END_DATE_DOJ)) %>%
  #filter(!is.na(RISK_SCORE)) %>%
  mutate(fta_all = case_when(fta_test_flag == 1 ~ 1,
                             RECID_ARREST_FTA_FLAG_DOJ == 1 ~ 1,
                             FAILURE_TO_APPEAR_COUNT == 1 ~ 1,
                             T ~ 0)) %>%
  count(COUNTY, fta_all) %>%
  group_by(COUNTY) %>%
  mutate(tot = sum(n), perc = round(100*n/sum(n),1)) %>%
  ungroup()



```

Old FTA rate
```{r}
fta_old <- agg_rec %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes" | !is.na(PRETRIAL_PERIOD_END_DATE_DOJ)) %>%
  #filter(!is.na(RISK_SCORE)) %>%
  mutate(fta_all = case_when(FAILURE_TO_APPEAR_COUNT == 1 ~ 1,
                             RECID_ARREST_FTA_FLAG_DOJ == 1 ~ 1,
                             T ~ 0)) %>%
  count(COUNTY, fta_all) %>%
  group_by(COUNTY) %>%
  mutate(tot = sum(n), perc_old = round(100*n/sum(n),1)) %>%
  ungroup()
```

Side by side comparison
```{r}
fta_compare <- fta_rec %>%
  select(-n) %>%
  left_join(fta_old %>% select(COUNTY, fta_all, perc_old))

fta_dif <- fta_compare %>%
  group_by(COUNTY) %>%
  filter(fta_all == max(fta_all)) %>%
  mutate(perc = if_else(perc == 100 & fta_all == 0, 0, perc),
         perc_old = if_else(perc_old == 100 & fta_all == 0, 0, perc_old)) %>%
  select(-fta_all) %>%
  mutate(dif = perc - perc_old)
  
fta_dif
```
Separate warrant FTAs from hearing FTAs
```{r}
fta_hearing <- agg_rec %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes" | !is.na(PRETRIAL_PERIOD_END_DATE_DOJ)) %>%
  count(COUNTY, fta_test_flag, FAILURE_TO_APPEAR_COUNT) %>%
  group_by(COUNTY) %>%
  mutate(tot = sum(n), perc = round(100*n/sum(n),1)) %>%
  ungroup() %>%
  filter(fta_test_flag == 0 & FAILURE_TO_APPEAR_COUNT == 1)

fta_hearing <- fta_hearing %>%
  arrange(COUNTY) %>%
  select(COUNTY, perc_hearing = perc)

fta_county_old <- agg_rec %>%
  filter(BOOKING_DATE > '2018-07-01',
         BOOKING_DATE < '2023-01-01') %>%
  filter(IS_BOOKING_ASSESSED == "Yes") %>%
  filter(IS_RELEASE_ELIGIBLE == "Yes") %>%
  filter(IS_RELEASED_PRETRIAL == "Yes") %>%
  filter(!is.na(CII)) %>%
  filter(HAS_PRETRIAL_PERIOD_END == "Yes" | !is.na(PRETRIAL_PERIOD_END_DATE_DOJ)) %>%
  #filter(!is.na(RISK_SCORE)) %>%
  mutate(fta_county = case_when(FAILURE_TO_APPEAR_COUNT == 1 ~ 1,
                             T ~ 0)) %>%
  count(COUNTY, fta_county) %>%
  group_by(COUNTY) %>%
  mutate(tot = sum(n), perc_county_old = round(100*n/sum(n),1)) %>%
  ungroup()


fta_county_old <- fta_county_old %>%
  group_by(COUNTY) %>%
  filter(fta_county == max(fta_county)) %>%
  mutate(perc_county_old = if_else(perc_county_old == 100 & fta_county == 0, 0, perc_county_old)) %>%
  select(-fta_county) %>%
  select(-n)


fta_hearing_warrant <- fta_county_old %>%
  left_join(fta_hearing) %>%
  mutate(perc_hearing = if_else(is.na(perc_hearing), 0, perc_hearing)) %>%
  mutate(perc_warrant_old = perc_county_old - perc_hearing) %>%
  mutate(source = case_when(perc_warrant_old != 0 & perc_hearing !=0 ~ "Both hearings and warrants",
                            perc_warrant_old !=0 ~ "Warrants only",
                            perc_hearing !=0 ~ "Hearings only",
                            T ~ "Neither"))

fta_hearing_warrant %>%
  left_join(fta_dif) %>%
  rename(fta_tot_with_recalls = perc) %>%
  rename(perc_old_total = perc_old) %>%
  rename(perc_recalled_warrants = dif) %>%
  mutate(perc_doj = perc_old_total - perc_county_old) %>%
  select(-fta_tot_with_recalls) %>%
  select(-perc_old_total)
```


