---
output:
  pdf_document: default
  html_document: default
---
# Settup and Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
knitr::opts_knit$set(root.dir = "G:/CrimJustice/PretrialAssessmentPilot")

# library(rlang)
library(tidyverse)
library(data.table)
library(openxlsx)
library(readxl)
library(lubridate)
library(XML)
library(xml2)
# library(xmltools)o
library(gsubfn)
library(fuzzyjoin)
library(dplyr)
library(openxlsx)
library(fuzzyjoin)
# library(multidplyr)
library(pROC)
library(broom)
library(kableExtra)
library(stargazer)

# shell.exec(getwd())
```


```{r warning=FALSE, include=FALSE}
load("G:/CrimJustice/PretrialAssessmentPilot/Tool Validation Final Data Frame.RData")

eval_df <- eval_df %>%
  filter(tool_name %in% c("oras", "psa", "vprai", "vprair"))


eval_df %>%
  group_by(tool_name) %>%
  summarise(earliest_assessment = min(assessment_date), latest_assessment = max(assessment_date))
```

\newpage

Race df
```{r include=FALSE}
race_df <- eval_df %>%
  mutate(race = factor(race, levels = c("White", "Black", "Hispanic", "Other_Unknown"))) %>%
  filter(race != "Other_Unknown")
```

Gender df
```{r include=FALSE}
sex_df <- eval_df %>%
  mutate(sex = factor(sex, levels = c("Male", "Female"))) %>%
  filter(sex != "Other_Unknown")
```


# PSA race

PSA
\newline
```{r fig.height=6, fig.width=10, dpi=1200}
risk_df <- eval_df %>%
  filter(tool_name == "psa") %>%
  group_by(psa_fta_risk_score, race, county) %>%
  select(fta_flag) %>%
  pivot_longer(fta_flag) 

names(risk_df)[1] <- "psa_risk_score"

risk_df2 <- eval_df %>%
  filter(tool_name == "psa") %>%
  group_by(psa_nca_risk_score, race, county) %>%
  select(recid_arrested_flag, recid_filed_flag, recid_convicted_flag) %>%
  pivot_longer(recid_arrested_flag:recid_convicted_flag) 

names(risk_df2)[1] <- "psa_risk_score"

risk_df3 <- eval_df %>%
  filter(tool_name == "psa", !is.na(psa_nvca_risk_score)) %>%
  group_by(psa_nvca_risk_score, race, county) %>%
  select(recid_arrest_violent_psa_flag) %>%
  pivot_longer(recid_arrest_violent_psa_flag) 

names(risk_df3)[1] <- "psa_risk_score"

risk_df <- bind_rows(risk_df, risk_df2, risk_df3)
  
rm(risk_df2, risk_df3)

risk_df <- risk_df %>%
  mutate(race = factor(race, levels = c("White", "Black", "Hispanic", "Other_Unknown"))) %>%
  filter(race %in% c("White", "Black", "Hispanic")) %>%
  mutate(name = case_when(name == "fta_flag" ~ "FTA",
                          name == "recid_arrested_flag" ~ "New Arrest",
                          name == "recid_filed_flag" ~ "New Filing",
                          name == "recid_convicted_flag" ~ "New Conviction",
                          name == "recid_arrest_violent_psa_flag" ~ "New Violent Arrest"),
         name = factor(name, levels = c("FTA", "New Arrest", "New Filing", "New Conviction", "New Violent Arrest"))) %>%
  filter(county %in% c("Los Angeles", "Sacramento"))

ggplot(risk_df) +
  aes(x = psa_risk_score, y = value, color = race) +
  geom_smooth(method = "glm", method.args = list(family=binomial), alpha = .2) +
  # geom_line() +
  # geom_point() +
  theme_bw() +
  # ylim(0,100) +
  facet_wrap(~name, scales = "free") +
  # facet_grid(county~name, scales = "free") +
  labs(x = "Risk Category", y = "Percent", title = "Comparison of Racial Differences in Logistic Regression Curves--PSA") +
  scale_x_continuous(breaks = 1:6)

# eval_df %>%
#   filter(tool_name == "psa") %>%
#   count(county)
```
\newpage


PSA--With Interactions at lowest score
\newline
```{r, results='asis'}
m1 <- glm(family = binomial(),fta_flag ~ psa_fta_risk_score * race + release_to_pretrial_end , data = race_df %>% mutate(across(contains("score"), ~.x-1)))
m2 <- glm(family = binomial(),recid_arrested_flag ~ psa_nca_risk_score * race + release_to_pretrial_end , data = race_df %>% mutate(across(contains("score"), ~.x-1)))
m3 <- glm(family = binomial(),recid_filed_flag ~ psa_nca_risk_score * race + release_to_pretrial_end , data = race_df %>% mutate(across(contains("score"), ~.x-1)))
m4 <- glm(family = binomial(),recid_convicted_flag ~ psa_nca_risk_score * race + release_to_pretrial_end , data = race_df %>% mutate(across(contains("score"), ~.x-1)))
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ psa_nvca_risk_score * race + release_to_pretrial_end , data = race_df)

stargazer(list(m1,m2,m3,m4,m5),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest"), 
          covariate.labels = c("PSA FTA Risk Score", "PSA NCA Risk Score", "PSA NVCA Risk Score", 
                               "Race:Black", "Race:Hispanic", "Days Released", "FTA*Black", "FTA*Hispanic",
                               "NCA*Black", "NCA*Hispanic", "NVCA*Black", "NVCA*Hispanic"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")
```
\newpage

PSA--With Interactions at risk score 6
\newline
```{r, results='asis'}
m1 <- glm(family = binomial(),fta_flag ~ psa_fta_risk_score * race + release_to_pretrial_end , data = race_df %>% mutate(across(contains("score"), ~.x-6)))
m2 <- glm(family = binomial(),recid_arrested_flag ~ psa_nca_risk_score * race + release_to_pretrial_end , data = race_df %>% mutate(across(contains("score"), ~.x-6)))
m3 <- glm(family = binomial(),recid_filed_flag ~ psa_nca_risk_score * race + release_to_pretrial_end , data = race_df %>% mutate(across(contains("score"), ~.x-6)))
m4 <- glm(family = binomial(),recid_convicted_flag ~ psa_nca_risk_score * race + release_to_pretrial_end , data = race_df %>% mutate(across(contains("score"), ~.x-6)))
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ psa_nvca_risk_score * race + release_to_pretrial_end , data = race_df%>% mutate(across(contains("score"), ~.x-1)))

stargazer(list(m1,m2,m3,m4,m5),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest"), 
          covariate.labels = c("PSA FTA Risk Score", "PSA NCA Risk Score", "PSA NVCA Risk Score", 
                               "Race:Black", "Race:Hispanic", "Days Released", "FTA*Black", "FTA*Hispanic",
                               "NCA*Black", "NCA*Hispanic", "NVCA*Black", "NVCA*Hispanic"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")

```
\newpage

# PSA gender
PSA
\newline
```{r fig.height=6, fig.width=10, dpi=1200}
risk_df <- eval_df %>%
  filter(tool_name == "psa") %>%
  group_by(psa_fta_risk_score, sex, county) %>%
  select(fta_flag) %>%
  pivot_longer(fta_flag) 

names(risk_df)[1] <- "psa_risk_score"

risk_df2 <- eval_df %>%
  filter(tool_name == "psa") %>%
  group_by(psa_nca_risk_score, sex, county) %>%
  select(recid_arrested_flag, recid_filed_flag, recid_convicted_flag) %>%
  pivot_longer(recid_arrested_flag:recid_convicted_flag) 

names(risk_df2)[1] <- "psa_risk_score"

risk_df3 <- eval_df %>%
  filter(tool_name == "psa", !is.na(psa_nvca_risk_score)) %>%
  group_by(psa_nvca_risk_score, sex, county) %>%
  select(recid_arrest_violent_psa_flag) %>%
  pivot_longer(recid_arrest_violent_psa_flag) 

names(risk_df3)[1] <- "psa_risk_score"

risk_df <- bind_rows(risk_df, risk_df2, risk_df3)
  
rm(risk_df2, risk_df3)

risk_df <- risk_df %>%
  mutate(sex = factor(sex, levels = c("Male", "Female"))) %>%
  filter(sex %in% c("Male", "Female")) %>%
  mutate(name = case_when(name == "fta_flag" ~ "FTA",
                          name == "recid_arrested_flag" ~ "New Arrest",
                          name == "recid_filed_flag" ~ "New Filing",
                          name == "recid_convicted_flag" ~ "New Conviction",
                          name == "recid_arrest_violent_psa_flag" ~ "New Violent Arrest"),
         name = factor(name, levels = c("FTA", "New Arrest", "New Filing", "New Conviction", "New Violent Arrest"))) %>%
  filter(county %in% c("Los Angeles", "Sacramento"))

ggplot(risk_df) +
  aes(x = psa_risk_score, y = value, color = sex) +
  geom_smooth(method = "glm", method.args = list(family=binomial), alpha = .2) +
  # geom_line() +
  # geom_point() +
  theme_bw() +
  # ylim(0,100) +
  # facet_grid(county~name, scales = "free") +
  facet_wrap(~name, scales = "free") +
  labs(x = "Risk Category", y = "Percent", title = "Comparison of Gender Differences in Logistic Regression Curves--PSA") +
  scale_x_continuous(breaks = 1:6)

# eval_df %>%
#   filter(tool_name == "psa") %>%
#   count(county)
```
\newpage

PSA--With Interactions at lowest score
\newline
```{r, results='asis'}
m1 <- glm(family = binomial(),fta_flag ~ psa_fta_risk_score * sex + release_to_pretrial_end , data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m2 <- glm(family = binomial(),recid_arrested_flag ~ psa_nca_risk_score * sex + release_to_pretrial_end , data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m3 <- glm(family = binomial(),recid_filed_flag ~ psa_nca_risk_score * sex + release_to_pretrial_end , data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m4 <- glm(family = binomial(),recid_convicted_flag ~ psa_nca_risk_score * sex + release_to_pretrial_end , data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ psa_nvca_risk_score * sex + release_to_pretrial_end , data = sex_df)

stargazer(list(m1,m2,m3,m4,m5),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest"), 
          covariate.labels = c("PSA FTA Risk Score", "PSA NCA Risk Score", "PSA NVCA Risk Score", 
                               "Female", "Days Released", "FTA*Female",
                               "NCA*Female", "NVCA*Female"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")
```
\newpage

PSA--With Interactions at highest score
\newline
```{r, results='asis'}
m1 <- glm(family = binomial(),fta_flag ~ psa_fta_risk_score * sex + release_to_pretrial_end , data = sex_df %>% mutate(across(contains("score"), ~.x-6)))
m2 <- glm(family = binomial(),recid_arrested_flag ~ psa_nca_risk_score * sex + release_to_pretrial_end , data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m3 <- glm(family = binomial(),recid_filed_flag ~ psa_nca_risk_score * sex + release_to_pretrial_end , data = sex_df %>% mutate(across(contains("score"), ~.x-6)))
m4 <- glm(family = binomial(),recid_convicted_flag ~ psa_nca_risk_score * sex + release_to_pretrial_end , data = sex_df %>% mutate(across(contains("score"), ~.x-6)))
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ psa_nvca_risk_score * sex + release_to_pretrial_end , data = sex_df%>% mutate(across(contains("score"), ~.x-1)))

stargazer(list(m1,m2,m3,m4,m5),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest"), 
          covariate.labels = c("PSA FTA Risk Score", "PSA NCA Risk Score", "PSA NVCA Risk Score", 
                               "Female", "Days Released", "FTA*Female",
                               "NCA*Female", "NVCA*Female"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")
```
\newpage


# VPRAI gender
VPRAI
\newline
```{r fig.height=6, fig.width=10, dpi=1200}
risk_df <- eval_df %>%
  mutate(sex = factor(sex, levels = c("Male", "Female"))) %>%
  filter(tool_name == "vprai", !is.na(vprai_risk_score)) %>%
  group_by(vprai_risk_score, sex) %>%
  select(vprai_risk_score, sex, fta_flag, recid_arrested_flag, recid_filed_flag, recid_convicted_flag,
         any_pretrial_failure_flag, recid_arrest_violent_psa_flag) %>%
  pivot_longer(fta_flag:recid_arrest_violent_psa_flag) %>%
  mutate(name = case_when(name == "fta_flag" ~ "FTA",
                          name == "recid_arrested_flag" ~ "New Arrest",
                          name == "recid_filed_flag" ~ "New Filing",
                          name == "recid_convicted_flag" ~ "New Conviction",
                          name == "any_pretrial_failure_flag" ~ "FTA or New Arrest",
                          name == "recid_arrest_violent_psa_flag" ~ "New Violent Arrest"),
         name = factor(name, levels = c("FTA or New Arrest", "FTA", "New Arrest", "New Filing", "New Conviction", "New Violent Arrest"))) %>%
  filter(sex %in% c("Male", "Female")) 
  # filter(county %in% c("Los Angeles", "Sacramento"))

ggplot(risk_df) +
  aes(x = vprai_risk_score, y = value, color = sex) +
  geom_smooth(method = "glm", method.args = list(family=binomial), alpha = .2) +
  # geom_line() +
  # geom_point() +
  theme_bw() +
  # ylim(0,100) +
  facet_wrap(~name, scales = "free") +
  labs(x = "Risk Category", y = "Percent", title = "Comparison of Gender Differences in Logistic Regression Curves--VPRAI") +
  scale_x_continuous(breaks = 1:5)

# eval_df %>%
#   filter(tool_name == "vprai") %>%
#   count(county)
```
\newpage

VPRAI--With Interactions at lowest score
\newline
```{r results='asis'}
m1 <- glm(family = binomial(),fta_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m2 <- glm(family = binomial(),recid_arrested_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m3 <- glm(family = binomial(),recid_filed_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m4 <- glm(family = binomial(),recid_convicted_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-1)))
m6 <- glm(family = binomial(),any_pretrial_failure_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-1)))

stargazer(list(m1,m2,m3,m4,m5,m6),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest", "FTA or New Arrest"), 
          covariate.labels = c("VPRAI Risk Score", "Female",
                               "Days Released", "VPRAI*Female"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")
```
\newpage

VPRAI--With Interactions at highest score
\newline
```{r results='asis'}
m1 <- glm(family = binomial(),fta_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-5)))
m2 <- glm(family = binomial(),recid_arrested_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-5)))
m3 <- glm(family = binomial(),recid_filed_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-5)))
m4 <- glm(family = binomial(),recid_convicted_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-5)))
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-5)))
m6 <- glm(family = binomial(),any_pretrial_failure_flag ~ vprai_risk_score * sex + release_to_pretrial_end, data = sex_df %>% mutate(across(contains("score"), ~.x-5)))

stargazer(list(m1,m2,m3,m4,m5,m6),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest", "FTA or New Arrest"), 
          covariate.labels = c("VPRAI Risk Score", "Female",
                               "Days Released", "VPRAI*Female"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")
```
\newpage


# VPRAI race
VPRAI
\newline
```{r fig.height=6, fig.width=10, dpi=1200}
risk_df <- eval_df %>%
  mutate(race = factor(race, levels = c("White", "Black", "Hispanic", "Other_Unknown"))) %>%
  filter(tool_name == "vprai", !is.na(vprai_risk_score)) %>%
  group_by(vprai_risk_score, race) %>%
  select(vprai_risk_score, race, fta_flag, recid_arrested_flag, recid_filed_flag, recid_convicted_flag,
         any_pretrial_failure_flag, recid_arrest_violent_psa_flag) %>%
  pivot_longer(fta_flag:recid_arrest_violent_psa_flag) %>%
  mutate(name = case_when(name == "fta_flag" ~ "FTA",
                          name == "recid_arrested_flag" ~ "New Arrest",
                          name == "recid_filed_flag" ~ "New Filing",
                          name == "recid_convicted_flag" ~ "New Conviction",
                          name == "any_pretrial_failure_flag" ~ "FTA or New Arrest",
                          name == "recid_arrest_violent_psa_flag" ~ "New Violent Arrest"),
         name = factor(name, levels = c("FTA or New Arrest", "FTA", "New Arrest", "New Filing", "New Conviction", "New Violent Arrest"))) %>%
  filter(race %in% c("White", "Black", "Hispanic")) 
  # filter(county %in% c("Los Angeles", "Sacramento"))

ggplot(risk_df) +
  aes(x = vprai_risk_score, y = value, color = race) +
  geom_smooth(method = "glm", method.args = list(family=binomial), alpha = .2) +
  # geom_line() +
  # geom_point() +
  theme_bw() +
  # ylim(0,100) +
  facet_wrap(~name, scales = "free") +
  labs(x = "Risk Category", y = "Percent", title = "Comparison of Racial Differences in Logistic Regression Curves--VPRAI") +
  scale_x_continuous(breaks = 1:5)
```
\newpage


VPRAI--With Interactions at lowest score
\newline
```{r results='asis'}
m1 <- glm(family = binomial(),fta_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-1)))
m2 <- glm(family = binomial(),recid_arrested_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-1)))
m3 <- glm(family = binomial(),recid_filed_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-1)))
m4 <- glm(family = binomial(),recid_convicted_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-1)))
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ vprai_risk_score * race + release_to_pretrial_end, data =
            race_df %>% mutate(across(contains("score"), ~.x-1)))
m6 <- glm(family = binomial(), any_pretrial_failure_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-1)))

stargazer(list(m1,m2,m3,m4,m5,m6),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest", "FTA or New Arrest"), 
          covariate.labels = c("VPRAI Risk Score", "Race:Black", "Race:Hispanic",
                               "Days Released", "VPRAI*Black", "VPRAI*Hispanic"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")
```
\newpage

VPRAI--With Interactions at score 5
\newline
```{r results='asis'}
m1 <- glm(family = binomial(),fta_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-5)))
m2 <- glm(family = binomial(),recid_arrested_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-5)))
m3 <- glm(family = binomial(),recid_filed_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-5)))
m4 <- glm(family = binomial(),recid_convicted_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-5)))
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ vprai_risk_score * race + release_to_pretrial_end, data =
            race_df %>% mutate(across(contains("score"), ~.x-5)))
m6 <- glm(family = binomial(), any_pretrial_failure_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = race_df %>% mutate(across(contains("score"), ~.x-5)))

stargazer(list(m1,m2,m3,m4,m5,m6),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest", "FTA or New Arrest"), 
          covariate.labels = c("VPRAI Risk Score", "Race:Black", "Race:Hispanic",
                               "Days Released", "VPRAI*Black", "VPRAI*Hispanic"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")

```
\newpage





# San Joaquin race
San Joaquin
\newline
```{r fig.height=6, fig.width=10, dpi=1200}
risk_df <- eval_df %>%
  filter(county == "San Joaquin") %>%
  mutate(race = factor(race, levels = c("White", "Black", "Hispanic", "Other_Unknown"))) %>%
  filter(tool_name == "vprai", !is.na(vprai_risk_score)) %>%
  group_by(vprai_risk_score, race) %>%
  select(vprai_risk_score, race, fta_flag, recid_arrested_flag, recid_filed_flag, recid_convicted_flag,
         any_pretrial_failure_flag, recid_arrest_violent_psa_flag) %>%
  pivot_longer(fta_flag:recid_arrest_violent_psa_flag) %>%
  mutate(name = case_when(name == "fta_flag" ~ "FTA",
                          name == "recid_arrested_flag" ~ "New Arrest",
                          name == "recid_filed_flag" ~ "New Filing",
                          name == "recid_convicted_flag" ~ "New Conviction",
                          name == "any_pretrial_failure_flag" ~ "FTA or New Arrest",
                          name == "recid_arrest_violent_psa_flag" ~ "New Violent Arrest"),
         name = factor(name, levels = c("FTA or New Arrest", "FTA", "New Arrest", "New Filing", "New Conviction", "New Violent Arrest"))) %>%
  filter(race %in% c("White", "Black", "Hispanic")) 

ggplot(risk_df) +
  aes(x = vprai_risk_score, y = value, color = race) +
  geom_smooth(method = "glm", method.args = list(family=binomial), alpha = .2) +
  # geom_line() +
  # geom_point() +
  theme_bw() +
  # ylim(0,100) +
  facet_wrap(~name, scales = "free") +
  labs(x = "Risk Category", y = "Percent",
       title = "Comparison of Racial Differences in Logistic Regression Curves--VPRAI, San Joaquin") +
  scale_x_continuous(breaks = 1:5)

# eval_df %>%
#   filter(tool_name == "vprai") %>%
#   count(county)
```
\newpage
San Joaquin--With Interactions at lowest score
\newline
```{r results='asis'}
county_df <- race_df %>%
  filter(county == "San Joaquin") %>%
  mutate(across(contains("score"), ~.x-1))

m1 <- glm(family = binomial(),fta_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m2 <- glm(family = binomial(),recid_arrested_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m3 <- glm(family = binomial(),recid_filed_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m4 <- glm(family = binomial(),recid_convicted_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m6 <- glm(family = binomial(),any_pretrial_failure_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)


stargazer(list(m1,m2,m3,m4,m5, m6),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest", "FTA or New Arrest"), 
          covariate.labels = c("VPRAI Risk Score", "Race:Black", "Race:Hispanic",
                               "Days Released", "VPRAI*Black", "VPRAI*Hispanic"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")

```
\newpage
San Joaquin--With Interactions at highest score
\newline
```{r results='asis'}
county_df <- race_df %>%
  filter(county == "San Joaquin") %>%
  mutate(across(contains("score"), ~.x-5))

m1 <- glm(family = binomial(),fta_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m2 <- glm(family = binomial(),recid_arrested_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m3 <- glm(family = binomial(),recid_filed_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m4 <- glm(family = binomial(),recid_convicted_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m5 <- glm(family = binomial(),recid_arrest_violent_psa_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)
m6 <- glm(family = binomial(),any_pretrial_failure_flag ~ vprai_risk_score * race + release_to_pretrial_end, data = county_df)


stargazer(list(m1,m2,m3,m4,m5, m6),
          # type = "text",
          dep.var.labels = c("FTA", "New Arrest", "New Filing", 
                             "New Conviction", "New Violent Arrest", "FTA or New Arrest"), 
          covariate.labels = c("VPRAI Risk Score", "Race:Black", "Race:Hispanic",
                               "Days Released", "VPRAI*Black", "VPRAI*Hispanic"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(.05, .01, .001),
          notes = c("*p<0.05; **p<0.01; ***p<.001"),
          notes.append = F, font.size = "small")
```
\newpage
