---
output:
  pdf_document: default
  html_document: default
  word_document: default
---
# Tables for introductions for county-level validation studies
# Settup and Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

knitr::opts_knit$set(root.dir = "C:/PretrialPilot/Pretrial-Pilot-County-Analysis")


# library(rlang)
library(tidyverse)
library(data.table)
library(openxlsx)
#library(readxl)
library(lubridate)
library(gsubfn)
library(fuzzyjoin)
library(dplyr)
# library(multidplyr)
library(pROC)
library(broom)
library(kableExtra)
library(stargazer)
library(DBI)
library(dbplyr)
library(odbc)
library(tinytex)
library(gt)
# shell.exec(getwd())
```


MyKable function
```{r warning=FALSE, include=FALSE}
my_kable <- function(x){
  kable(x, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14, latex_options = "hold_position") %>%
    row_spec(nrow(x), bold = T)
    # column_spec(2, bold = T)
  # footnote(general_title = "", general = "Source: Judicial Council of California, Recidivism Reduction Fund Quarterly Reports (July 1, 2015-March 31, 2018).")  %>%
    
}


```
Connection
```{r}

con <- dbConnect(odbc::odbc(), "snowflake_pretrial", uid ="Sal.Lempert@jud.ca.gov", pwd = rstudioapi::askForPassword("Password"))

```

Pull snowflake data -- cjs_df_std 
```{sql connection=con, include=FALSE, output.var='df'}
SELECT *
FROM "DWH_PROD"."DATA_SCIENCE"."CJS_DF_STD"
;
```

Pull snowflake data -- cjs_outcome_std 
```{sql connection=con, include=FALSE, output.var='full_df'}
SELECT *
FROM "DWH_PROD"."DATA_SCIENCE"."CJS_OUTCOME_STD"
;
```
\newpage

Format df
```{r}
names(df) <- tolower(names(df))

df <- df %>%
  mutate(tool_name_orig = tool_name,
         tool_name = case_when(county_name == "Modoc" ~ "ORAS",
                               county_name == "Yuba" ~ "ORAS",
                               county_name == "San Joaquin" ~ "VPRAI",
                               T ~ tool_name_standard),
         county = county_name,
         County = case_when(county %in% c("Calaveras", "Modoc", "Tuolumne", "Yuba") ~ "Small Counties",
                            county %in% c("Kings", "Napa", "Nevada", "Sierra") ~ "Small/Medium Counties",
                            T ~ county),
         County = ordered(County),
         County = fct_relevel(County, levels = c("Small Counties", "Small/Medium Counties")),
         charge_level_orig = charge_level,
         charge_level = charge_level_standard,
         arrest_charge_level = charge_level,
         age = individual_age,
         sex_orig = sex,
         sex = if_else(sex %in% c("Male", "Female"), sex, "Other/Unknown"),
         race_orig = race,
         race = if_else(race_standard == "American Indian", "Other/Unknown", race_standard),
         oras_risk_score = if_else(tool_name == "ORAS", risk_score_raw, NULL),
         vprai_risk_score = if_else(tool_name == "VPRAI", risk_score_raw, NULL),
         vprair_risk_score = if_else(tool_name == "VPRAI-R", risk_score_raw, NULL),
         vpraio_risk_score = if_else(tool_name == "VPRAI-O", generic_tool_total_score_raw, NULL),
         psa_fta_risk_score = score_failure_to_appear,
         psa_nca_risk_score = score_new_criminal_activity,
         psa_nvca_risk_score = score_new_criminal_violent_activity,
         scored_assessment = if_else(tool_name %in% c("ORAS", "VPRAI", "VPRAI-R") & !is.na(risk_score_raw) |
                                       tool_name == "PSA" & !is.na(score_new_criminal_activity) |
                                       tool_name == "VPRAI-O" & !is.na(generic_tool_total_score_raw), 1, 0),
         monitor_level = if_else(monitoring_level_grouped %in% c("Lowest Levels", "Medium Levels", "Highest Levels"), monitoring_level_grouped, "Other/Unknown")) %>%
  arrange(County) %>%
  filter(assessment_date >= as.Date("2019-10-01"),
         assessment_date <= as.Date("2021-12-31")) %>%
  filter(scored_assessment == 1)
```

\newpage

Format full_df, join_df, and eval_df
```{r warning=FALSE, include=FALSE}
snow_df <- full_df

names(full_df) <- tolower(names(full_df))

full_df <- full_df %>%
  mutate(book_date = booking_date,
         race_orig = race,
         race = if_else(race_standard == "American Indian", "Other/Unknown", race_standard),
         County = case_when(county %in% c("Calaveras", "Modoc", "Tuolumne", "Yuba") ~ "Small Counties",
                            county %in% c("Kings", "Napa", "Nevada", "Sierra") ~ "Small/Medium Counties",
                            T ~ county),
         County = ordered(County),
         County = fct_relevel(County, levels = c("Small Counties", "Small/Medium Counties")),
         new_arrest_flag = release_eligible_count,
         charge_level_orig = charge_level,
         charge_level = charge_level_standard,
         arrest_charge_level = case_when(charge_level == "F" ~ "Felony",
                                         charge_level == "M" ~ "Misdemeanor",
                                         charge_level == "I" ~ "Infraction",
                                         T ~ "Other/Unknown"),
         pretrial_period_end_count = pretrial_period_end_count_standard,
         monitor_level = if_else(monitoring_level_grouped %in% c("Lowest Levels", "Medium Levels", "Highest Levels"), monitoring_level_grouped, "Other/Unknown"),
         fta_flag = fta_county_or_doj,
         recid_arrested_flag = recid_county_or_doj,
         age = indiv_age,
         tool_name = if_else(county == "Kings", "VPRAIO", tool_name),
         oras_risk_score = if_else(tool_name == "ORAS", risk_score_raw, NULL),
         vprai_risk_score = if_else(tool_name == "VPRAI", risk_score_raw, NULL),
         vprair_risk_score = if_else(tool_name == "VPRAIR", risk_score_raw, NULL),
         vpraio_risk_score = if_else(tool_name == "VPRAIO", generic_tool_total_score_raw, NULL),
         psa_fta_risk_score = score_failure_to_appear,
         psa_nca_risk_score = score_new_criminal_activity,
         psa_nvca_risk_score = score_new_criminal_violent_activity,
         scored_assessment = if_else(tool_name %in% c("ORAS", "VPRAI", "VPRAIR") & !is.na(risk_score_raw) |
                                       tool_name == "PSA" & !is.na(score_new_criminal_activity) |
                                       tool_name == "VPRAIO" & !is.na(generic_tool_total_score_raw), 1, 0),
         pretrial_period_end_date = if_else(is.na(pretrial_period_end_date), as.Date(pretrial_period_end_date_doj), as.Date(pretrial_period_end_date))) %>%
  mutate(recid_filed_flag = recid_filed_flag_doj, 
         recid_convicted_flag = recid_convicted_flag_doj, 
         recid_arrest_violent_psa_flag = recid_arrest_violent_psa_flag_doj,
         recid_filed_violent_psa_flag = recid_filed_violent_psa_flag_doj,
         any_pretrial_failure_flag = if_else(recid_arrested_flag == 1 | fta_flag == 1, 1, 0)) %>% ## update this when we get county data on these
  mutate(across(contains("_flag"), ~if_else(is.na(.x), 0, as.numeric(.x)))) %>%
  arrange(County) 

join_df <- full_df  %>%
  filter(booking_date >= as.Date("2019-10-01"),
         booking_date <= as.Date("2021-12-31"))


eval_df <- full_df %>%
  filter(booking_assessed_count == 1,
         scored_assessment == 1,
         release_eligible_count ==1,
         released_pretrial_count == 1,
         pretrial_period_end_count == 1,
         booking_date < as.Date("2022-01-01"),
         tool_name %in% c("ORAS", "PSA", "VPRAI", "VPRAIR", "VPRAIO")
         ) %>%
  mutate(release_to_pretrial_end = pretrial_period_end_date - release_date)


```

# Date range for indiv counties
```{r}
date_df <- eval_df %>%
  group_by(county) %>%
  summarise(min_date = min(assessment_date), max_date = max(assessment_date)) 

names(date_df) <- c("County", "Earliest Assessment Date", "Latest Assessment Date")

kable(date_df, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14, latex_options = "hold_position")

# gt(date_df) %>%
#   gtsave(filename = "dates by county.html")
```

# Drop-Off
```{r}

drop_df1 <- df %>%
  filter(!is.na(risk_score)) %>%
  mutate(county = if_else(county %in% c("Sierra", "Nevada"), "Nevada/Sierra", county)) %>%
  count(tool_name, county)

drop_df2 <- full_df %>%
  filter(!is.na(tool_name)) %>%
  mutate(county = if_else(county %in% c("Sierra", "Nevada"), "Nevada/Sierra", county)) %>%
  group_by(tool_name, county) %>%
  summarise('Assessed Bookings' = sum(booking_assessed_count), 
            'Pretrial Complete' = sum(booking_assessed_count*pretrial_period_end_count),
            'Validation Dataset' = sum(booking_assessed_count*pretrial_period_end_count*released_pretrial_count))

drop_df <- drop_df1 %>%
  left_join(drop_df2) %>%
  rename('Assessments' = n,
         'Tool Name' = tool_name,
         'County' = county)

drop_df_out <- drop_df %>%
  mutate(`Validation Type` = case_when(`Validation Dataset` >= 1000 ~ "General + Bias",
                                       `Validation Dataset` >= 200 ~ "General Only",
                                       `Validation Dataset` < 200 ~ "Sample Too Small")) %>%
  arrange(`Validation Type`) %>%
  ungroup()

kable(drop_df_out , booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    column_spec(3:6, width = "1.5cm") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 10, 
                  latex_options = "hold_position") 

# gt(drop_df_out) %>%
#   gtsave(filename = "drop off by county.html")

# gt(drop_df_out %>% filter(County == "Los Angeles")) %>%
#   gtsave(filename = "drop off LA.html")
```



# The Percent of Assessments by Demographic
```{r}
race_df <- eval_df %>%
  count(county, race) %>%
  group_by(county) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  race, values_from =  n, values_fill = 0) %>%
  select(county, Black, White, Hispanic, "Other" = 'Other/Unknown', Total) %>%
  bind_rows(eval_df %>%
              count(race) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  race, values_from =  n, values_fill = 0) %>%
              mutate(county = "Total") %>%
              select(county, Black, White, Hispanic, "Other" = 'Other/Unknown', Total)) %>%
  mutate_at(vars("Black", "White", "Hispanic", "Other"), funs(round(./Total*100)))

gender_df <- eval_df %>%
  count(county, sex) %>%
  group_by(county) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  sex, values_from =  n, values_fill = 0) %>%
  select(county, Male, Female, Total) %>%
  bind_rows(eval_df %>%
              count(sex) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  sex, values_from =  n, values_fill = 0) %>%
              mutate(county = "Total") %>%
              select(county, Male, Female, Total)) %>%
  mutate_at(vars("Male", "Female"), funs(round(./Total*100)))

age_df <- eval_df %>%
  group_by(county) %>%
  summarise(age = median(age, na.rm = T)) %>%
  bind_rows(eval_df %>%
              summarise(age = median(age, na.rm = T)) %>%
              mutate(county = "Total"))


demo_df <- left_join(race_df, gender_df) %>%
  left_join(age_df) %>%
  select("County" = county, Total, everything(), "Median Age" = age)

my_kable(demo_df) %>%
  add_header_above(c(" " = 2, "Race/Ethnicity (%)" = 4, "Gender (%)" = 2, " " = 1))

# gt(demo_df) %>%
#   gtsave(filename = "demographics by county.html")
```
Source: Pretrial Pilot Multi-Agency Linked Data. Data are limited to bookings with a defendant released pretrial and a completed pretrial period.
\newpage

# Arrest Offenses
```{r eval=FALSE, include=FALSE}
arrest_df <- eval_df %>%
  group_by(county) %>%
  summarise_at(vars(arrest_felony_flag, arrest_misd_flag, arrest_violent_psa_flag, arrest_property_flag, arrest_drug_flag,
                    arrest_dui_flag, arrest_dv_flag), funs(round(mean(.)*100))) %>%
  mutate(arrest_misd_flag = 100 - arrest_felony_flag) 

names(arrest_df) <- c("County", "Felony", "Misdemeanor", "Violent", "Property", "Drug", "DUI", "DV")

kable(arrest_df, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14, latex_options = "hold_position")
```

# Adverse Outcomes
```{r}
outcome_df <- eval_df %>%
  group_by(county) %>%
  summarise_at(vars(fta_flag, recid_arrested_flag, recid_filed_flag, recid_convicted_flag, 
                    recid_arrest_violent_psa_flag), 
                    # any_pretrial_failure_flag),
               funs(round(mean(.)*100, 1)))

names(outcome_df) <- c("County", "FTA", "New Arrest", "New Filing", "New Conviction", "New Violent Arrest") 
                       # "FTA or New Arrest")

kable(outcome_df, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14, latex_options = "hold_position")

# gt(outcome_df) %>%
#   gtsave(filename = "outcome rates by county.html")
```

#LA only tables
```{r}
kable(drop_df_out %>% filter(County == "Los Angeles") , booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    column_spec(3:6, width = "1.5cm") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 10, 
                  latex_options = "hold_position") 


kable(demo_df %>% filter(County == "Los Angeles"), booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex")  %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 10, 
                  latex_options = "hold_position") %>%
  add_header_above(c(" " = 2, "Race/Ethnicity (%)" = 4, "Gender (%)" = 2, " " = 1))


kable(outcome_df %>% filter(County == "Los Angeles"), booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14, latex_options = "hold_position")
```