---
output:
  pdf_document: default
  html_document: default
---
# Tables for introductions for county-level validation studies
# Settup and Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
#knitr::opts_knit$set(root.dir = "G:/CrimJustice/PretrialAssessmentPilot")

# library(rlang)
library(tidyverse)
library(data.table)
library(openxlsx)
library(readxl)
library(lubridate)
library(gsubfn)
library(fuzzyjoin)
library(dplyr)
library(openxlsx)
library(fuzzyjoin)
# library(multidplyr)
library(pROC)
library(broom)
library(kableExtra)
library(stargazer)

# shell.exec(getwd())
```


MyKable function
```{r warning=FALSE, include=FALSE}
my_kable <- function(x){
  kable(x, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14, latex_options = "hold_position") %>%
    row_spec(nrow(x), bold = T)
    # column_spec(2, bold = T)
  # footnote(general_title = "", general = "Source: Judicial Council of California, Recidivism Reduction Fund Quarterly Reports (July 1, 2015-March 31, 2018).")  %>%
    
}


```

```{r}
# This is really going to be a focus on assessments matched with bookings. 
drop_df <- full_df %>%
  filter(new_arrest_flag == 1,
         !is.na(assessment_date)) %>%
  mutate(pretrial_end_date = if_else(is.na(pretrial_end_date), pretrial_end_date_doj, pretrial_end_date)) %>%
  mutate(arrest_charge_level = case_when(is.na(arrest_charge_level)|arrest_charge_level %in% c("Other", "I") ~"Other_Unknown",
                                         arrest_charge_level == "F" ~ "Felony",
                                         arrest_charge_level == "M" ~ "Misdemeanor")) %>%
  filter(!is.na(cii)) %>%
  mutate(monitor_level = case_when(
    monitor_level %in% c("Level I - Pretrial Release Supervision",
                                     "Pretrial Supervision Level I", "1", "Low") ~ "Low",
    monitor_level %in% c("Level II - Pretrial Release Supervision",
                                     "Pretrial Supervision Level II", "2", "Medium") ~ "Medium",
    monitor_level %in% c("Level III - Pretrial Release Supervision",
                                     "Pretrial Supervision Level III", "3:4", "High") ~ "High",
                              T ~ monitor_level)) %>%
  mutate(fta_flag = if_else(fta_flag == 1|arrest_fta_flag == 1|court_fta_flag == 1|court_fta_flag_doj == 1, 1, 0),
         revoked_flag = if_else(pretrial_termination_outcome == "Unsuccessful", 1, 0),
         oras_risk_score = if_else(oras_risk_score == -Inf, NA_real_, oras_risk_score)) %>%
  mutate(monitor_level = factor(monitor_level, levels = c("Low", "Medium", "High", "Other_Unknown"))) %>%
  mutate(county = tools::toTitleCase(gsub("_", " ", county))) %>%
  mutate(pre_trial_release_flag = if_else(release_date >= pretrial_end_date|is.na(release_date), 0, 1)) %>%
  mutate(sex = case_when(sex == "F" ~ "Female",
                         sex == "M" ~ "Male",
                         T ~ sex),
         tool_name = gsub("-", "", tool_name),
         tool_name = if_else(county == "Alameda" & !is.na(assessment_date), "vprair", tool_name),
         tool_name = if_else(county == "Yuba" & !is.na(assessment_date), "oras", tool_name),
         tool_name = if_else(tool_name == "ORASPAT", "oras", tolower(tool_name)),
         tool_name = if_else(tool_name == "null", NA_character_, tool_name)) %>%
  mutate(release_type = case_when(
    county %in% c("San Joaquin", "Ventura", "Alameda", "Tuolumne", "Nevada", "San Mateo", "Kings") &
      release_type_original %in% c("EMERGENCY ZERO BAIL", "Zero Bail", "TEMPORARY EMERGENCY BAIL",
                                   "TEMPORARY EMERGENCY CITATION", "Covid 19", "Emergency Bail Schedule",
                                   "ZERO DOLLAR BAIL", "COVID-Pretrial Court-Order", "Pandemic Citation Release", 
                                   "Pandemic Sentence Release", "Emergency Bail Schedule-Cite", 
                                   "Emergency Bail Schedule-Court") ~ "Zero_Bail",
    county %in% c("San Joaquin", "Ventura", "Alameda", "Tuolumne", "Nevada", "San Mateo", "Kings") & 
      release_type == "Bail_Bond" ~ "Non_Zero_Bail",
    (!county %in% c("San Joaquin", "Ventura", "Alameda", "Tuolumne", "Nevada", "San Mateo", "Kings")) & 
      release_type == "Bail_Bond" ~ "Unknown_Bail",
    T ~ release_type)) %>%
  mutate(arrest_charge_level = case_when(is.na(arrest_charge_level)|arrest_charge_level %in% c("Other", "I") ~"Other_Unknown",
                                         arrest_charge_level == "F" ~ "Felony",
                                         arrest_charge_level == "M" ~ "Misdemeanor")) %>%
  filter(tool_name %in% c("oras", "psa", "vprai", "vprair", "ccat", "vpraio")) %>%
   filter((psa_nca_risk_score %in% c(1:6) &
         psa_fta_risk_score %in% c(1:6))|tool_name != "psa") %>%
  group_by(tool_name, county) %>%
  summarise("Assessed Bookings" = n(),
            "Has End Date" = sum(!is.na(pretrial_end_date), na.rm = T),
            "Released Pretrial" = sum(pretrial_end_date - as_date(release_date) > 0, na.rm = T)) %>%
  rename("Tool Name" = tool_name) %>%
  mutate(`Tool Name` = toupper(`Tool Name`)) %>%
  arrange(county)


files <- list.files("Assessment Output Tables", pattern = "RData", full.names = T)

assess_df <- lapply(files, function(x) {
  load(file = x)
  df <- get(ls()[!ls() %in% c("files", "court_df", "assess_df", "eval_df", "full_df", "drop_df")]) %>%
    filter(assessment_date >= as_date("2016-11-08")) %>%
    group_by(tool_name, county) %>%
    mutate(assessment_date = if_else(assessment_date == -Inf|assessment_date == Inf, NA_Date_, as_date(assessment_date))) %>%
    summarise(assessments = n(), min_assessment_date = min(assessment_date, na.rm = T), max_assessment_date = max(assessment_date, na.rm = T))
}) %>% bind_rows() 

assess_df <- assess_df %>%
  arrange(county)

drop_df$`Released Pretrial` <- (eval_df %>%
                                  arrange(county) %>%
                                  count(county, tool_name))$n


assess_df <- assess_df %>%
  mutate(tool_name = gsub("-", "", tolower(tool_name)),
         tool_name = if_else(county == "Alameda","vprair", tool_name),
         tool_name = if_else(county == "Yuba", "oras", tool_name),
         tool_name = if_else(tool_name == "oraspat", "oras", tolower(tool_name)),
         tool_name = if_else(tool_name == "null", NA_character_, tool_name)) %>%
  filter(tool_name %in% c("oras", "psa", "vprai", "vprair", "ccat", "vpraio")) %>%
  group_by(tool_name, county) %>%
  summarise(Assessments = sum(assessments)) %>%
  rename("Tool Name" = tool_name) %>%
  mutate(`Tool Name` = toupper(`Tool Name`)) %>%
  arrange(county)

drop_df <- assess_df %>%
  left_join(drop_df)

names(drop_df)[2] <- "County"
names(drop_df)[5] <- "Pretrial Complete" 

save(drop_df, file = "Assessment to Validation Drop Off.RData")


```

# Date range for indiv counties
```{r}
date_df <- eval_df %>%
  group_by(county) %>%
  summarise(min_date = min(assessment_date), max_date = max(assessment_date)) 

names(date_df) <- c("County", "Earliest Assessment Date", "Latest Assessment Date")

kable(date_df, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14, latex_options = "hold_position")

gt(date_df) %>%
  gtsave(filename = "dates by county.html")
```

# Drop-Off
```{r}

drop_df1 <- df %>%
  filter(!is.na(risk_score)) %>%
  mutate(county = if_else(county %in% c("Sierra", "Nevada"), "Nevada/Sierra", county)) %>%
  count(tool_name, county)

drop_df2 <- full_df %>%
  filter(!is.na(tool_name)) %>%
  mutate(county = if_else(county %in% c("Sierra", "Nevada"), "Nevada/Sierra", county)) %>%
  group_by(tool_name, county) %>%
  summarise('Assessed Bookings' = sum(booking_assessed_count), 
            'Pretrial Complete' = sum(booking_assessed_count*pretrial_period_end_count),
            'Validation Dataset' = sum(booking_assessed_count*pretrial_period_end_count*released_pretrial_count))

drop_df <- drop_df1 %>%
  left_join(drop_df2) %>%
  rename('Assessments' = n,
         'Tool Name' = tool_name,
         'County' = county)

drop_df_out <- drop_df %>%
  mutate(`Validation Type` = case_when(`Validation Dataset` >= 1000 ~ "General + Bias",
                                       `Validation Dataset` >= 200 ~ "General Only",
                                       `Validation Dataset` < 200 ~ "Sample Too Small")) %>%
  arrange(`Validation Type`) %>%
  ungroup()

kable(drop_df_out , booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    column_spec(3:6, width = "1.5cm") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 10, 
                  latex_options = "hold_position") 

gt(drop_df_out) %>%
  gtsave(filename = "drop off by county.html")

gt(drop_df_out %>% filter(County == "Los Angeles")) %>%
  gtsave(filename = "drop off LA.html")
```

# The Percent of Assessments by Demographic
```{r}
race_df <- eval_df %>%
  count(county, race) %>%
  group_by(county) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  race, values_from =  n, values_fill = 0) %>%
  select(county, Black, White, Hispanic, "Other" = 'Other/Unknown', Total) %>%
  bind_rows(eval_df %>%
              count(race) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  race, values_from =  n, values_fill = 0) %>%
              mutate(county = "Total") %>%
              select(county, Black, White, Hispanic, "Other" = 'Other/Unknown', Total)) %>%
  mutate_at(vars("Black", "White", "Hispanic", "Other"), funs(round(./Total*100)))

gender_df <- eval_df %>%
  count(county, sex) %>%
  group_by(county) %>%
  mutate(Total = sum(n)) %>%
  pivot_wider(names_from =  sex, values_from =  n, values_fill = 0) %>%
  select(county, Male, Female, Total) %>%
  bind_rows(eval_df %>%
              count(sex) %>%
              mutate(Total = sum(n)) %>%
              pivot_wider(names_from =  sex, values_from =  n, values_fill = 0) %>%
              mutate(county = "Total") %>%
              select(county, Male, Female, Total)) %>%
  mutate_at(vars("Male", "Female"), funs(round(./Total*100)))

age_df <- eval_df %>%
  group_by(county) %>%
  summarise(age = median(age, na.rm = T)) %>%
  bind_rows(eval_df %>%
              summarise(age = median(age, na.rm = T)) %>%
              mutate(county = "Total"))


demo_df <- left_join(race_df, gender_df) %>%
  left_join(age_df) %>%
  select("County" = county, Total, everything(), "Median Age" = age)

my_kable(demo_df) %>%
  add_header_above(c(" " = 2, "Race/Ethnicity (%)" = 4, "Gender (%)" = 2, " " = 1))

gt(demo_df) %>%
  gtsave(filename = "demographics by county.html")
```
Source: Pretrial Pilot Multi-Agency Linked Data. Data are limited to bookings with a defendant released pretrial and a completed pretrial period.
\newpage

# Arrest Offenses
```{r}
arrest_df <- eval_df %>%
  group_by(county) %>%
  summarise_at(vars(arrest_felony_flag, arrest_misd_flag, arrest_violent_psa_flag, arrest_property_flag, arrest_drug_flag,
                    arrest_dui_flag, arrest_dv_flag), funs(round(mean(.)*100))) %>%
  mutate(arrest_misd_flag = 100 - arrest_felony_flag) 

names(arrest_df) <- c("County", "Felony", "Misdemeanor", "Violent", "Property", "Drug", "DUI", "DV")

kable(arrest_df, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14, latex_options = "hold_position")
```

# Adverse Outcomes
```{r}
outcome_df <- eval_df %>%
  group_by(county) %>%
  summarise_at(vars(fta_flag, recid_arrested_flag, recid_filed_flag, recid_convicted_flag, 
                    recid_arrest_violent_psa_flag), 
                    # any_pretrial_failure_flag),
               funs(round(mean(.)*100, 1)))

names(outcome_df) <- c("County", "FTA", "New Arrest", "New Filing", "New Conviction", "New Violent Arrest") 
                       # "FTA or New Arrest")

kable(outcome_df, booktabs = T, format.args = list(big.mark = ","), 
        # table.attr = "style = \"color: black;\"",
        format = "latex") %>%
    kable_styling(position = "center", full_width = F, 
                  bootstrap_options = c("striped", "hover"), stripe_color = "gray", font_size = 14, latex_options = "hold_position")

gt(outcome_df) %>%
  gtsave(filename = "outcome rates by county.html")
```

