---
title: "SB 129"
output: html_document
date: '2022-11-28'
---
# Settup and Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
knitr::opts_knit$set(root.dir = "C:/PretrialPilot/Pretrial-Pilot-County-Analysis")

# library(rlang)
library(tidyverse)
library(data.table)
library(openxlsx)
library(lubridate)
library(dplyr)
library(broom)
library(DBI)
library(dbplyr)
library(odbc)

# shell.exec(getwd())
```

# Get Snowflake data
Connection
```{r include=FALSE}
con <- dbConnect(odbc::odbc(), "snowflake_pretrial", uid ="Sal.Lempert@jud.ca.gov", pwd = rstudioapi::askForPassword("Password"))


```

Pull live snowflake data -- join_df
```{sql echo=TRUE, connection=con, output.var='join_df'}
SELECT *
FROM "DWH_PROD"."DATA_SCIENCE"."JOIN_DF_STD"
;
```

Pull additional variables - monitoring start date and pretrial termination date
```{sql echo=TRUE, connection=con, output.var='mon_df'}
SELECT 'Alameda' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
FROM "01_ALAMEDA-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Calaveras' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "05_CALAVERAS-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Kings' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "16_KINGS-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Los Angeles' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "19_LOSANGELES-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Modoc' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "25_MODOC-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Napa' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "28_NAPA-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Nevada' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "29_NEVADA-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Sacramento' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "34_SACRAMENTO-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'San Joaquin' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "39_SANJOAQUIN-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'San Mateo' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "41_SANMATEO-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Santa Barbara' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "42_SANTABARBARA-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Sierra' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "46_SIERRA-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Sonoma' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "49_SONOMA-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Tulare' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "54_TULARE-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Tuolumne' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "55_TUOLUMNE-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Ventura' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "56_VENTURA-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"

UNION ALL

SELECT  'Yuba' as county, BOOKING_KEY, DIM_PRETRIAL_MONITORING_START_DATE_KEY, DIM_PRETRIAL_TERMINATION_DATE_KEY
from "58_YUBA-DWH_PROD"."SECURE_SHARE"."FACT_PRETRIAL_ASSESSMENT"
;
```

Format data - join df  
```{r warning=FALSE, include=FALSE}

names(join_df) <- tolower(names(join_df))

join_df <- join_df %>%
  mutate(book_date = booking_date,
         race_orig = race,
         race = if_else(race_standard %in% c("White", "Black", "Hispanic"), race_standard, "Other/Unknown"),
         age = individual_age,
         charge_level_orig = charge_level,
         charge_level = charge_level_standard)%>%
  mutate(across(contains("_flag"), ~if_else(is.na(.x) | .x == "No" | .x == "Unknown" | .x == "0" | .x == 0, 0, as.numeric(1))))  

```



SB 129 numbers
```{r}
rep_df <- join_df %>%
  filter(booking_date >= as.Date("2021-07-01")) %>%
  mutate(rep_q = case_when(booking_date < as.Date("2022-01-01") ~ "FY1 Q1-2",
                           booking_date < as.Date("2022-04-01") ~ "FY1 Q3",
                           booking_date < as.Date("2022-07-01") ~ "FY1 Q4",
                           booking_date < as.Date("2022-10-01") ~ "FY2 Q1",
                           booking_date < as.Date("2023-01-01") ~ "FY2 Q2",
                           booking_date < as.Date("2023-04-01") ~ "FY2 Q3",
                           booking_date < as.Date("2023-07-01") ~ "FY2 Q4",
                           booking_date < as.Date("2023-10-01") ~ "FY3 Q1",
                           booking_date < as.Date("2024-01-01") ~ "FY3 Q2",
                           booking_date < as.Date("2024-04-01") ~ "FY3 Q3")) %>%
  mutate(rel_within_2days = case_when(
    weekdays(book_date) == "Thursday" & release_date - book_date <= 4 ~ 1,
    weekdays(book_date) == "Friday" & release_date - book_date <= 4 ~ 1,
    weekdays(book_date) == "Saturday" & release_date - book_date <= 3 ~ 1,
    !weekdays(book_date) %in% c("Thursday", "Friday", "Saturday") & release_date - book_date <= 2 ~ 1,
    is.na(release_date) ~ 0,
    T ~ 0)) %>%
  mutate(rel_after_2days = if_else(!is.na(release_date) & rel_within_2days == 0, 1, 0)) %>%
  mutate(age_grp = case_when(age %in% 18:25 ~ "18-25",
                             age %in% 26:35 ~ "26-35",
                             age %in% 36:45 ~ "36-45",
                             age %in% 46:55 ~ "46-55",
                             age > 55 ~ "Over 56",
                             T ~ "Other")) %>%
  mutate(race = if_else(race_standard %in% c("White", "Black", "Hispanic", "Asian"), race_standard, "Other/Unknown")) %>%
  mutate(sex_standard = case_when(sex %in% c("Female") ~ "Female",
                                  sex %in% c("M", "Male") ~ "Male",
                                  T ~ "Other/Unknown")) %>%
  mutate(release_type = case_when(release_type %in% c("Cite Release", "CiteR elease") ~ "Jail Cite and Release",
                                  release_type %in% c("Bail Bond") ~ "Release on Bail",
                                  release_type %in% c("Own Recognizance") ~ "Release by Judicial Officer on OR",
                                  release_type %in% c("Pretrial Monitor") ~ "Pretrial Supervision",
                                  release_type %in% c("Detain only", "Detain Only", "Dismissed") ~ "No Charges Filed/Charges Dismissed",
                                  release_type %in% c("Prison", "Time Served") ~ "Charges Resolved (includes by plea)",
                                  release_type %in% c("Zero Bail") ~ "Zero Bail",
                                  T ~ "Other"))

rep_df <- rep_df %>%
  mutate(monitoring_level_grouped = if_else(monitoring_level_grouped %in% c("Alameda.GPS Monitoring","Alameda.Alcohol Monitoring","Alameda.GPS and Alcohol Monitoring"), "Highest Levels", monitoring_level_grouped))


```

Format mon_df and join to rep_df
```{r}
names(mon_df) <- tolower(names(mon_df))

mon_dfj <- mon_df %>%
  filter(!is.na(booking_key))

mon_dfj <- mon_dfj %>%
  mutate(monitoring_start_date = ymd(dim_pretrial_monitoring_start_date_key)) %>%
  filter(dim_pretrial_monitoring_start_date_key !=0) %>%
  select(-dim_pretrial_monitoring_start_date_key, -dim_pretrial_termination_date_key)

rep_df <- rep_df %>%
  mutate(rownum = row_number()) %>%
  left_join(mon_dfj, by = c('county', 'booking_key')) %>%
  distinct(rownum, .keep_all = T) %>%
  select(-rownum)

```

Test code to look at all open monitoring cases in each quarter, whether or not they started that quarter
```{r}
test <- rep_df %>%
  filter(release_type == "Pretrial Supervision" | monitoring_level_grouped %in% c("Lowest Levels", "Medium Levels", "Highest Levels"))
  
test <- test %>%
   mutate(FY1Q12 = if_else("2021-07-01" < pretrial_termination_date & monitoring_start_date < "2022-01-01", 1, 0),
          FY1Q3 = if_else("2022-01-01" < pretrial_termination_date& monitoring_start_date < "2022-04-01", 1, 0),
          FY1Q4 = if_else("2022-04-01" < pretrial_termination_date & monitoring_start_date < "2022-07-01", 1, 0),
          FY2Q1 = if_else("2022-07-01"  < pretrial_termination_date & monitoring_start_date < "2022-10-01", 1, 0),
          FY2Q2 = if_else("2022-10-01" < pretrial_termination_date & monitoring_start_date < "2023-01-01", 1, 0),
          FY2Q3 = if_else("2023-01-01" < pretrial_termination_date & monitoring_start_date < "2023-04-01", 1, 0),
          FY2Q4 = if_else("2023-04-01" < pretrial_termination_date & monitoring_start_date < "2023-07-01", 1, 0),
          FY3Q1 = if_else("2023-07-01" < pretrial_termination_date & monitoring_start_date < "2023-10-01", 1, 0),
          FY3Q2 = if_else("2023-10-01" < pretrial_termination_date & monitoring_start_date < "2024-01-01", 1, 0),
          FY3Q3 = if_else("2024-01-01" < pretrial_termination_date & monitoring_start_date < "2024-04-01", 1, 0))
  
  
test %>% 
  select(county, 'FY1Q12', 'FY1Q3', 'FY1Q4', 'FY2Q1', 'FY2Q2', 'FY2Q3', 'FY2Q4', 'FY3Q1', 'FY3Q2', 'FY3Q3') %>%
  pivot_longer(cols = c('FY1Q12', 'FY1Q3', 'FY1Q4', 'FY2Q1', 'FY2Q2', 'FY2Q3', 'FY2Q4', 'FY3Q1', 'FY3Q2', 'FY3Q3'), names_to = "rep_quart", values_to = "flag") %>%
  group_by(county, rep_quart) %>%
  summarise(tot = sum(flag, na.rm = T))
```


```{r}
out <- createWorkbook()

#Q1: Total bookings (all bookings even if not eligible for pretrial release)
addWorksheet(out, "1 Total Bookings")

q1 <- rep_df %>%
  group_by(county, rep_q) %>%
  count()

writeData(out, sheet = "1 Total Bookings", x = q1)

#Q2: New offense bookings by misdo/fel
addWorksheet(out, "2 New offense misd.fel")
q2 <- rep_df %>%
  filter(county %in% c("Los Angeles", "Tulare", "Yuba") | booking_type %in% c("On View", "New Warrant", "Warrant")) %>%
  filter(charge_level %in% c("M", "F")) %>%
  group_by(county, rep_q, charge_level) %>%
  count()

writeData(out, sheet = "2 New offense misd.fel", x = q2)


#Q3: New offense released within 2 days by release type and misd/fel
addWorksheet(out, "3 Released within 2 days")
q3 <- rep_df %>%
  filter(county %in% c("Los Angeles", "Tulare", "Yuba") | booking_type %in% c("On View", "New Warrant", "Warrant")) %>%
  filter(charge_level %in% c("M", "F")) %>%
  filter(!is.na(release_date), rel_within_2days == 1) %>%
  group_by(county, rep_q, charge_level, release_type) %>%
  count()%>%
  arrange(county, charge_level, release_type, rep_q)

writeData(out, sheet = "3 Released within 2 days", x = q3)


#Q3: New offense released after 2 days by release type and misd/fel
addWorksheet(out, "4 Released after 2 days")
q4 <- rep_df %>%
  filter(county %in% c("Los Angeles", "Tulare", "Yuba") | booking_type %in% c("On View", "New Warrant", "Warrant")) %>%
  filter(charge_level %in% c("M", "F")) %>%
  filter(!is.na(release_date), rel_after_2days == 1) %>%
  group_by(county, rep_q, charge_level, release_type) %>%
  count()%>%
  arrange(county, charge_level, release_type, rep_q)

writeData(out, sheet = "4 Released after 2 days", x = q4)

#Q5: Total quarterly bookings by demographics
addWorksheet(out, "5 Tot qtly bookings by sex")

q5_sex <- rep_df %>%
  filter(sex %in% c("Male", "Female")) %>%
  group_by(county, rep_q, sex) %>%
  count(name = 'tot_bookings') 

writeData(out, sheet = "5 Tot qtly bookings by sex", x = q5_sex)

addWorksheet(out, "5 Tot qtly bookings by age")

q5_age <- rep_df %>%
  filter(age_grp != "Other") %>%
  group_by(county, rep_q, age_grp) %>%
  count(name = 'tot_bookings')

writeData(out, sheet = "5 Tot qtly bookings by age", x = q5_age)


addWorksheet(out, "5 Tot qtly bookings by race")

q5_race <- rep_df %>%
  group_by(county, rep_q, race) %>%
  count(name = 'tot_bookings') 

writeData(out, sheet = "5 Tot qtly bookings by race", x = q5_race)

#Q6: Total assessments
addWorksheet(out, "6 Total Assessments")

q6 <- rep_df %>%
  mutate(aq = case_when(assessment_date < as.Date("2022-01-01") ~ "FY1 Q1-2",
                           assessment_date < as.Date("2022-04-01") ~ "FY1 Q3",
                           assessment_date < as.Date("2022-07-01") ~ "FY1 Q4",
                           assessment_date < as.Date("2022-10-01") ~ "FY2 Q1",
                           assessment_date < as.Date("2023-01-01") ~ "FY2 Q2",
                           assessment_date < as.Date("2023-04-01") ~ "FY2 Q3",
                           assessment_date < as.Date("2023-07-01") ~ "FY2 Q4",
                           assessment_date < as.Date("2023-10-01") ~ "FY3 Q1",
                           assessment_date < as.Date("2024-01-01") ~ "FY3 Q2",
                           assessment_date < as.Date("2024-04-01") ~ "FY3 Q3")) %>%
  mutate(scored_assessment = if_else(is.na(risk_score_raw) & is.na(score_new_criminal_activity) & is.na(generic_tool_total_score_raw), 0,1)) %>%
  filter(is_booking_assessed == "Yes" & scored_assessment == 1) %>%
  group_by(county, aq) %>%
  count()

writeData(out, sheet = "6 Total Assessments", x = q6)

#Q7: Total monitored
addWorksheet(out, "7 Total Monitored")

q7 <- rep_df %>%
  filter(release_type == "Pretrial Supervision" | monitoring_level_grouped %in% c("Lowest Levels", "Medium Levels", "Highest Levels")) %>%
  mutate(rq = case_when(release_date < as.Date("2022-01-01") ~ "FY1 Q1-2",
                           release_date < as.Date("2022-04-01") ~ "FY1 Q3",
                           release_date < as.Date("2022-07-01") ~ "FY1 Q4",
                           release_date < as.Date("2022-10-01") ~ "FY2 Q1",
                           release_date < as.Date("2023-01-01") ~ "FY2 Q2",
                           release_date < as.Date("2023-04-01") ~ "FY2 Q3",
                           release_date < as.Date("2023-07-01") ~ "FY2 Q4",
                           release_date < as.Date("2023-10-01") ~ "FY3 Q1",
                           release_date < as.Date("2024-01-01") ~ "FY3 Q2",
                           release_date < as.Date("2024-04-01") ~ "FY3 Q3")) %>%
  group_by(county, rep_q) %>%
  count()

writeData(out, sheet = "7 Total Monitored", x = q7)

#Q7a: Total EM
addWorksheet(out, "7a Total EM")

q7a <- rep_df %>%
  mutate(rq = case_when(release_date < as.Date("2022-01-01") ~ "FY1 Q1-2",
                           release_date < as.Date("2022-04-01") ~ "FY1 Q3",
                           release_date < as.Date("2022-07-01") ~ "FY1 Q4",
                           release_date < as.Date("2022-10-01") ~ "FY2 Q1",
                           release_date < as.Date("2023-01-01") ~ "FY2 Q2",
                           release_date < as.Date("2023-04-01") ~ "FY2 Q3",
                           release_date < as.Date("2023-07-01") ~ "FY2 Q4",
                           release_date < as.Date("2023-10-01") ~ "FY3 Q1",
                           release_date < as.Date("2024-01-01") ~ "FY3 Q2",
                           release_date < as.Date("2024-04-01") ~ "FY3 Q3")) %>%
  group_by(county, rep_q) %>%
  summarise(em_flag = sum(condition_em_flag, na.rm = T), em_monitored = sum(if_else(condition_em_flag == 1 & (release_type == "Pretrial Supervision" | monitoring_level_grouped %in% c("Lowest Levels", "Medium Levels", "Highest Levels")), 1,0)))


writeData(out, sheet = "7a Total EM", x = q7a)

#Q7b: Total support
addWorksheet(out, "7b Total support")

q7b <- rep_df %>%
  mutate(pretrial_service_flag = case_when(other_pretrial_service == 1 ~ 1,
                                           toupper(other_pretrial_service) == "YES" ~ 1,
                                           other_pretrial_service == "Receives Other Pretrial Services" ~ 1,
                                           T ~ 0)) %>%
  mutate(rq = case_when(release_date < as.Date("2022-01-01") ~ "FY1 Q1-2",
                           release_date < as.Date("2022-04-01") ~ "FY1 Q3",
                           release_date < as.Date("2022-07-01") ~ "FY1 Q4",
                           release_date < as.Date("2022-10-01") ~ "FY2 Q1",
                           release_date < as.Date("2023-01-01") ~ "FY2 Q2",
                           release_date < as.Date("2023-04-01") ~ "FY2 Q3",
                           release_date < as.Date("2023-07-01") ~ "FY2 Q4",
                           release_date < as.Date("2023-10-01") ~ "FY3 Q1",
                           release_date < as.Date("2024-01-01") ~ "FY3 Q2",
                           release_date < as.Date("2024-04-01") ~ "FY3 Q3")) %>%
  group_by(county, rep_q) %>%
  summarise(support_flag = sum(if_else(transit_service_flag == 1 | pretrial_service_flag == 1, 1, 0)), support_monitored = sum(if_else((transit_service_flag == 1 | pretrial_service_flag == 1) & (release_type == "Pretrial Supervision" | monitoring_level_grouped %in% c("Lowest Levels", "Medium Levels", "Highest Levels")), 1,0)))

writeData(out, sheet = "7b Total support", x = q7b)



#Q7c: New monitoring cases
addWorksheet(out, "7c New Monitoring Cases")

q7c <- rep_df %>%
  filter(release_type == "Pretrial Supervision" | monitoring_level_grouped %in% c("Lowest Levels", "Medium Levels", "Highest Levels")) %>%
  mutate(rq = case_when(release_date < as.Date("2022-01-01") ~ "FY1 Q1-2",
                           release_date < as.Date("2022-04-01") ~ "FY1 Q3",
                           release_date < as.Date("2022-07-01") ~ "FY1 Q4",
                           release_date < as.Date("2022-10-01") ~ "FY2 Q1",
                           release_date < as.Date("2023-01-01") ~ "FY2 Q2",
                           release_date < as.Date("2023-04-01") ~ "FY2 Q3",
                           release_date < as.Date("2023-07-01") ~ "FY2 Q4",
                           release_date < as.Date("2023-10-01") ~ "FY3 Q1",
                           release_date < as.Date("2024-01-01") ~ "FY3 Q2",
                           release_date < as.Date("2024-04-01") ~ "FY3 Q3")) %>%
  group_by(county, rep_q) %>%
  count()

writeData(out, sheet = "7c New Monitoring Cases", x = q7c)


out
#saveWorkbook(out, "SB 129 pilot numbers for Deirdre 12.1.22.xlsx")
saveWorkbook(out, "SB 129 pilot numbers for Deirdre 3.3.22.xlsx")

rep_df %>%
  count(monitoring_level_grouped, release_type) %>%
  arrange(desc(n))
  select(contains("monitor"))
```

Something is wrong with Calaveras
```{r}
rep_df %>%
  filter(county == "Calaveras",
         is_booking_assessed == "Yes") %>%
  select(contains("risk"))
  

```

FTAs
```{r}
fta_county <- rep_df %>%
  mutate(scored_assessment = if_else(is.na(risk_score_raw) & is.na(score_new_criminal_activity) & is.na(generic_tool_total_score_raw), 0,1)) %>%
  filter(book_date < as.Date("2022-07-01"),
         is_released_pretrial == "Yes",
         is_booking_assessed == "Yes",
         scored_assessment == 1) %>%
  group_by(county) %>%
  summarise(total_assessed_released_pretrial = n(), ftas = sum(fta_county_or_doj), fta_rate = ftas/total_assessed_released_pretrial)

#write.csv(fta_county, file = "FTA numbers for Deirdre 1.23.23.csv")
write.csv(fta_county, file = "FTA numbers for Deirdre 3.2.23.csv")


```
# Court date reminder tables
```{r}
rep_df %>%
  group_by(county) %>%
  count(court_date_reminder_flag) %>%
  mutate(perc = round(100*n/sum(n), 1), N = sum(n)) %>%
  filter(court_date_reminder_flag == 1 | perc == 100) %>%
  mutate(perc = if_else(court_date_reminder_flag == 0 & perc == 100, 0, perc)) %>%
  select(county, perc, N) %>%
    distinct()
```
By quarter
```{r}

qdf <- rep_df %>%
  group_by(county, rep_q) %>%
  count(court_date_reminder_flag) %>%
  mutate(perc = round(100*n/sum(n), 1), N = sum(n)) %>%
  filter(court_date_reminder_flag == 1 & n > 10) %>%
  mutate(perc = if_else(court_date_reminder_flag == 0 & perc == 100, 0, perc)) %>%
  select(rep_q, county, perc, N) %>%
    distinct()

write.csv(qdf, file = "quarterly court date reminder percent of all bookings by county 3.3.23.csv")
```

Only matched bookings
```{r}
rep_df %>%
  filter(is_unmatched_booking == "No") %>%
  group_by(county) %>%
  count(court_date_reminder_flag) %>%
  mutate(perc = round(100*n/sum(n), 1), N = sum(n)) %>%
  filter(court_date_reminder_flag == 1 | perc == 100) %>%
  mutate(perc = if_else(court_date_reminder_flag == 0 & perc == 100, 0, perc)) %>%
  select(county, perc, N) %>%
    distinct()
```
Quarterly, matched bookings
```{r}
qdf <- rep_df %>%
  filter(is_unmatched_booking == "No") %>%
  group_by(county, rep_q) %>%
  count(court_date_reminder_flag) %>%
  mutate(perc = round(100*n/sum(n), 1), N = sum(n)) %>%
  filter(court_date_reminder_flag == 1 & n > 10) %>%
  mutate(perc = if_else(court_date_reminder_flag == 0 & perc == 100, 0, perc)) %>%
  select(rep_q, county, perc, N) %>%
    distinct()

write.csv(qdf, file = "quarterly court date reminder percent of bookings with case by county 3.3.23.csv")
```

Only matched booking with filing after booking
```{r}
rep_df %>%
  filter(is_unmatched_booking == "No",
         case_filed_date >= booking_date) %>%
  group_by(county) %>%
  count(court_date_reminder_flag) %>%
  mutate(perc = round(100*n/sum(n), 1), N = sum(n)) %>%
  filter(court_date_reminder_flag == 1 | perc == 100) %>%
  mutate(perc = if_else(court_date_reminder_flag == 0 & perc == 100, 0, perc)) %>%
  select(county, perc, N) %>%
    distinct()

# all counties, filing on or after booking
rep_df %>%
  filter(is_unmatched_booking == "No",
         case_filed_date >= booking_date) %>%
  count(court_date_reminder_flag) %>%
  mutate(perc = round(100*n/sum(n), 1), N = sum(n))
```


```{r}
# all counties, all bookings with cases, just 2022
rep_df %>%
  filter(is_unmatched_booking == "No",
         booking_date >= as.Date("2022-1-1"),
         booking_date < as.Date("2023-1-1")) %>%
  count(court_date_reminder_flag) %>%
  mutate(perc = round(100*n/sum(n), 1), N = sum(n))

```


```{r}
full_df %>%
  filter(is_unmatched_booking == "No") %>%
  group_by(county) %>%
  count(court_date_reminder_flag) %>%
  mutate(perc = round(100*n/sum(n), 1), N = sum(n)) %>%
  filter(court_date_reminder_flag == 1 | perc == 100) %>%
  mutate(perc = if_else(court_date_reminder_flag == 0 & perc == 100, 0, perc)) %>%
  select(county, perc, N) %>%
    distinct() %>%
  ungroup() %>%
  summarise(tot = sum(N), reminders = sum(N*perc/100))

```

