---
title: "SB 36 Charts and Tables_JW"
output:
  html_document:
    df_print: paged
---

# library
```{r}
library(gt)
library(readxl)
library(scales)
library(tidyverse)
```

# import data
```{r}
files <- list.files("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 tables 2023", pattern = "^[0-9]", full.names = T)

df_list <- lapply(files, function(x) {
  lapply(excel_sheets(x), function(i) {
    read_excel(x, sheet = i)
  })
}) %>%
  unlist(recursive = F)

df_names <- lapply(files, function(x) {
  lapply(excel_sheets(x), function(i) {
    df_name <- sub(".*\\/", "", x)
    df_name <- gsub("-", "", df_name)
    df_name <- if_else(!is.na(as.numeric(substr(gsub("^\\S* ", "", gsub(".xlsx", "", df_name)), 1, 1))), paste0("df_", gsub("^\\S* ", "", gsub(".xlsx", "", df_name))), gsub(" ", "_", paste(gsub("^\\S* ", "", gsub(".xlsx", "", df_name)), gsub(" .*", "", gsub(".xlsx", "", df_name)))))
    df_name <- if_else(i == "Sheet 1", df_name, paste0(df_name, "_", i))
  })
}) %>%
  unlist(recursive = F)

names(df_list) <- df_names
list2env(df_list, .GlobalEnv)

# load("df.RData")
# load("join_df.RData")
# load("eval_df.RData")
```

# Table 1a
```{r}
Offense_Type_fresh_2A %>%
  filter(`Arrest Charge Level` == "Misdemeanor") %>%
  select(-`Arrest Charge Level`) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All New Arrest Bookings (Misdemeanor)", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T1a.png")
```

# Table 1b
```{r}
Offense_Type_fresh_2A %>%
  filter(`Arrest Charge Level` == "Felony") %>%
  select(-`Arrest Charge Level`) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All New Arrest Bookings (Felony)", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T1b.png")
```

# Table 1c
```{r}
Offense_Type_LA_2A %>%
  select(-County) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All Bookings", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T1c.png")
```

# Table 2a
```{r}
Gender_fresh_2A %>%
  filter(Gender == "Female") %>%
  select(-Gender) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All New Arrest Bookings (Female)", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T2a.png")
```

# Table 2b
```{r}
Gender_fresh_2A %>%
  filter(Gender == "Male") %>%
  select(-Gender) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All New Arrest Bookings (Male)", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T2b.png")
```

# Table 2c
```{r}
Gender_LA_2A %>%
  select(-County) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All Bookings", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T2c.png")
```

# Table 3a
```{r}
Race_fresh_2A %>%
  filter(Race == "Black") %>%
  select(-Race) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All New Arrest Bookings (Black Defendants)", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T3a.png")
```

# Table 3b
```{r}
Race_fresh_2A %>%
  filter(Race == "Hispanic") %>%
  select(-Race) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All New Arrest Bookings (Hispanic Defendants)", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T3b.png")
```

# Table 3c
```{r}
Race_fresh_2A %>%
  filter(Race == "White") %>%
  select(-Race) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All New Arrest Bookings (White Defendants)", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T3c.png")
```

# Table 3d
```{r}
Race_LA_2A %>%
  select(-County) %>%
  gt() %>%
  fmt_number(columns = Total, decimals = 0, sep_mark = ",") %>%
  fmt_percent(columns = -Total, decimals = 0) %>%
  cols_label_with(fn = ~ gsub(" within 2 court days| after 2 days| type", "", .)) %>%
  tab_spanner("All Bookings", 1:2) %>%
  tab_spanner("POST-RESOLUTION", 3:4) %>%
  tab_spanner("PRETRIAL", 5:8) %>%
  tab_spanner("UNKNOWN", 9) %>%
  tab_spanner("TOTAL", 10) %>%
  tab_spanner("PRETRIAL ", 11:14) %>%
  tab_spanner("Released Within 2 Court Days", 3:10) %>%
  tab_spanner("Released After 2 Court Days", 11:14) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T3d.png")
```

# Table 4
```{r}
df_2B %>%
  filter(`Offense Type` %in% c("Felony", "Misdemeanor")) %>%
  select(-c(Total, Sort)) %>%
  pivot_wider(names_from = `Release Type/Risk Level`, values_from = `Court Appearance Rate`) %>%
  select(-County) %>%
  rename(County = `Offense Type`) %>%
  gt() %>%
  sub_missing() %>%
  tab_row_group(md("**Ventura**"), 19:20) %>%
  tab_row_group(md("**Tulare**"), 17:18) %>%
  tab_row_group(md("**Sonoma**"), 15:16) %>%
  tab_row_group(md("**San Mateo**"), 13:14) %>%
  tab_row_group(md("**San Joaquin**"), 11:12) %>%
  tab_row_group(md("**Sacramento**"), 9:10) %>%
  tab_row_group(md("**Los Angeles**"), 7:8) %>%
  tab_row_group(md("**Alameda**"), 5:6) %>%
  tab_row_group(md("**Small/Medium Counties**"), 3:4) %>%
  tab_row_group(md("**Small Counties**"), 1:2) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T4.png")
```

# Table 5
```{r}
df_2C %>%
  filter(`Offense Type` %in% c("Felony", "Misdemeanor")) %>%
  select(-c(Total, Sort)) %>%
  pivot_wider(names_from = `Release Type/Risk Level`, values_from = `No New Charge Rate`) %>%
  select(-County) %>%
  rename(County = `Offense Type`) %>%
  gt() %>%
  sub_missing() %>%
  tab_row_group(md("**Ventura**"), 19:20) %>%
  tab_row_group(md("**Tulare**"), 17:18) %>%
  tab_row_group(md("**Sonoma**"), 15:16) %>%
  tab_row_group(md("**San Mateo**"), 13:14) %>%
  tab_row_group(md("**San Joaquin**"), 11:12) %>%
  tab_row_group(md("**Sacramento**"), 9:10) %>%
  tab_row_group(md("**Los Angeles**"), 7:8) %>%
  tab_row_group(md("**Alameda**"), 5:6) %>%
  tab_row_group(md("**Small/Medium Counties**"), 3:4) %>%
  tab_row_group(md("**Small Counties**"), 1:2) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T5.png")
```

# Table 6
```{r}
Age_2D %>%
  pivot_wider(names_from = age, values_from = n) %>%
  bind_rows(summarise(., across(where(is.character), ~ "Total"),
                      across(where(is.numeric), ~ sum(., na.rm = T)))) %>%
  relocate(Total, .after = last_col()) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  cols_label(Total = md("**Total**")) %>%
  tab_style(cell_text(weight = "bold"), list(cells_body(Total), cells_body(rows = County == "Total"))) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T6.png")
```

# Table 7
```{r}
Gender_2D %>%
  pivot_wider(names_from = sex, values_from = n) %>%
  bind_rows(summarise(., across(where(is.character), ~ "Total"),
                      across(where(is.numeric), ~ sum(., na.rm = T)))) %>%
  relocate(Total, .after = last_col()) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  cols_label(Total = md("**Total**")) %>%
  tab_style(cell_text(weight = "bold"), list(cells_body(Total), cells_body(rows = County == "Total"))) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T7.png")
```

# Table 8
```{r}
Race_2D %>%
  select(-race_sort) %>%
  mutate(race = fct_relevel(race, "Other/Unknown", after = 4)) %>%
  arrange(County, race) %>%
  pivot_wider(names_from = race, values_from = n) %>%
  bind_rows(summarise(., across(where(is.character), ~ "Total"),
                      across(where(is.numeric), ~ sum(., na.rm = T)))) %>%
  relocate(Total, .after = last_col()) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  sub_missing() %>%
  cols_label(Total = md("**Total**")) %>%
  tab_style(cell_text(weight = "bold"), list(cells_body(Total), cells_body(rows = County == "Total"))) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T8.png")
```

# Table 9
```{r}
Risk_Level_2E %>%
  select(-risk_level_sort) %>%
  pivot_wider(names_from = risk_level, values_from = n) %>%
  bind_rows(summarise(., across(where(is.character), ~ "Total"),
                      across(where(is.numeric), ~ sum(., na.rm = T)))) %>%
  mutate(Total = rowSums(across(where(is.numeric)), na.rm = T)) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  cols_label(Total = md("**Total**")) %>%
  tab_style(cell_text(weight = "bold"), list(cells_body(Total), cells_body(rows = County == "Total"))) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T9.png")
```

# Table 10a (Pre-Arraignment)
```{r}
Release_Decision_PreArraignment_2E %>%
  group_by(County, release_decision_prearraignment) %>%
  mutate(n = sum(n, na.rm = T)) %>%
  ungroup() %>%
  distinct() %>%
  pivot_wider(names_from = release_decision_prearraignment, values_from = n) %>%
  bind_rows(summarise(., across(where(is.character), ~ "Total"),
                      across(where(is.numeric), ~ sum(., na.rm = T)))) %>%
  mutate(Total = rowSums(across(where(is.numeric)), na.rm = T)) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  sub_missing() %>%
  cols_label(Total = md("**Total**")) %>%
  tab_style(cell_text(weight = "bold"), list(cells_body(Total), cells_body(rows = County == "Total"))) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T10a(Pre-Arraignment).png")
```

# Table 10a (Arraignment)
```{r}
Release_Decision_Arraignment_2E %>%
  filter(County != "Los Angeles") %>%
  group_by(County, release_decision_arraignment) %>%
  mutate(n = sum(n, na.rm = T)) %>%
  ungroup() %>%
  distinct() %>%
  pivot_wider(names_from = release_decision_arraignment, values_from = n) %>%
  bind_rows(summarise(., across(where(is.character), ~ "Total"),
                      across(where(is.numeric), ~ sum(., na.rm = T)))) %>%
  mutate(Total = rowSums(across(where(is.numeric)), na.rm = T)) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  sub_missing() %>%
  cols_label(Total = md("**Total**")) %>%
  tab_style(cell_text(weight = "bold"), list(cells_body(Total), cells_body(rows = County == "Total"))) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T10a(Arraignment).png")
```

# Table 10b
```{r}
Release_Decision_LA_only_2E %>%
  group_by(release_decision_prearraignment) %>%
  mutate(n = sum(n, na.rm = T)) %>%
  ungroup() %>%
  distinct() %>%
  pivot_wider(names_from = release_decision_prearraignment, values_from = n) %>%
  mutate(Total = rowSums(across(where(is.numeric)), na.rm = T)) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  cols_label(Total = md("**Total**")) %>%
  tab_style(cell_text(weight = "bold"), list(cells_body(Total))) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T10b.png")
```

# Table 11
```{r}
Charge_Level_2E %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  pivot_wider(names_from = arrest_charge_level, values_from = n) %>%
  bind_rows(summarise(., across(where(is.character), ~ "Total"),
                      across(where(is.numeric), ~ sum(., na.rm = T)))) %>%
  mutate(Total = rowSums(across(where(is.numeric)), na.rm = T)) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  cols_label(Total = md("**Total**")) %>%
  tab_style(cell_text(weight = "bold"), list(cells_body(Total), cells_body(rows = County == "Total"))) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T11.png")
```

# Table 12
```{r}
Supervision_Level_2F %>%
  select(contains("Count"), Total) %>%
  rename_with(~ gsub("Count_", "", .)) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  cols_label(Total = md("**Total**")) %>%
  tab_style(cell_text(weight = "bold"), list(cells_body(Total), cells_body(rows = County == "Total"))) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T12.png")
```

# Table 13
```{r}
Supervision_Level_2F %>%
  select(County, contains("Percent"), -Percent_Other) %>%
  rename_with(~ gsub("Percent_", "", .)) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  tab_style(cell_text(weight = "bold"), cells_body(rows = County == "Total")) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T13.png")
```

# Table 14
```{r}
Supervision_Level_2G %>%
  select(-County) %>%
  rename(County = monitor_level,
         FTAs = FTA_Count,
         `New Arrests` = New_Arrest_Count) %>%
  gt() %>%
  fmt_number(decimals = 0, sep_mark = ",") %>%
  tab_row_group(md("**Tulare**"), 22:24) %>%
  tab_row_group(md("**Sonoma**"), 19:21) %>%
  tab_row_group(md("**San Mateo**"), 16:18) %>%
  tab_row_group(md("**San Joaquin**"), 13:15) %>%
  tab_row_group(md("**Sacramento**"), 10:12) %>%
  tab_row_group(md("**Alameda**"), 7:9) %>%
  tab_row_group(md("**Small/Medium Counties**"), 4:6) %>%
  tab_row_group(md("**Small Counties**"), 1:3) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T14.png")
```

# Table 15
```{r}
Supervision_Level_Percent_2G %>%
  select(monitor_level, contains("percent")) %>%
  rename(County = monitor_level,
         FTAs = FTA_percent,
         `New Arrests` = New_Arrest_Percent) %>%
  gt() %>%
  fmt_percent(columns = where(is.numeric), decimals = 0) %>%
  sub_missing() %>%
  tab_row_group(md("**Tulare**"), 22:24) %>%
  tab_row_group(md("**Sonoma**"), 19:21) %>%
  tab_row_group(md("**San Mateo**"), 16:18) %>%
  tab_row_group(md("**San Joaquin**"), 13:15) %>%
  tab_row_group(md("**Sacramento**"), 10:12) %>%
  tab_row_group(md("**Alameda**"), 7:9) %>%
  tab_row_group(md("**Small/Medium Counties**"), 4:6) %>%
  tab_row_group(md("**Small Counties**"), 1:3) %>%
  gtsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/T15.png")
```

# Figure 1
```{r}
PSA_FTA_3A %>%
  mutate(Total = formatC(as.numeric(Total), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100,
         h = if_else(psa_fta_risk_score == "Total", T, F)) %>%
  ggplot(aes(x = psa_fta_risk_score, y = p, fill = h)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5) +
  geom_label(aes(y = 0.1, label = Total)) +
  theme(legend.position = "none")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F1.png")
```

# Figure 2
```{r}
PSA_NCA_3A %>%
  mutate(Total = formatC(as.numeric(Total), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100,
         h = if_else(psa_nca_risk_score == "Total", T, F)) %>%
  ggplot(aes(x = psa_nca_risk_score, y = p, fill = h)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5) +
  geom_label(aes(y = 0.1, label = Total)) +
  theme(legend.position = "none")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F2.png")
```

# Figure 3
```{r}
PSA_FTA_3C_Gender %>%
  filter(!grepl("Unknown", sex)) %>%
  group_by(psa_fta_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = psa_fta_risk_score, y = p, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F3.png")
```

# Figure 4
```{r}
`PSA_FTA_3C_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  group_by(psa_fta_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = psa_fta_risk_score, y = p, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F4.png")
```

# Figure 5
```{r}
PSA_FTA_3C_Race %>%
  filter(race != "Other/Unknown") %>%
  group_by(psa_fta_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = psa_fta_risk_score, y = p, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  geom_label(aes(y = 0.1, label = t), show.legend = F) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F5.png")
```

# Figure 6
```{r}
PSA_NCA_3C_Gender %>%
  filter(!grepl("Unknown", sex)) %>%
  group_by(psa_nca_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = psa_nca_risk_score, y = p, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F6.png")
```

# Figure 7
```{r}
`PSA_NCA_3C_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  group_by(psa_nca_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = psa_nca_risk_score, y = p, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F7.png")
```

# Figure 8
```{r}
PSA_NCA_3C_Race %>%
  filter(race != "Other/Unknown") %>%
  group_by(psa_nca_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = psa_nca_risk_score, y = p, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  geom_label(aes(y = 0.1, label = t), show.legend = F) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F8.png")
```

# Figure 9
```{r}
PSA_NVCA_3C_Gender %>%
  filter(!grepl("Unknown", sex)) %>%
  group_by(psa_nvca_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Violent Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = psa_nvca_risk_score, y = p, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Violent Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F9.png")
```

# Figure 10
```{r}
`PSA_NVCA_3C_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  group_by(psa_nvca_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Violent Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = psa_nvca_risk_score, y = p, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Violent Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F10.png")
```

# Figure 11
```{r}
PSA_NVCA_3C_Race %>%
  filter(race != "Other/Unknown") %>%
  group_by(psa_nvca_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Violent Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = psa_nvca_risk_score, y = p, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Violent Charge Rate`), vjust = -0.5, position = position_dodge(width = 0.9), size = 3.5) +
  geom_label(aes(y = 0.1, label = t), show.legend = F) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F11.png")
```

# Figure 12
```{r}
PSA_FTA_3B_Gender %>%
  filter(sex != "Other/Unknown") %>%
  mutate(psa_fta_risk_score = as.character(psa_fta_risk_score)) %>%
  ggplot(aes(x = psa_fta_risk_score, y = n, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F12.png")
```

# Figure 13
```{r}
`PSA_FTA_3B_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(psa_fta_risk_score = as.character(psa_fta_risk_score)) %>%
  ggplot(aes(x = psa_fta_risk_score, y = n, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F13.png")
```

# Figure 14
```{r}
PSA_FTA_3B_Race %>%
  filter(race != "Other/Unknown") %>%
  mutate(psa_fta_risk_score = as.character(psa_fta_risk_score)) %>%
  ggplot(aes(x = psa_fta_risk_score, y = n, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F14.png")
```

# Figure 15 Arraignment
```{r}
`PSA_FTA_3B_Release Arraignment` %>%
  mutate(psa_fta_risk_score = as.character(psa_fta_risk_score)) %>%
  ggplot(aes(x = psa_fta_risk_score, y = n, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F15 (Arraignment).png")
```
# Figure 15 Prearraignment
```{r}
`PSA_FTA_3B_Release Prearraignment` %>%
  mutate(psa_fta_risk_score = as.character(psa_fta_risk_score)) %>%
  ggplot(aes(x = psa_fta_risk_score, y = n, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F15 (Prerraignment).png")
```
# Figure 16
```{r}
PSA_NCA_3B_Gender %>%
  filter(sex != "Other/Unknown") %>%
  mutate(psa_nca_risk_score = as.character(psa_nca_risk_score)) %>%
  ggplot(aes(x = psa_nca_risk_score, y = n, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F16.png")
```

# Figure 17
```{r}
`PSA_NCA_3B_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(psa_nca_risk_score = as.character(psa_nca_risk_score)) %>%
  ggplot(aes(x = psa_nca_risk_score, y = n, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F17.png")
```

# Figure 18
```{r}
PSA_NCA_3B_Race %>%
  filter(race != "Other/Unknown") %>%
  mutate(psa_nca_risk_score = as.character(psa_nca_risk_score)) %>%
  ggplot(aes(x = psa_nca_risk_score, y = n, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F18.png")
```

# Figure 19 Arraignment
```{r}
`PSA_NCA_3B_Release Arraignment` %>%
  mutate(psa_nca_risk_score = as.character(psa_nca_risk_score)) %>%
  ggplot(aes(x = psa_nca_risk_score, y = n, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F19 (Arraignment).png")
```
# Figure 19 Prearraignment
```{r}
`PSA_NCA_3B_Release Prearraignment` %>%
  mutate(psa_nca_risk_score = as.character(psa_nca_risk_score)) %>%
  ggplot(aes(x = psa_nca_risk_score, y = n, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F19 (Prearraignment).png")
```
# Figure 20
```{r}
PSA_NVCA_3B_Gender %>%
  filter(sex != "Other/Unknown") %>%
  mutate(psa_nvca_risk_score = as.character(psa_nvca_risk_score)) %>%
  ggplot(aes(x = psa_nvca_risk_score, y = n, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F20.png")
```

# Figure 21
```{r}
`PSA_NVCA_3B_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(psa_nvca_risk_score = as.character(psa_nvca_risk_score)) %>%
  ggplot(aes(x = psa_nvca_risk_score, y = n, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F21.png")
```

# Figure 22
```{r}
PSA_NVCA_3B_Race %>%
  filter(race != "Other/Unknown") %>%
  mutate(psa_nvca_risk_score = as.character(psa_nvca_risk_score)) %>%
  ggplot(aes(x = psa_nvca_risk_score, y = n, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(width = 0.9), size = 3.5) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F22.png")
```

# Figure 23 Arraignment
```{r}
`PSA_NVCA_3B_Release Arraignment` %>%
  mutate(psa_nvca_risk_score = as.character(psa_nvca_risk_score)) %>%
  ggplot(aes(x = psa_nvca_risk_score, y = n, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F23 (Arraignment).png")
```
# Figure 23 Prearraignment
```{r}
`PSA_NVCA_3B_Release Prearraignment` %>%
  mutate(psa_nvca_risk_score = as.character(psa_nvca_risk_score)) %>%
  ggplot(aes(x = psa_nvca_risk_score, y = n, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(n), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F23 (Prearraignment).png")
```
# Figure 24
```{r}
Oras_categories_3A %>%
  mutate(Total = formatC(as.numeric(Total), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100,
         h = if_else(oras_risk_score == "Total", T, F)) %>%
  ggplot(aes(x = oras_risk_score, y = p, fill = h)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5) +
  geom_label(aes(y = 0.1, label = Total)) +
  theme(legend.position = "none")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F24.png")
```

# Figure 25
```{r}
Oras_categories_3A %>%
  mutate(Total = formatC(as.numeric(Total), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100,
         h = if_else(oras_risk_score == "Total", T, F)) %>%
  ggplot(aes(x = oras_risk_score, y = p, fill = h)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5) +
  geom_label(aes(y = 0.1, label = Total)) +
  theme(legend.position = "none")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F25.png")
```

# Figure 26
```{r}
Oras_categories_3C_Gender %>%
  filter(sex != "Undefined") %>%
  group_by(oras_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = oras_risk_score, y = p, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F26.png")
```

# Figure 27
```{r}
`Oras_categories_3C_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  group_by(oras_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = oras_risk_score, y = p, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F27.png")
```

# Figure 28
```{r}
Oras_categories_3C_Race %>%
  filter(race != "Other/Unknown") %>%
  group_by(oras_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = oras_risk_score, y = p, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  geom_label(aes(y = 0.1, label = t), show.legend = F) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F28.png")
```

# Figure 29
```{r}
Oras_categories_3C_Gender %>%
  filter(sex != "Undefined") %>%
  group_by(oras_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = oras_risk_score, y = p, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F29.png")
```

# Figure 30
```{r}
`Oras_categories_3C_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  group_by(oras_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = oras_risk_score, y = p, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F30.png")
```

# Figure 31
```{r}
Oras_categories_3C_Race %>%
  filter(race != "Other/Unknown") %>%
  group_by(oras_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = oras_risk_score, y = p, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  geom_label(aes(y = 0.1, label = t), show.legend = F) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F31.png")
```

# Figure 32
```{r}
ORAS_3B_Gender %>%
  filter(sex != "Other/Unknown") %>%
  group_by(sex, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F32.png")
```

# Figure 33
```{r}
`ORAS_3B_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  group_by(arrest_charge_level, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F33.png")
```

# Figure 34
```{r}
ORAS_3B_Race %>%
  filter(race != "Other/Unknown") %>%
  group_by(race, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9)) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F34.png")
```

# Figure 35 Arraignment
```{r}
`ORAS_3B_Release Arraignment` %>%
  group_by(release_decision, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F35 (Arraignment).png")
```
# Figure 35 Prearraignment
```{r}
`ORAS_3B_Release Prearraignment` %>%
  group_by(release_decision, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F35 (Prearraignment).png")
```

# Figure 36
```{r}
Vprai_categories_3A %>%
  mutate(vprai_risk_score = fct_relevel(vprai_risk_score, "Scores 0-1", after = 0),
         Total = formatC(as.numeric(Total), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100,
         h = if_else(vprai_risk_score == "Total", T, F)) %>%
  ggplot(aes(x = vprai_risk_score, y = p, fill = h)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5) +
  geom_label(aes(y = 0.1, label = Total)) +
  theme(legend.position = "none")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F36.png")
```

# Figure 37
```{r}
Vprai_categories_3A %>%
  mutate(vprai_risk_score = fct_relevel(vprai_risk_score, "Scores 0-1", after = 0),
         Total = formatC(as.numeric(Total), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100,
         h = if_else(vprai_risk_score == "Total", T, F)) %>%
  ggplot(aes(x = vprai_risk_score, y = p, fill = h)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5) +
  geom_label(aes(y = 0.1, label = Total)) +
  theme(legend.position = "none")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F37.png")
```

# Figure 38
```{r}
VPRAI_categories_3C_Gender %>%
  mutate(vprai_risk_score = fct_relevel(vprai_risk_score, "Scores 0-1", after = 0)) %>%
  group_by(vprai_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprai_risk_score, y = p, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F38.png")
```

# Figure 39
```{r}
`VPRAI_categories_3C_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(vprai_risk_score = fct_relevel(vprai_risk_score, "Scores 0-1", after = 0)) %>%
  group_by(vprai_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprai_risk_score, y = p, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F39.png")
```

# Figure 40
```{r}
VPRAI_categories_3C_Race %>%
  filter(race != "Other/Unknown") %>%
  mutate(vprai_risk_score = fct_relevel(vprai_risk_score, "Scores 0-1", after = 0)) %>%
  group_by(vprai_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprai_risk_score, y = p, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  geom_label(aes(y = 0.1, label = t), show.legend = F) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F40.png")
```

# Figure 41
```{r}
VPRAI_categories_3C_Gender %>%
  mutate(vprai_risk_score = fct_relevel(vprai_risk_score, "Scores 0-1", after = 0)) %>%
  group_by(vprai_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprai_risk_score, y = p, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F41.png")
```

# Figure 42
```{r}
`VPRAI_categories_3C_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(vprai_risk_score = fct_relevel(vprai_risk_score, "Scores 0-1", after = 0)) %>%
  group_by(vprai_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprai_risk_score, y = p, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F42.png")
```

# Figure 43
```{r}
VPRAI_categories_3C_Race %>%
  filter(race != "Other/Unknown") %>%
  mutate(vprai_risk_score = fct_relevel(vprai_risk_score, "Scores 0-1", after = 0)) %>%
  group_by(vprai_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprai_risk_score, y = p, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  geom_label(aes(y = 0.1, label = t), show.legend = F) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F43.png")
```

# Figure 44
```{r}
VPRAI_3B_Gender %>%
  filter(sex != "Other/Unknown") %>%
  mutate(risk_category = fct_relevel(risk_category, "Scores 0-1", after = 0)) %>%
  group_by(sex, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F44.png")
```

# Figure 45
```{r}
`VPRAI_3B_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(risk_category = fct_relevel(risk_category, "Scores 0-1", after = 0)) %>%
  group_by(arrest_charge_level, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F45.png")
```

# Figure 46
```{r}
VPRAI_3B_Race %>%
  filter(race != "Other/Unknown") %>%
  mutate(risk_category = fct_relevel(risk_category, "Scores 0-1", after = 0)) %>%
  group_by(race, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(width = 0.9), size = 3.5) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F46.png")
```

# Figure 47 Arraignment
```{r}
`VPRAI_3B_Release Arraignment` %>%
  mutate(risk_category = fct_relevel(risk_category, "Scores 0-1", after = 0)) %>%
  group_by(release_decision, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F47 (Arraignment).png")
```
# Figure 47 Prearraignment
```{r}
`VPRAI_3B_Release Prearraignment` %>%
  mutate(risk_category = fct_relevel(risk_category, "Scores 0-1", after = 0)) %>%
  group_by(release_decision, risk_category) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = risk_category, y = t, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F47 (Prearraignment).png")
```
# Figure 48
```{r}
VpraiR_categories_3A %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5),
         Total = formatC(as.numeric(Total), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100,
         h = if_else(vprair_risk_score == "Total", T, F)) %>%
  ggplot(aes(x = vprair_risk_score, y = p, fill = h)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5) +
  geom_label(aes(y = 0.1, label = Total)) +
  theme(legend.position = "none")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F48.png")
```

# Figure 49
```{r}
VpraiR_categories_3A %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5),
         Total = formatC(as.numeric(Total), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100,
         h = if_else(vprair_risk_score == "Total", T, F)) %>%
  ggplot(aes(x = vprair_risk_score, y = p, fill = h)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5) +
  geom_label(aes(y = 0.1, label = Total)) +
  theme(legend.position = "none")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F49.png")
```

# Figure 50
```{r}
VPRAIR_categories_3C_Gender %>%
  filter(sex %in% c("Female", "Male")) %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(vprair_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = p, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F50.png")
```

# Figure 51
```{r}
`VPRAIR_categories_3C_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(vprair_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = p, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F51.png")
```

# Figure 52
```{r}
VPRAIR_categories_3C_Race %>%
  filter(race != "Other/Unknown") %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(vprair_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non FTA Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = p, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non FTA Rate`), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  geom_label(aes(y = 0.1, label = t), show.legend = F) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F52.png")
```

# Figure 53
```{r}
VPRAIR_categories_3C_Gender %>%
  filter(sex %in% c("Female", "Male")) %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(vprair_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = p, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F53.png")
```

# Figure 54
```{r}
`VPRAIR_categories_3C_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(vprair_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = p, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(0.9)) +
  geom_label(aes(y = 0.1, label = t), show.legend = F)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F54.png")
```

# Figure 55
```{r}
VPRAIR_categories_3C_Race %>%
  filter(race != "Other/Unknown") %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(vprair_risk_score) %>%
  mutate(t = formatC(sum(as.numeric(Total), na.rm = T), format = "d", big.mark = ","),
         p = as.numeric(gsub(" %", "", `Non New Charge Rate`)) / 100) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = p, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = `Non New Charge Rate`), vjust = -0.5, position = position_dodge(width = 0.9), size = 2.5) +
  geom_label(aes(y = 0.1, label = t), show.legend = F) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F55.png")
```

# Figure 56
```{r}
VPRAIR_3B_Gender %>%
  filter(sex != "Other/Unknown") %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(sex, vprair_risk_score) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = t, fill = sex)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F56.png")
```

# Figure 57
```{r}
`VPRAIR_3B_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(arrest_charge_level, vprair_risk_score) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = t, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F57.png")
```

# Figure 58
```{r}
VPRAIR_3B_Race %>%
  filter(race != "Other/Unknown") %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(race, vprair_risk_score) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = t, fill = race)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(width = 0.9), size = 2) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F58.png")
```

# Figure 59 Arraignment
```{r}
`VPRAIR_3B_Release Arraignment` %>%
  filter(release_decision != "Other") %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(release_decision, vprair_risk_score) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = t, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F59 (Arraignment).png")
```
# Figure 59 Prearraignment
```{r}
`VPRAIR_3B_Release Prearraignment` %>%
  filter(release_decision != "Other") %>%
  mutate(vprair_risk_score = fct_relevel(vprair_risk_score, "Scores 11-14", after = 5)) %>%
  group_by(release_decision, vprair_risk_score) %>%
  mutate(t = sum(n, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = vprair_risk_score, y = t, fill = release_decision)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = comma) +
  geom_text(aes(label = formatC(as.numeric(t), format = "d", big.mark = ",")), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F59 (Prearraignment).png")
```
# Figure 60
```{r}
VPRAIO_3B_Gender %>%
  mutate(vpraio_risk_score = as.character(vpraio_risk_score)) %>%
  ggplot(aes(x = vpraio_risk_score, y = n, fill = sex)) +
  geom_col()+
  geom_text(aes(label = n), vjust = -0.5)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F60.png")
```

# Figure 61
```{r}
`VPRAIO_3B_Offense Type` %>%
  filter(arrest_charge_level %in% c("Felony", "Misdemeanor")) %>%
  mutate(vpraio_risk_score = as.character(vpraio_risk_score)) %>%
  ggplot(aes(x = vpraio_risk_score, y = n, fill = arrest_charge_level)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = n), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F61.png")
```

# Figure 62
```{r}
VPRAIO_3B_Race %>%
  mutate(vpraio_risk_score = as.character(vpraio_risk_score)) %>%
  ggplot(aes(x = vpraio_risk_score, y = n, fill = race)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = n), vjust = -0.5, position = position_dodge(0.9)) +
  theme(legend.position = "top")

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F62.png")
```

# Figure 63 Arraignment
```{r}
`VPRAIO_3B_Release Arraignment` %>%
  mutate(vpraio_risk_score = as.character(vpraio_risk_score)) %>%
  ggplot(aes(x = vpraio_risk_score, y = n, fill = release_decision)) +
  geom_col() +
  geom_text(aes(label = n), vjust = -0.5)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F63 (Arraignment).png")
```
# Figure 63 Prearraignment
```{r}
`VPRAIO_3B_Release Prearraignment` %>%
  mutate(vpraio_risk_score = as.character(vpraio_risk_score)) %>%
  ggplot(aes(x = vpraio_risk_score, y = n, fill = release_decision)) +
  geom_col() +
  geom_text(aes(label = n), vjust = -0.5)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F63 (Prearraignment).png")
```
# Figure 64
```{r}
df_3D_Overrides %>%
  mutate(p = paste0(round(override_percent * 100), "%")) %>%
  ggplot(aes(x = tool_name, y = override_percent)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = p), vjust = -0.5)

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F64.png")
```

# Figure 65
```{r}
df_3D_Supplementary %>%
  mutate(release = case_when(
    release_recommendation == "Deny Release" & release_decision == "Deny Release" ~ "Detain Recommendation, Program Release Denied",
    release_recommendation == "Deny Release" & release_decision == "Release" ~ "Detain Recommendation, Program Release Granted",
    release_recommendation == "Release" & release_decision == "Deny Release" ~ "Release Recommendation, Program Release Denied",
    release_recommendation == "Release" & release_decision == "Release" ~ "Release Recommendation, Program Release Granted",
    T ~ "Other/Unknown"
  ),
  p = paste0(round(prop * 100), "%")) %>%
  ggplot(aes(x = release, y = prop, fill = tool_name)) +
  geom_col(position = "dodge") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(labels = percent_format(1)) +
  geom_text(aes(label = p), vjust = -0.5, position = position_dodge(0.9))

ggsave("G:/CrimJustice/Pretrial/000-Pretrial Pilot Program/SB 36 and AB 74  Reporting/SB 36 Output 2023/F65.png")
```

