---
title: "R Notebook"
output: html_notebook
---
Libraries
```{r setup}
library(gsubfn)
library(lubridate)
library(openxlsx)
library(readxl)
library(fuzzyjoin)
# library(pROC)
library(tidyverse)
#library(tools)
library(data.table)
```

# DOJ loading, cleaning, collapsing
Loading in Full DOJ RRF Data
```{r eval=FALSE, include=FALSE}
#files <- list.files("D:/DOJ Pretrial Pilot Data/19-148/Output", full.names = T)
files <- list.files("C:/temp files for transfer 3.30.22/Run 05/unzipped", full.names = T)

#1st Partition
doj_df <- lapply(files[2:38], function(x){
  
  df <- read.csv(x, colClasses = "character", header = F) %>%
    select_if(function(x) !(all(is.na(x)) | all(x=="") | all(x=="#")))
  
  return(df)
})

doj_df <- doj_df %>% bind_rows()

fwrite(doj_df, file = "1 of 2 CORI CII Pretrial Dataset.csv")
rm(doj_df)

#2nd Partition
doj_df2 <- lapply(files[39:77], function(x){
  
  df <- read.csv(x, colClasses = "character", header = F) %>%
    select_if(function(x) !(all(is.na(x)) | all(x=="") | all(x=="#")))
  
  return(df)
})

doj_df2 <- doj_df2 %>% bind_rows()

fwrite(doj_df2, file = "2 of 2 CORI CII Pretrial Dataset.csv")
rm(doj_df2)

# Combinging First Partition with Headers
doj_df <- fread("1 of 2 CORI CII Pretrial Dataset.csv", colClasses = "character")

#Top with Headers, except this time they did not  give us headers
top_doj <- read.csv(files[1], colClasses = "character", header = F)
top_doj <- read_fwf(files[1])

top_doj <- top_doj %>%
  select_if(function(x) !(all(is.na(x)) | all(x=="") | all(x=="#")))

names(doj_df) <- names(top_doj)

doj_df <- bind_rows(top_doj, doj_df)

doj_df <- doj_df %>%
  filter(as_date(CYC_DATE) >= "2012-01-01")

#Combining Second Partition
doj_df2 <- fread("2 of 2 CORI CII Pretrial Dataset.csv", colClasses = "character")

names(doj_df2) <- names(top_doj)

doj_df2 <- doj_df2 %>%
  filter(as_date(CYC_DATE) >= "2012-01-01")

doj_df <- bind_rows(doj_df, doj_df2)

fwrite(doj_df, file = "CORI CII Pretrial Dataset Post 2012.csv")

rm(top_doj, doj_df2)

# fread(files[1])

# c(12, 2, 12, 1, 10, 30, 1, 8, 8, 9, 1, 10, 30, 1, 8, 9, 8, 8, 8, 9, 1, 1, 15, 3, 30, 3, 30, 3, 3, 1, 1, 2, 30, 8, 30, 1, 12, 8, 1, 12, 8, 2, 30, 1, 25, 9, 25, 2, 30, 1, 12, 8, 20, 5, 50, 1, 30, 5, 50, 1, 30, 12, 5, 50, 1, 30, 12, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 12, 4, 40, 1, 20, 1, 12, 2, 15, 3, 1, 15, 3, 1, 1, 150, 1)

read_fwf(files[1], col_positions = fwf_widths(c(12, 2, 12, 1, 10, 30, 1, 8, 8, 9, 1, 10, 30, 1, 8, 9, 8, 8, 8, 9, 1, 1, 15, 3, 30, 3, 30, 3, 3, 1, 1, 2, 30, 8, 30, 1, 12, 8, 1, 12, 8, 2, 30, 1, 25, 9, 25, 2, 30, 1, 12, 8, 20, 5, 50, 1, 30, 5, 50, 1, 30, 12, 5, 50, 1, 30, 12, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 12, 4, 40, 1, 20, 1, 12, 2, 15, 3, 1, 15, 3, 1, 1, 150, 1), col_names = c("RECORD_ID", "SUBJECT_STATUS", "SUBJECT_ID",
"REQ_SEG_SEP", "REQ_CII_NUMBER", "REQ_NAME", "REQ_GENDER", "REQ_DOB", "REQ_CDL", "REQ_SSN", "PII_SEG_SEP",
"CII_NUMBER", "PRI_NAME", "GENDER", "PRI_DOB", "PRI_SSN", "PRI_CDL", "PRI_IDN", "PRI_INN", "FBI_NUMBER", "PDR_SEG_SEP",
"RACE_CODE", "RACE_DESCR", "EYE_COLOR_CODE", "EYE_COLOR_DESCR", "HAIR_COLOR_CODE", "HAIR_COLOR_DESCR",
"HEIGHT", "WEIGHT", "SINGLE_SOURCE", "MULTI_SOURCE", "POB_CODE", "POB_NAME", "POB_TYPE", "CITIZENSHIP_LIST",
"CYC_SEG_SEP","CYC_ORDER", "CYC_DATE", "STP_SEG_SEP", "STP_ORDER", "STP_EVENT_DATE", "STP_TYPE_CODE", "STP_TYPE_DESCR",
"STP_ORI_TYPE", "STP_ORI_TYPE_DESCR", "STP_ORI_CODE", "STP_ORI_DESCR", "STP_ORI_CNTY_CODE", "STP_ORI_CNTY_NAME",
"CNT_SEG_SEP", "CNT_ORDER", "DISP_DATE", "OFN", "OFFENSE_CODE", "OFFENSE_DESCR", "OFFENSE_TOC", "OFFENSE_QUAL_LST",
"DISP_OFFENSE_CODE", "DISP_OFFENSE_DESCR", "DISP_OFFENSE_TOC", "DISP_OFFENSE_QUAL_LST", "CONV_OFFENSE_ORDER", "CONV_OFFENSE_CODE", "CONV_OFFENSE_DESCR",
"CONV_OFFENSE_TOC", "CONV_OFFENSE_QUAL_LST", "FE_NUM_ORDER", "FE_NUM_ARR_AGY", "FE_NUM_BNCH_WARR", "FE_NUM_CITE", "FE_NUM_DOCKET",
"FE_NUM_INCIDENT", "FE_NUM_BOOKING", "FE_NUM_NUMBER", "FE_NUM_REMAND", "FE_NUM_OOS_INN", "FE_NUM_CRT_CASE", "FE_NUM_WARRANT",
"DISP_ORDER", "DISP_CODE", "DISP_DESCR", "CONV_STAT_CODE", "CONV_STAT_DESCR", "SENT_SEG_SEP",
"SENT_ORDER", "SENT_LOC_CODE", "SENT_LOC_DESCR", "SENT_LENGTH", "SENT_TIME_CODE", "SENT_TIME_DESCR", "CYC_AGE", "CII_TYPE", "CII_TYPE_ALPHA", "COMMENT_TEXT", "END_OF_REC")))

# c("RECORD_ID", "SUBJECT_STATUS", "SUBJECT_ID",
# "REQ_SEG_SEP",
# "REQ_CII_NUMBER", "REQ_NAME", "REQ_GENDER", "REQ_DOB", "REQ_CDL", "REQ_SSN",
# "PII_SEG_SEP",
# "CII_NUMBER", "PRI_NAME", "GENDER", "PRI_DOB", "PRI_SSN", "PRI_CDL", "PRI_IDN", "PRI_INN", "FBI_NUMBER",
# "PDR_SEG_SEP",
# "RACE_CODE", "RACE_DESCR", "EYE_COLOR_CODE", "EYE_COLOR_DESCR", "HAIR_COLOR_CODE", "HAIR_COLOR_DESCR",
# "HEIGHT", "WEIGHT", "SINGLE_SOURCE", "MULTI_SOURCE", "POB_CODE", "POB_NAME", "POB_TYPE", "CITIZENSHIP_LIST",
# "CYC_SEG_SEP","CYC_ORDER", "CYC_DATE",
# "STP_SEG_SEP",
# "STP_ORDER", "STP_EVENT_DATE", "STP_TYPE_CODE", "STP_TYPE_DESCR",
# "STP_ORI_TYPE", "STP_ORI_TYPE_DESCR", "STP_ORI_CODE", "STP_ORI_DESCR",
# "STP_ORI_CNTY_CODE", "STP_ORI_CNTY_NAME",
# "CNT_SEG_SEP",
# "CNT_ORDER", "DISP_DATE", "OFN", "OFFENSE_CODE", "OFFENSE_DESCR", "OFFENSE_TOC", "OFFENSE_QUAL_LST",
# "DISP_OFFENSE_CODE", "DISP_OFFENSE_DESCR", "DISP_OFFENSE_TOC", "DISP_OFFENSE_QUAL_LST",
# "CONV_OFFENSE_ORDER", "CONV_OFFENSE_CODE", "CONV_OFFENSE_DESCR",
# "CONV_OFFENSE_TOC", "CONV_OFFENSE_QUAL_LST",
# "FE_NUM_ORDER", "FE_NUM_ARR_AGY", "FE_NUM_BNCH_WARR", "FE_NUM_CITE", "FE_NUM_DOCKET",
# "FE_NUM_INCIDENT", "FE_NUM_BOOKING", "FE_NUM_NUMBER", "FE_NUM_REMAND", "FE_NUM_OOS_INN",
# "FE_NUM_CRT_CASE", "FE_NUM_WARRANT",
# "DISP_ORDER", "DISP_CODE", "DISP_DESCR", "CONV_STAT_CODE", "CONV_STAT_DESCR",
# "SENT_SEG_SEP",
# "SENT_ORDER", "SENT_LOC_CODE", "SENT_LOC_DESCR", "SENT_LENGTH", "SENT_TIME_CODE", "SENT_TIME_DESCR",
# "CYC_AGE", "CII_TYPE", "CII_TYPE_ALPHA", "COMMENT_TEXT",
# "END_OF_REC")
```

```{r eval=FALSE, include=FALSE}
ct <- "ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc"

doj_df <- lapply(files, function(x){
  
  df <- read_fwf(x, 
                 col_positions = fwf_widths(c(12, 2, 12, 1, 10, 30, 1, 8, 8, 9, 1, 10, 30, 1, 8, 9, 8, 8, 8, 9, 1, 1, 15, 3, 30, 3, 30, 3, 3, 1, 1, 2, 30, 8, 30, 1, 12, 8, 1, 12, 8, 2, 30, 1, 25, 9, 25, 2, 30, 1, 12, 8, 20, 5, 50, 1, 30, 5, 50, 1, 30, 12, 5, 50, 1, 30, 12, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 12, 4, 40, 1, 20, 1, 12, 2, 15, 3, 1, 15, 3, 1, 1, 150, 1), 
                 col_names = c("RECORD_ID", "SUBJECT_STATUS", "SUBJECT_ID",
"REQ_SEG_SEP", "REQ_CII_NUMBER", "REQ_NAME", "REQ_GENDER", "REQ_DOB", "REQ_CDL", "REQ_SSN", "PII_SEG_SEP",
"CII_NUMBER", "PRI_NAME", "GENDER", "PRI_DOB", "PRI_SSN", "PRI_CDL", "PRI_IDN", "PRI_INN", "FBI_NUMBER", "PDR_SEG_SEP",
"RACE_CODE", "RACE_DESCR", "EYE_COLOR_CODE", "EYE_COLOR_DESCR", "HAIR_COLOR_CODE", "HAIR_COLOR_DESCR",
"HEIGHT", "WEIGHT", "SINGLE_SOURCE", "MULTI_SOURCE", "POB_CODE", "POB_NAME", "POB_TYPE", "CITIZENSHIP_LIST",
"CYC_SEG_SEP","CYC_ORDER", "CYC_DATE", "STP_SEG_SEP", "STP_ORDER", "STP_EVENT_DATE", "STP_TYPE_CODE", "STP_TYPE_DESCR",
"STP_ORI_TYPE", "STP_ORI_TYPE_DESCR", "STP_ORI_CODE", "STP_ORI_DESCR", "STP_ORI_CNTY_CODE", "STP_ORI_CNTY_NAME",
"CNT_SEG_SEP", "CNT_ORDER", "DISP_DATE", "OFN", "OFFENSE_CODE", "OFFENSE_DESCR", "OFFENSE_TOC", "OFFENSE_QUAL_LST",
"DISP_OFFENSE_CODE", "DISP_OFFENSE_DESCR", "DISP_OFFENSE_TOC", "DISP_OFFENSE_QUAL_LST", "CONV_OFFENSE_ORDER", "CONV_OFFENSE_CODE", "CONV_OFFENSE_DESCR",
"CONV_OFFENSE_TOC", "CONV_OFFENSE_QUAL_LST", "FE_NUM_ORDER", "FE_NUM_ARR_AGY", "FE_NUM_BNCH_WARR", "FE_NUM_CITE", "FE_NUM_DOCKET",
"FE_NUM_INCIDENT", "FE_NUM_BOOKING", "FE_NUM_NUMBER", "FE_NUM_REMAND", "FE_NUM_OOS_INN", "FE_NUM_CRT_CASE", "FE_NUM_WARRANT",
"DISP_ORDER", "DISP_CODE", "DISP_DESCR", "CONV_STAT_CODE", "CONV_STAT_DESCR", "SENT_SEG_SEP",
"SENT_ORDER", "SENT_LOC_CODE", "SENT_LOC_DESCR", "SENT_LENGTH", "SENT_TIME_CODE", "SENT_TIME_DESCR", "CYC_AGE", "CII_TYPE", "CII_TYPE_ALPHA", "COMMENT_TEXT", "END_OF_REC")),
                col_types = ct) 
  
  return(df)
})

doj_d <- doj_df %>% bind_rows() %>%
    select_if(function(x) !(all(is.na(x)) | all(x=="") | all(x=="#"))) %>%
    filter(as_date(CYC_DATE) >= "2012-01-01") #fix this with more appropriate date cutoff

fwrite(doj_d, file = "CORI CII Pretrial Dataset Post 2012 4.5.22.csv")

```


Cleaning--Only looking at 2016-11-08+ for now.
```{r eval=FALSE, include=FALSE}
doj_d <- fread("CORI CII Pretrial Dataset Post 2012.csv", colClasses = "character")

doj_df <- doj_d %>%
  #Earliest assessment
  filter(as_date(CYC_DATE) >= "2016-11-08")

doj_df <- doj_df %>%
  ungroup() %>%
  select(4,6:7, 21:24,26,28,32,34:38,48,50,52:59, DISP_CODE, DISP_DESCR) %>%
  mutate(DISP_CODE = as.numeric(DISP_CODE)) %>%
  mutate(arrested_flag = if_else(grepl("ARREST", STP_TYPE_DESCR), 1, 0),
       filed_flag = if_else(grepl("COURT", STP_TYPE_DESCR), 1, 0),
       convicted_flag = if_else(DISP_CODE %in% c(2500:2799), 1, 0),
       dismissed_flag = if_else(DISP_CODE %in% c(50:299, 450:549, 550:599, 1000:1299, 1900:2199, 2800:3099), 1, 0),
       acquitted_flag = if_else(DISP_CODE %in% c(3100:3399), 1, 0),
       non_final_disp_flag = if_else(DISP_CODE %in% c(0:50, 300:449, 600:999, 1300:1899, 2200:2499, 3400:5000), 1, 0),
       arrest_disp_flag = if_else(DISP_CODE %in% c(50:299, 1000:1299), 1, 0),
       pros_disp_flag = if_else(DISP_CODE %in% c(450:549, 1900:2199), 1, 0),
       court_disp_flag = if_else(DISP_CODE %in% c(550:599, 2500:3399), 1, 0)) %>% # disposition code list provided by DOJ
  mutate(SENTENCE_DATE = if_else(SENT_ORDER != "", STP_EVENT_DATE, ""),
         DISP_DATE = if_else(!is.na(DISP_CODE) & DISP_DATE == "", STP_EVENT_DATE , DISP_DATE),
         DISP_DATE = if_else(non_final_disp_flag == 1, "" , DISP_DATE)) %>%
  filter(!grepl("ADDITIONAL ACTION", STP_TYPE_DESCR)) %>%
  separate(OFFENSE_DESCR, c("charge","doj_charge_description"), sep = "-") %>%
  separate(charge, c("charge", "charge_code"), sep = " " ) %>%
  mutate(charge_original = charge) %>%
  mutate(charge = toupper(gsub("\\/|\\(|\\)| |\\.|\\.*|^[A-Z]*|\\\\.*|\\{|\\}","", charge))) %>%
  rename(charge_level = OFFENSE_TOC) %>%
  unite(join_var, charge_level, charge_code, charge, remove = T)


  
save(doj_df, file = "CORI CII Pretrial Dataset Post 2018 4.6.22.RData")

```

Hierarchy
```{r eval=FALSE, include=FALSE}
# doj_df <- doj_df %>%
#   select(-c(OFFENSE_TOC, charge, code_type)) %>%
#   rename(doj_charge_description = desc)

load("Complete Charge Code Hierarchy.RData")

doj_df <- left_join(doj_df, charge_hier) 

doj_df <- doj_df %>%
  ungroup() %>%
  mutate(felony_flag = if_else(charge_level == "F", 1, 0),
         misd_flag = if_else(charge_level == "M", 1, 0)) %>%
  mutate_if(is.numeric, funs(if_else(is.na(.), 0, .))) %>%
  mutate(hierarchy = if_else(hierarchy == 0, 1e6, hierarchy)) 
 
# ?mutate_if
# charge_list <- doj_df %>%
#   count(charge, desc) %>%
#   arrange(desc(n))
# 
# write.xlsx(charge_list, file = "All DOJ Charges.csv")
# 
# charge_hier
```


Collapse to Booking and Court
```{r eval=FALSE, include=FALSE}
# doj_df <- fread("CORI CII Pretrial Dataset Post 2012.csv", colClasses = "character")

# court_dispo is an intermediate flag to make sure dispostion is only related to court actions 
doj_df <- doj_df %>%
  rename(CII_NUMBER = REQ_CII_NUMBER) %>%
  # mutate(court_dispo_flag = if_else(STP_ORI_TYPE_DESCR == "Court", 1, 0),
  #        dispo_flag = if_else(court_dispo_flag == 1 | DISP_DESCR != "", 1, 0)) %>%
  # mutate(SENTENCE_DATE = if_else(SENT_ORDER != "", STP_EVENT_DATE, ""),
  #        DISP_DATE = if_else(DISP_DESCR != "" & DISP_DATE == "", STP_EVENT_DATE, DISP_DATE),
  #        DISP_DATE = if_else(STP_ORI_TYPE_DESCR == "Court" & DISP_DATE == "", STP_EVENT_DATE, DISP_DATE)) %>%
  group_by(CII_NUMBER, CYC_DATE) %>%
  mutate(arrest_date = min(STP_EVENT_DATE),
         SENTENCE_DATE = max(SENTENCE_DATE), # LOOK AT THIS -- should this be min instead of max????? ******************** (currently formatted as character, so if you take min it will mess it up, change format or otherwise deal with this)
         DISP_DATE = max(DISP_DATE)) %>%
  ungroup() %>%
  select(-c(SENT_ORDER:SENT_TIME_DESCR))

#save(doj_df, file = "Cleaned uncollapsed DOJ Data 4.6.22.RData")

# load("Cleaned uncollapsed DOJ Data 4.6.22.RData")


coll_df <- doj_df %>%
  mutate(CYC_DATE = ymd(CYC_DATE),
         STP_EVENT_DATE = ymd(STP_EVENT_DATE),
         DISP_DATE = ymd(DISP_DATE),
         SENTENCE_DATE = ymd(SENTENCE_DATE),
         arrest_date = ymd(arrest_date)) %>% 
  mutate_at(vars(special_flag:dv_possible_flag, -hierarchy), funs("arrest" = if_else(. == 1 & STP_ORI_TYPE_DESCR == "Arrest", 1, 0))) %>%
  mutate_at(vars(special_flag:dv_possible_flag, -hierarchy), funs("court" = if_else(. == 1 & STP_ORI_TYPE_DESCR == "Court", 1, 0))) %>%
  mutate_at(vars(special_flag:dv_possible_flag, -hierarchy), funs("conviction" = if_else(. == 1 & convicted_flag == 1, 1, 0))) %>%
  rename_at(vars(ends_with("arrest")), funs(paste0("arrest_", gsub("_arrest", "", .)))) %>%
  rename_at(vars(ends_with("court")), funs(paste0("court_", gsub("_court", "", .)))) %>%
  rename_at(vars(ends_with("conviction")), funs(paste0("conviction_", gsub("_conviction", "", .)))) %>%
  mutate(pretrial_end_date = if_else(DISP_DATE <= SENTENCE_DATE | is.na(SENTENCE_DATE), DISP_DATE, SENTENCE_DATE)) %>%
  group_by(CII_NUMBER, CYC_DATE) %>%
  mutate_at(vars(contains("flag")), max) %>%
  # mutate(pretrial_dispo_date = if_else(convicted == 1|dismissed == 1, max(STP_EVENT_DATE[convicted == 1|dismissed == 1]), as_date(NA))) %>%
  # mutate(max_hier = min(hierarchy),
  #        max_charge = charge[hierarchy == max_hier][1],
  #        max_descrip = off_descrip[hierarchy == max_hier][1]) %>%
  # mutate(max_conv_charge = charge[grepl("^CONVICTED", DISP_DESCR)][1],
  #        max_conv_descrip = off_descrip[grepl("^CONVICTED", DISP_DESCR)][1],
  #        max_conv_hier = hierarchy[max_conv_charge == charge][1]) %>%
  # mutate_at(vars(dv_flag:violent), funs(max(.))) %>%
  mutate(join_var = paste(join_var, collapse = " ")) %>%  
  filter(hierarchy == min(hierarchy)) %>%
         # SENT_LOC_DESCR = paste(unique(SENT_LOC_DESCR), collapse = ", "),
         # SENT_LENGTH = paste(unique(SENT_LENGTH), collapse = ", "),
         # SENT_TIME_DESCR = paste(unique(SENT_TIME_DESCR), collapse = ", ")) %>%
  # filter(hierarchy == min(hierarchy)) %>%
  ungroup() %>%
  distinct(CII_NUMBER, CYC_DATE, .keep_all = T) 
  # mutate(pretrial_end_date = if_else(is.na(DISP_DATE), SENTENCE_DATE, pretrial_end_date))

# coll_df <- coll_df %>%
#   mutate(max_conv_hier = if_else(max_conv_charge == "", 1e6, max_conv_hier)) %>%
#   mutate_at(vars(DISP_DESCR, desc), funs(gsub("^,", "", .)))

#save(coll_df, file = "Collapsed Pretrial DOJ Data 4.6.22.RData")

```


# Join collapsed DOJ and Snowflake extract
Load and format Snowflake extract
```{r}
load("D:/DOJ Pretrial Pilot Data/Collapsed Pretrial DOJ Data 4.6.22.RData")
#load("Pre-DOJ Combined County Pretrial Data.RData")
# load("Unmatched Court Data.RData")
# G:\CrimJustice\PretrialAssessmentPilot\CIIs for DOJ\CIIs for DOJ 3 21 2022
files <- list.files("G:/CrimJustice/PretrialAssessmentPilot/CIIs for DOJ/CIIs for DOJ 3 21 2022/snowflake extract with joining fields", full.names = T)

#1st Partition
sf_df <- lapply(files[2:16], function(x){
  
  df <- fread(x, colClasses = "character")
  
  return(df)
})

#2nd partition
sf_dfhead <- fread(files[1], colClasses = "character")

sf_df <- sf_df %>% bind_rows()
names(sf_df) <- names(sf_dfhead)

sf_df <- sf_dfhead %>%
  bind_rows(sf_df)


sf_df <- sf_df %>%
  mutate(across(contains("DATE"), ~ymd(.x)))

#save(sf_df, file = "Snowflake extract for joining 4.6.22.RData")
```

Standardizing names in doj data
```{r}
names(coll_df) <- tolower(names(coll_df))

coll_df <- coll_df %>%
  rename(cii = cii_number)

#standardizing cii and then race variable names.
#names(coll_df)[1:3] <- c("cii", "sex", "race")

names(sf_df) <- tolower(names(sf_df))

names(sf_df)
```

Primary Joining
```{r}
# coll_df <- coll_df %>%
  # Flags are currently off
  # filter(filed_flag == 1)
  # select(-c(race, cyc_order, stp_order, stp_type_descr, stp_ori_type_descr, offense_code, charge_original), -(dv_flag:sf_violent), everything(),
  #        sentence_date) %>%
  # mutate(pretrial_dispo_date = if_else(is.na(disp_date), sentence_date, pretrial_dispo_date)) %>%
  # mutate(start = as.numeric(cyc_date),
  #        end = start) %>%
  # ungroup() %>%
  # filter(charge_level %in% c("F", "M")) %>%
  # mutate(row_doj = row_number())


dispo_df <- coll_df %>%
  mutate(start = as.numeric(cyc_date),
         end = start) %>%
  select(cii, arrest_date, start, end, sentence_date, disp_date, pretrial_end_date, disp_descr, filed_flag, convicted_flag, court_disp_flag, matches("court_.*_flag"), matches("conviction_.*_flag"))

 
# full_df <- df %>%
#   mutate(start = as.numeric(if_else(is.na(arrest_date), book_date - 2, arrest_date)),
#          end = as.numeric(if_else(is.na(arrest_date), book_date, arrest_date)),
#          row_m = row_number()) 


full_df <- sf_df %>%
  filter(!is.na(booking_date)) %>%
  mutate(start = as.numeric(booking_date -2),
         end = as.numeric(booking_date),
         row_m = row_number())

full_df %>%
  filter(is.na(start))

sf_df %>%
  #filter(is.na(booking_date)) %>%
  count(county)
```

Diagnostic
```{r eval=FALSE, include=FALSE}
dispo_df <- coll_df %>%
  mutate(start = as.numeric(CYC_DATE),
         end = start)

dispo_df %>%
  summarise(min_start = min(start), min_end = min(end), max_start = max(start), max_end = max(end))

dispo_df %>%
  summarise(min_cyc = min(CYC_DATE), max_cyc = max(CYC_DATE))
  

load("G:/CrimJustice/PretrialAssessmentPilot/temp files for transfer 3.30.22/processed/Snowflake extract for joining 4.6.22.RData")

sf_df %>%
  summarise(min(BOOKING_DATE, na.rm = T), max(BOOKING_DATE, na.rm = T), sum(is.na(BOOKING_DATE)))

sf_df %>%
  count(is.na(CII))

sf_cii <- sf_df %>%
  select(CII) %>%
  distinct()

coll_cii <- coll_df %>%
  select(CII_NUMBER) %>%
  distinct() %>%
  rename(CII = CII_NUMBER)

coll_cii %>%
  semi_join(sf_cii)
#584,959 matching CIIs

sf_df %>%
  filter(!is.na(BOOKING_DATE)) %>%
  filter(BOOKING_DATE >= "2016-11-30") %>%
  distinct(BOOKING_DATE) %>%
  mutate(bdateminus = BOOKING_DATE -2) %>%
  mutate(bdatenum = as.numeric(BOOKING_DATE)) %>%
  mutate(bdatenumminus = as.numeric(bdateminus)) %>%
  select(BOOKING_DATE, bdateminus, bdatenum, bdatenumminus) %>%
  arrange(BOOKING_DATE)

sf_df %>%
  filter(!is.na(BOOKING_DATE)) %>%
  mutate(start = as.numeric(BOOKING_DATE -2),
         end = as.numeric(BOOKING_DATE),
         row_m = row_number())

coll_df %>%
  filter(!is.na(CYC_DATE)) %>%
  filter(CYC_DATE >= "2016-11-30") %>%
  distinct(CYC_DATE) %>%
  mutate(bdateminus = CYC_DATE -2) %>%
  mutate(bdatenum = as.numeric(CYC_DATE)) %>%
  mutate(bdatenumminus = as.numeric(bdateminus)) %>%
  select(CYC_DATE, bdateminus, bdatenum, bdatenumminus) %>%
  arrange(CYC_DATE)

as.numeric(as.Date("2018-01-01"))
as.numeric(as.Date("2018-01-03"))


gen_anti <- genome_anti_join(full_df, dispo_df, by = c("cii", "start", "end"))

#save(gen_anti, file = "anti genome join 4.7.22.RData")

full_df
```

Join DOJ data to all bookings
```{r}
full_df <- genome_left_join(full_df, dispo_df, by = c("cii", "start", "end"))

full_df <- full_df %>%
  rename_all(funs(gsub("\\.y$", "_doj", .))) %>%
  rename_all(funs(gsub("\\.x$", "", .))) %>%
  mutate(match_dif = abs(as.numeric(booking_date) - start_doj)) %>%
  group_by(county, row_m) %>%
  filter(match_dif == min(match_dif)|is.na(match_dif)) %>%
  ungroup() %>%
  distinct(row_m, .keep_all = T)
 

full_df <- full_df %>%
  mutate(pretrial_period_end_date_doj = if_else(is.na(pretrial_period_end_date), pretrial_period_end_date_doj, pretrial_period_end_date)) # changed 6.16.22
  #rename(pretrial_period_end_date_doj = pretrial_end_date) 

#save(full_df, file = "SF DOJ Joined 4.6.22.RData")
save(full_df, file = "SF DOJ Joined 6.17.22.RData")
```

Diagnostic
```{r eval=FALSE, include=FALSE}
load("G:/CrimJustice/PretrialAssessmentPilot/temp files for transfer 3.30.22/processed/SF DOJ Joined 4.6.22.RData")

full_df %>%
  count(match_dif)

full_df %>%
  mutate(pretrial_end_date_doj = if_else(is.na(pretrial_period_end_date), pretrial_period_end_date_doj, pretrial_period_end_date)) %>%
  mutate(start = as.numeric(as_date(release_date)) + 1,
         end = as.numeric(pretrial_period_end_date_doj)) %>%
  count(!is.na(pretrial_end_date_doj), !is.na(release_date), end > start)
```


Create subset for recidivism join using only complete pretrial periods
```{r}
# load("Jail, RRF, Court, DOJ Joined.RData")

match_df_2022 <- full_df %>%
  #mutate(pretrial_period_end_date_doj = if_else(is.na(pretrial_period_end_date), pretrial_period_end_date_doj, pretrial_period_end_date)) %>% #changed this, used to be assigned to pretrial_end_date, need to fix variable names going forward ****************************************************
  filter(!is.na(pretrial_period_end_date_doj)) %>%
  arrange(booking_date) %>%
  # group_by(row_j, county) %>%
  # mutate(pretrial_dispo_date = max(pretrial_dispo_date)) %>%
  ungroup() 
  # distinct(local_id, pretrial_dispo_date, .keep_all = T)
#

#save(match_df_2022, file = "Match df 4.12.22.RData")

# load("Court Collapsed Full Data.RData")
#load("Match df 4.12.22.RData")


# With county data unmatched with DOJ data for now.
match_df_2022 <- match_df_2022 %>%
  filter(!is.na(release_date),
         !is.na(pretrial_period_end_date_doj)) %>%
  filter(pretrial_period_end_date_doj - as_date(release_date) > 0) %>%
  mutate(start = as.numeric(as_date(release_date)) + 1,
         end = as.numeric(pretrial_period_end_date_doj)) %>%
  ungroup() %>%
  mutate(match_id = paste0(cii, county)) %>%
  filter(end > start) %>%
  mutate(row_m = row_number())
```

Recidivism join
```{r}
#With DOJ Data
recid_df <- coll_df %>%
  # filter(convicted_flag == 1) %>%
  mutate(row_doj = row_number()) %>%
  mutate(start = as.numeric(cyc_date),
         end = start) %>%
  select(recid_date = cyc_date, cii, recid_join_var = join_var, recid_charge_description = doj_charge_description, arrested_flag, 
         recid_filed_flag = filed_flag, recid_convicted_flag = convicted_flag, matches("convict|^arrest.*flag|^court.*flag"), start, end, row_doj) 

names(recid_df) <- gsub("conviction", "recid_conviction", names(recid_df))
names(recid_df) <- gsub("arrest", "recid_arrest", names(recid_df))
names(recid_df) <- gsub("court", "recid_filed", names(recid_df))



eval_df <- genome_left_join(match_df_2022, recid_df, by = c("cii", "start", "end"))

 
eval_df <- eval_df %>%
  mutate(recid_date = if_else(is.na(recid_date), as_date("2030-01-01"), recid_date)) %>%
  mutate_at(vars(contains("flag")), funs(if_else(is.na(.), 0, .))) %>%
  group_by(row_m) %>%
  mutate_at(vars(filed_flag:recid_conviction_dv_possible_flag, -row_m), max) %>%
  mutate(recid_date = min(recid_date)) %>%
  ungroup() %>%
  distinct(row_m, .keep_all = T) %>%
  mutate(recid_date = if_else(recid_date == as_date("2030-01-01"), as_date(NA), recid_date)) %>%
  select(-matches("^start"), -matches("^end")) %>%
  rename(cii = cii.x) %>%
  select(-cii.y)

#save(eval_df, file = "Eval df2 4.6.22.RData")
#save(eval_df, file = "Eval df 4.12.22.RData")
save(eval_df, file = "Eval df 6.17.22.RData")


shell.exec(getwd())

eval_df %>%
  count(county)
```

Add back on the rows from full_df that did not make it into eval_df??? Test run this code and alter to work!!
```{r}
all_with_doj_and_recid <- full_df %>%
  select(-row_m) %>% # remove any other rows that will be problematic because they were changed or removed in eval_df
  left_join(eval_df)

# check to make sure number of rows is correct
# check to make sure number of columns is correct

save(all_with_doj_and_recid, file = "All with recid 6.17.22.RData")

```

Diagnostic
```{r eval=FALSE, include=FALSE}
full_df %>%
  count(!is.na(release_date), !is.na(pretrial_period_end_date), !is.na(pretrial_period_end_date_doj), release_date < pretrial_period_end_date, release_date < pretrial_period_end_date_doj)

load("G:/CrimJustice/PretrialAssessmentPilot/temp files for transfer 3.30.22/processed/Eval df 4.12.22.RData")

eval_df %>%
  summarise(min(booking_date), max(booking_date))

summary(eval_df$booking_date)
summary(eval_2021$book_date)

eval_df %>%
  filter(booking_date >= "2019-07-01") %>%
  #filter(county == "Sacramento") %>%
  group_by(year(booking_date), month(booking_date), county) %>%
  count()

eval_2021 %>%
  filter(book_date >= "2019-07-01") %>%
    filter(county == "Sacramento") %>%
  group_by(year(book_date), month(book_date), county) %>%
  count()

eval_df %>%
  filter(county == "Los Angeles") %>%
  count()

eval_2021 %>%
  filter(county == "Los Angeles") %>%
  count()

eval_df %>%
  filter(booking_date >= "2018-07-01") %>%
  filter(county == "Los Angeles") %>%
  mutate(book_my = floor_date(booking_date, unit = "month")) %>%
  group_by(book_my, county) %>%
  count() %>%
  ggplot() +
  aes(x = book_my, y = n, color = county) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


eval_2021 %>%
  filter(book_date >= "2018-07-01") %>%
  filter(county == "Los Angeles") %>%
  mutate(book_my = floor_date(book_date, unit = "month")) %>%
  group_by(book_my, county) %>%
  count() %>%
  ggplot() +
  aes(x = book_my, y = n, color = county) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


summary_2022 <- eval_df %>%
  filter(booking_date >= "2017-01-01") %>%
  filter(booking_date < "2021-01-01") %>%
  group_by(year = year(booking_date), county) %>%
  count() %>%
  rename(count_2022 = n)

summary_2021 <- eval_2021 %>%
  filter(book_date >= "2017-01-01") %>%
  filter(book_date < "2021-01-01") %>%
  group_by(year = year(book_date), county) %>%
  count()  %>%
  rename(count_2021 = n)

summary_both <- summary_2022 %>%
  full_join(summary_2021, by = c("year","county")) %>%
  mutate(dif_2022minus2021 = count_2022 - count_2021) %>%
  arrange(year)
```

Nonsense
```{r eval=FALSE, include=FALSE}
summary_both %>%
  #filter(year == 2019) %>%
  ungroup() %>%
  select(-month, -dif_2022minus2021) %>%
  group_by(year, county) %>%
  mutate(sum2022 = sum(count_2022), sum2021 = sum(count_2021)) %>%
  select(-count_2022, -count_2021) %>%
  distinct() 

annual_2022 <- eval_df %>%
  group_by(year = year(booking_date)) %>%
  count() %>%
  rename(count_2022 = n)

annual_2021 <- eval_2021 %>%
  group_by(year = year(book_date)) %>%
  count() %>%
  rename(count_2021 = n)

annual_2022 %>%
  full_join(annual_2021) %>%
  mutate(count_2021 = if_else(is.na(count_2021), 0, as.numeric(count_2021))) %>%
  mutate(dif = count_2022 - count_2021) %>%
  select(-count_2022, -count_2021) 


eval_df %>%
  filter(booking_date <= "2017-01-01")
  
```


Anonymized Data Set
```{r eval=FALSE, include=FALSE}
# names(eval_df)

anon_df <- eval_df %>%
  select(-c(book_num, court_case_id, court_docket_id, cdl_id, fbi, cii, contains("name"), dob, matches("id$"), zip_code))

write.csv(anon_df, file = "Anonymized Fabricated Data for Practice.csv")
```

Mystery?
```{r eval=FALSE, include=FALSE}
# load("Final Failure Evaluation.RData")

#not sure what this piece of code is for, seems unnecessary and weird
eval_df_2022 <- eval_df %>%
  rename_all(funs(gsub("\\.y$", "_r", .))) %>%
  rename_all(funs(gsub("\\.x$", "", .))) %>%
  # select(-charge_level_r) %>%
  #Change Back tot_misd_r to actual match
  #mutate_at(vars(court_dispo:sf_violent_filing, -sentence_date), funs(if_else(is.na(.), 0, as.numeric(.)))) %>%
  mutate_at(vars(contains("_flag")), funs(if_else(is.na(.), 0, as.numeric(.)))) %>%
  # mutate_at(vars(dv_flag_r:tot_misd_r, small_vio:violent_recid), funs(if_else(is.na(.), 0, as.numeric(.)))) %>%
  group_by(row_m) %>%
  mutate_at(vars(court_dispo:sf_violent_filing, -sentence_date, -row_m), sum) %>%
  # mutate_at(vars(dv_flag_r:tot_misd_r, small_vio:violent_recid), sum) %>%
  # mutate_at(vars(contains("prior")), max) %>%
  filter(max_hier == min(max_hier)|is.na(max_hier)) %>%
  ungroup() %>%
  distinct(row_m, .keep_all = T) 

#save(eval_df, file = "Final Failure Evaluation 4.RData")
# 
# eval_df %>%
#   # filter(as_date(pretrial_dispo_date) - cyc_date == 0)
#   # mutate(dif = cyc_date - as_date(release_date)) %>%
#   mutate(dif = pretrial_dispo_date - cyc_date) %>%
#   ggplot() +
#   aes(x = dif) +
#   geom_density()
# 
# eval_df %>%
#   filter(!is.na(match_id.y))
# 
# match_df %>%
#   filter(match_id %in% unique(recid_df$match_id))
# 
# match_df %>%
#   add_count()

names(eval_df)
```

```{r eval=FALSE, include=FALSE}
eval_df <- eval_df %>%
  mutate(fta_warrant = if_else(fta_warrant == 0 & !is.na(fta_flag_r), fta_flag_r, as.numeric(fta_warrant))) %>%
  mutate(recid_combined = if_else(fta_warrant == 1, 1, recid)) 
# 
# eval_df <- eval_df %>%
#   filter(book_date >= as_date("2015-07-01"),
#          # book_type == "Street",
#          pretrial_dispo_date - as_date(release_date) > 0)

eval_df %>%
  count(county, recid, assessed_risk_level) %>%
  group_by(county, assessed_risk_level) %>%
  mutate(total = sum(n), n = n/total) %>%
  filter(recid == 1) %>%
  select(-total, -recid) %>%
  spread(assessed_risk_level, n) %>%
  select(county, low, med, high, unk, `<NA>`)

eval_df %>%
  count(county, fta_warrant, assessed_risk_level) %>%
  group_by(county, assessed_risk_level) %>%
  mutate(total = sum(n), n = n/total) %>%
  filter(fta_warrant == 1) %>%
  select(-total, -fta_warrant) %>%
  spread(assessed_risk_level, n) %>%
  select(county, low, med, high, unk, `<NA>`)

eval_df %>%
  count(county, recid_combined, assessed_risk_level) %>%
  group_by(county, assessed_risk_level) %>%
  mutate(total = sum(n), n = n/total) %>%
  filter(recid_combined == 1) %>%
  select(-total, -recid_combined) %>%
  spread(assessed_risk_level, n) %>%
  select(county, low, med, high, unk, `<NA>`)

roc_df <- eval_df %>%
  mutate(ra = case_when(assessed_risk_level == "low" ~ 0,
            assessed_risk_level == "med" ~ 1,
            assessed_risk_level == "high" ~ 2,
            T ~ NA_real_)) %>%
  filter(!is.na(ra))

summary(glm(fta_warrant ~ as.factor(ra) + county, data = roc_df))

sapply(unique(roc_df$county), function(i){
  roc_df <- roc_df %>%
    filter(county == i)
  roc(roc_df$recid_combined ~ roc_df$ra)
  })

  
eval_df %>%
  select(start, end, start_r, end_r)

check_df <- match_df %>%
  # mutate(dif = as.numeric(book_date) - start_doj) %>%
  mutate(dif = end - start) 
  count(dif)
  
summary(check_df$dif)

table(imp_df$book_type_original)
```

